### 2024-11-01 posts/Abortion/abortion.qmd
abortion

---
title: "Abortion"
date: 10/29/2024
date-modified: last-modified
date-format: full
categories: [Others]
website:
  comments: 
    utterances:
      repo: quarto-dev/quarto-web
#image: "cluster1.png"
tbl-colwidths: [5,30,125]
format: 
  html:
    page-layout: full
bibliography: references.bib
---

## Impact of Medicaid Expansion on Abortion Rates

### Introduction

The expansion of Medicaid reduced the cost of abortion and related care services, which may have increased the demand for abortion services. However, the expansion of Medicaid also increased access to contraception, which may have reduced the number of unwanted pregnancies and the demand for abortion services. Therefore, the impact of Medicaid expansion on abortion rates is ambiguous[@eliason2022]. To investigate the impact of Medicaid expansion on abortion rates, we used a difference-in-differences approach to compare changes in abortion rates in states that expanded Medicaid to those that did not.

### Data

#### Abortion Statistics

![](images/clipboard-3841962446.png)

#### Medicaid Expansion

[![](images/clipboard-174034814.png){fig-alt="MACPAC" fig-align="center"}](https://www.macpac.gov/subtopic/medicaid-expansion/)

## Impact of Telehealth Abortion on Abortion Rates

One in five abortion cases is through Telehealth. Telehealth abortion is a safe and effective way to access abortion services. Medication abortion accounted for 39% of all abortions in 2017. This number increased to 63% in 2020. Telehealth abortion has been shown to increase access to abortion services, reduce the abortion stigma.

[![](images/clipboard-890055587.png){fig-align="center"}](https://www.guttmacher.org/2024/03/medication-abortion-accounted-63-all-us-abortions-2023-increase-53-2020)

To investigate the impact of telehealth abortion on abortion rates, we used a difference-in-differences approach to compare changes in abortion rates in states that expanded telehealth abortion to those that did not.

-   “All telehealth abortions are counted according to **the state the medications are mailed to**.” This approach of defining and counting telehealth aborting is used by [WeCount](https://societyfp.org/research/wecount/ "https://societyfp.org/research/wecount/"), an institution for studying abortion. In the state official report (all types of abortion), I found abortions are counted by the occurrence location of the abortion procedure or residence identity (in or out of state residents). I did not find very consistent rules for counting telehealth abortions.

Some milestones for telehealth abortion:

-   In April 2020, the F.D.A. removed[ the in-person requirement ](https://www.nytimes.com/2021/04/13/health/covid-abortion-pills-mailed.html "https://www.nytimes.com/2021/04/13/health/covid-abortion-pills-mailed.html")for the duration of the pandemic, allowing pills to be mailed.

-   On December 16^th^ 2021, the new F.D.A. decision made the suspension permanent.

-   On June 24, 2022, the US Supreme Court overturned Roe v. Wade.

The states that applied the abortion shield laws, which protect providers to prescribe abortion pills to states where abortion is banned:

-   California

-   Colorado

-   Connecticut

-   Massachusetts

-   New York

-   Vermont

-   Washington

Nevertheless, the data of county or facility-level abortion reports are very limited. [Minnesota](https://www.health.state.mn.us/data/mchs/pubs/abrpt/index.html "https://www.health.state.mn.us/data/mchs/pubs/abrpt/index.html") is one of the few states that provides month-level abortion data, but the identifier of providers is not provided. Thus, it is not possible to build a panel data set. Virginia provides annual county-level abortion reports but not monthly.

### 2024-11-01 posts/Algorithmic Nudge/nudge.qmd
abortion

---
title: "Algorithmic Nudging: An Application in Curbing Problematic Smartphone Use"
date: 04/16/2024
date-modified: last-modified
date-format: full
categories: [Others]
#image: "search.png"
tbl-colwidths: [5,50,75]
format: 
  html:
    page-layout: full
---

# Algorithmic Nudging

An Application in Curbing Problematic Smartphone Use

<iframe src="pdfs/Behavior_Econ_Nudging.pdf" style="width:100%; height:600px;" frameborder="0"></iframe>

You can download it [here](pdfs/Behavior_Econ_Nudging.pdf).

### 2024-11-01 posts/Meidation/.vdoc.py

@@ -1,0 +1,194 @@
+# type: ignore
+# flake8: noqa
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| echo: false
+#| warning: false
+#| output: false
+import time;import pandas as pd;import numpy as np ;import datetime
+from datetime import datetime;from datetime import timedelta;import stata_setup
+stata_setup.config('/Applications/Stata', 'mp')
+#
+#
+#
+#
+#
+#| echo: true
+#| warning: false
+#| output: false
+#| code-fold: false
+#| code-overflow: wrap
+%%stata
+
+clear all
+set maxvar 120000, permanently
+set more off
+
+import delimited "/Users/shaokangyang/Library/CloudStorage/GoogleDrive-shaokang@vt.edu/My Drive/Nethealth/Data/CNSA/combine/7/df7_22-5.csv"
+gen date2 = date(date, "YMD")
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#

### 2024-11-05 posts/Abortion/abortion.qmd
abortion

@@
 title: "Abortion"
-date: 10/29/2024
+date: 11/03/2024
 date-modified: last-modified

### 2024-11-05 posts/Abortion/abortion.qmd
idea development

@@
 ---
-title: "Abortion"
+title: "Idea Development"
 date: 11/03/2024

### 2024-11-07 posts/Abortion/abortion.qmd
ideas

--- 2024-11-05 posts/Abortion/abortion.qmd
@@
 ---
-title: "Abortion"
-date: 11/03/2024
+title: "Idea Development"
+date: 10/30/2024
 date-modified: last-modified
@@
 
+## Impact of Medicaid Expansion on Wait Time in the Hospitals
+
+Timely treatment is crucial for healthcare outcome. The expansion of Medicaid lowered the barrier to receive healthcare service and could induce more patients to hospitals.
+
+A compelling body of research have studies the impact of Medicaid expansion on the waiting time in the emergency room.
+[@wang2022] find that Medicaid expansion increases ED wait time by 10.4% (or 3.5 minutes) However, it is not clear how Medicaid expansion impact waiting time of non-urgent hospitals.
+
+We conjecture that the expansion of Medicaid could attract patients withnon-urgent conditions to healthcare providers, yielding in an increase in waiting time for treatments.
+
+## Impact of Covid-19 on Organ Donations
+
+Organs from motor vehicle crashes is the largest organ transplant pool and accounts for **1 in 3** organ transplantation.
+
+The stay-at-home rules significantly reduced the fatal traffic collisions, resulting in decrease in organ supply [@dembosky2020].
+On the other hand, the pandemic also caused an decrease in public transportation usage and increase in personal vehicle usage [@ebrahimshaik2022].
+The increase in personal vehicle usage could increase traffic collisions, which potentially leads to an increase in organ supply.
+
+Our objective is examine the effects of Covid-19 on organ supplies.
+
+## Impact of Medicaid Expansion on Length of Stay at Hospitals
+
 ## Impact of Medicaid Expansion on Abortion Rates
@@
 Therefore, the impact of Medicaid expansion on abortion rates is ambiguous[@eliason2022].
-To investigate the impact of Medicaid expansion on abortion rates, we used a difference-in-differences approach to compare changes in abortion rates in states that expanded Medicaid to those that did not.
+To investigate the impact of Medicaid expansion on abortion rates, we plan to use a difference-in-differences approach to compare changes in abortion rates in states that expanded Medicaid to those that did not.
+
+[![](images/clipboard-1560225122.png){fig-align="center"}](https://www.pewresearch.org/short-reads/2024/03/25/what-the-data-says-about-abortion-in-the-us/sr_24-03-26_abortion_1-png/)
 
@@
 
+**Expansion Timeline**
+
+The following table shows the expansion timeline for Medicaid [@maclean2019a].
+
+![](images/clipboard-665024476.png)
+
+**Expansion Map**
+
 [![](images/clipboard-174034814.png){fig-alt="MACPAC" fig-align="center"}](https://www.macpac.gov/subtopic/medicaid-expansion/)
 
-## Impact of Telehealth Abortion on Abortion Rates
+## Impact of Telehealth on Abortion Rates
 
-One in five abortion cases is through Telehealth.
+1 in 5 abortion cases are through Telehealth in June 2024, which increased significantly compared to the 1 in 25 in April 2022 [@mulvihill2024].
 Telehealth abortion is a safe and effective way to access abortion services.
 Medication abortion accounted for 39% of all abortions in 2017.
-This number increased to 63% in 2020.
+This number increased to 63% in 2022 [@jones2024a].
 Telehealth abortion has been shown to increase access to abortion services, reduce the abortion stigma.
@@
 
-To investigate the impact of telehealth abortion on abortion rates, we used a difference-in-differences approach to compare changes in abortion rates in states that expanded telehealth abortion to those that did not.
+To investigate the impact of telehealth abortion on abortion rates, we plan to use a difference-in-differences approach to compare changes in abortion rates in states that expanded telehealth abortion to those that did not.
 
@@
 removed[ the in-person requirement ](https://www.nytimes.com/2021/04/13/health/covid-abortion-pills-mailed.html "https://www.nytimes.com/2021/04/13/health/covid-abortion-pills-mailed.html")for the duration of the pandemic, allowing pills to be mailed.
-
--   On December 16^th^ 2021, the new F.D.A. decision made the suspension permanent.
-
+-   On December 16^th^ 2021, a new F.D.A. decision made the suspension permanent.
 -   On June 24, 2022, the US Supreme Court overturned Roe v. Wade.
@@
 
+**Issues**
+
 Nevertheless, the data of county or facility-level abortion reports are very limited. [Minnesota](https://www.health.state.mn.us/data/mchs/pubs/abrpt/index.html "https://www.health.state.mn.us/data/mchs/pubs/abrpt/index.html") is one of the few states that provides month-level abortion data, but the identifier of providers is not provided.

### 2024-11-08 posts/Abortion/abortion.qmd
rstudio push

@@
 title: "Idea Development"
-date: 10/30/2024
+date: 10/29/2024
 date-modified: last-modified
@@
 ## Impact of Medicaid Expansion on Length of Stay at Hospitals
+
+Test
 

### 2024-11-10 posts/Abortion/abortion.qmd
abortion
remove wecount link

@@
 
--   “All telehealth abortions are counted according to **the state the medications are mailed to**.” This approach of defining and counting telehealth aborting is used by [WeCount](https://societyfp.org/research/wecount/ "https://societyfp.org/research/wecount/"), an institution for studying abortion.
+-   “All telehealth abortions are counted according to **the state the medications are mailed to**.” This approach of defining and counting telehealth aborting is used by WeCount, an institution for studying abortion.
 In the state official report (all types of abortion), I found abortions are counted by the occurrence location of the abortion procedure or residence identity (in or out of state residents).

### 2024-11-11 posts/Abortion/abortion.qmd
Abortion papers

@@
 Virginia provides annual county-level abortion reports but not monthly.
+
+### References
+
+-   Ozer et al. - 2023 - Digital Multisided Platforms and Women’s Health An Empirical Analysis of Peer-to-Peer Lending and Abortion Rates
+
+    <iframe src="PDF/Ozer et al. - 2023 - Digital Multisided Platforms and Women’s Health An Empirical Analysis of Peer-to-Peer Lending and A.pdf" style="width:100%; height:1500px;" frameborder="0">
+
+    </iframe>
+
+-   Augustine and Piazza - 2022 - Category Evolution Under Conditions of Stigma The Segregation of Abortion Provision into Specialist Clinics in the United States
+
+    <iframe src="PDF/Augustine and Piazza - 2022 - Category Evolution Under Conditions of Stigma The Segregation of Abortion Provision into Specialist.pdf" style="width:100%; height:1500px;" frameborder="0">
+
+    </iframe>
+
+-   Thomadsen et al. - 2023 - The Impact of a Supreme Court Decision on the Preferences of Americans Regarding Abortion Policy
+
+    <iframe src="PDF/Thomadsen et al. - 2023 - The Impact of a Supreme Court Decision on the Preferences of Americans Regarding Abortion Policy.pdf" style="width:100%; height:1500px;" frameborder="0">
+
+    </iframe>

### 2024-12-26 posts/Abortion/abortion.qmd
hide abortion blog

@@
 bibliography: references.bib
+visibility: hidden
 ---

### 2024-12-26 posts/Robustness Checks/Robustness.qmd
hide abortion blog

---
title: "Robustness Checks"
date: 07/27/2024
date-modified: last-modified
date-format: full
categories: [Paper1]
image: "images/clipboard-1164654317.png"
tbl-colwidths: [5,50,75]
format: 
  html:
    toc: true
    toc-location: right
    page-layout: full
bibliography: references.bib
---

# Test of U-Shaped Relationship

In this section, we discuss whether the U-shaped relationship is caused by outliers in the data. First of all, we take a look at the descriptive statistics of the main variables:

## Treatment of Outliers

### Raw Data

```{python}
#| echo: false
#| warning: false
#| output: true
import time;import pandas as pd;import numpy as np;import datetime
from datetime import datetime;from datetime import timedelta;import sqlite3;import warnings
import matplotlib.pyplot as plt;import seaborn as sns;warnings.filterwarnings('ignore')

df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/GoogleDrive-sky.ang510@gmail.com/My Drive/Nethealth/Data/CNSA/combine/7/df7_3hr.csv")

df[['sleep_debt','screen_time','unlock','message','message_q','screen_com','screen_nocom','sms','mms','whatsapp','length','bytes','sc_com_pct','screen_com_level2','com_level']].describe(percentiles=[.05, .10, .15, .20,  .25, .50, .75, .90,.95]).round(2)
```

We observe that there are some outliers in the data. For example, the maximum value of sleep debt is about 8 hours (479 minutes), suggesting that one did not sleep at all on that day. The minimal value of sleep debt is -12.96 hours (-778 minutes), suggesting that one slept for 20.96 hours, which is quite unusual. Moreover, the maximum screen time is 179.99 minutes; the maximum message is 1015 and the maximum unlock actions is 817 times, which could barely happen.

Recall the model-free analysis about the relationship among sleep debt, screen time and message:

![](images/model-free.png){fig-align="center"}

The margins plot based on fixed effect model with the above data is as follows:

![](images/estimation.png){fig-align="center"}

Considering the existence of outliers, the upwarding part of the U-shape might be caused by the outliers at the tail (the rightmost few bars). To check whether the U-shaped relationship is caused by outliers, we reviewed the literature about the treatement of outliers and identified the following outlier treatment strategies: **winsorization, trimming, and interquartile range method** [@leone2019; @mitton2022; @vinutha2018].

![](images/clipboard-3892815503.png){fig-align="center"}

### Winsorization

Winsorization replaces the extreme values with values at certain quartile cutoffs. The most commonly used cutoffs in business research is 1st and 99th percentiles, 5th/95th and 10th/90th are used as well [@mitton2022]. We winsorize the continuous variables in our specification at cutoffs of 1st/99tth, 2.5th/97.5th, 5th/95th and 10th/90th. The following table shows the descriptive statistics after winsorization at cutoffs of 5th/95th.

```{python}
#| echo: false
#| warning: false
#| output: true
df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/GoogleDrive-sky.ang510@gmail.com/My Drive/Nethealth/Data/CNSA/combine/7/df7_3hr-winsor95.csv")
df[['sleep_debt','screen_time','unlock','message']].describe().round(2)
```

We can find that range of sleep debt changes to \[-111, 224\] minutes from \[-778, 479\] minutes; the maximum screen time decreased to 121.46 minutes from 179.99 minutes; the maximum unlock decreased to 40 from 817; the maximum message decreased to 95 from 1015, which are relatively normal. The following table shows the descriptive statistics with winsorization at cutoffs of 1st/99tth, 2.5th/97.5th, 5th/95th and 10th/90th.

![](images/clipboard-4106334890.png){fig-align="center"}

### Trimming

Trimming deals with the outliers by simply dropping the observations with extreme values. Different from winsorization, trimming reduces the number of observations. We trim the data based on screen time at cutoffs of 1st/99tth, 2.5th/97.5th, 5th/95th and 10th/90th.

![](images/clipboard-407226497.png){fig-align="center"}

### Variable Ranks

The interquartile range (IQR) method is a variable rank strategy that rules out the outliers by calculating the upper and lower fence based on quartile values ([link](https://www.scribbr.com/statistics/outliers/)).

-   Interquartile Range (IQR)=Q3-Q1

-   Upper fence = Q3+1.5×IQR

-   Lower fence = Q1-1.5×IQR

Recall the descriptive statistics of raw data, the IQR for screen time = Q3-Q1 = 58.32 - 8.23 = 50.09 minutes. Thus, the upper and lower fences for screen time are calculated as:

-   Upper fence = 58.32+1.5×50.09 = 133.455 minutes

-   Lower fence = 8.23-1.5×50.09 = -66.891 minutes

Considering that screen time should a non-negative value, the range for screen time is **\[0, 133. 455\]** minutes. The descriptive statistics for the main variables are as follows:

```{python}
#| echo: false
#| warning: false
#| output: true
df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/GoogleDrive-sky.ang510@gmail.com/My Drive/Nethealth/Data/CNSA/combine/7/df7_3hr-IQR.csv")
df[['sleep_debt','screen_time','unlock','message']].describe().round(2)
```

We then estimate the sleep debt based on the data after winsorization, trimming and IQR method with the fixed effect model.

![](images/clipboard-36233801.png){fig-align="center"}

The results are as follows:

![](images/clipboard-3325119646.png){fig-align="center"}

The estimated coefficients for screen time and its quadratic terms are significant suggesting that the existence of turning points. The following figure visualize the margin plot based on the above outlier treatment strategies:

![](images/combined_graph.png)

The margins plot supports the existence of U-shaped relationship and the turning point are within the range of measurement windows (180 minutes).

### Outlier Treatment Based on Individual Average

#### Screen Time

![](images/clipboard-2336158588.png){fig-align="center"}

#### Deviation Measure of Screen Time

![](images/clipboard-1329186503.png){fig-align="center"}

## Spline Regressions

Spline regressions estimate the coefficients of screen time on sleep debt piecewisely. Spline regressions are widely used to test the existence of U- and inverted U-Shaped relationships [@kesavan2014; @huang2023; @tan2019; @xu2022; @zou2023]. For example, the following equation estimated the coefficients with 4 knots.

![](images/clipboard-4088933022.png){fig-align="center"}

We vary the number of knots from 1 to 5 and obtained the following results:

![](images/clipboard-3259393049.png){fig-align="center"}

We observe that the estimated coefficient transit from negative to positive regardless of the number of spline knots. The following figure visualize the transition for the spline regression with 5 knots, which supports the U-Shaped relationship.

![](images/clipboard-1164654317.png){fig-align="center"}

## Addition Checks

In addition to the above checks for U-Shaped relationships, [@haans2016] sgguested the following checks:

1.  The turning point should be within the range of observations. We can observe that both the turning points above are within the measurement window.

2.  Theoretical support for the U-shaped relationship. Moderate smartphone use makes users relax and reduces sleep debt. After the turning point, the crowding out effect of screen time and blue light effects dominate the impact of screen time and increases sleep debt.

The above checks support the U-Shaped relationship in our main specification.

# **Model Selection.**

## **Evaluation of Model Fit**

In this section, we compare the performance of various models based on Akaike information criterion (AIC) and Bayesian information criterion (BIC) [@karhade2021]

![](images/clipboard-2996370340.png){fig-align="center"}

Based on the estimation results above, the AIC and BIC values in the curvilinear model are smaller than those of the control and linear models, suggesting that the curvilinear model outperforms the control and linear models.

## **Deviation Measure of Screen Time**

In this section, we consider individuals' different levels of smartphone use or use habits since individuals' dependence levels on smartphone may differ. For example, one's smartphone use amount may be systematically above the population's average while his use level is below her/his own use level on a particular day.

To address this concern, we create a deviation measure for screen time: **Screen Time Deviation = Screen Time - Unit Average Screen Time**[@ho2017; @karhade2021]

![](images/clipboard-163764688.png){fig-align="center"}

The estimation results above support the existence of U-shaped relationship and curvilinear model outperforms the control and linear models.

# Endogeneity

## Introduction

In the blog [selection issues](https://shaokang-yang.net/posts/Selection%20Issue/selection.html), we discussed the confounders that may threaten the causal relationship in the study. In this section, we discuss the different types of causes of endogeneity and their corresponding remedy strategies . Overall, there are four types of causes of endogeneity: omitted variable, simultaneity, measurement Error, and selection (of treatment and/or into sample)[@hill2021].

+---------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+---------------+
| Endogeneity Cause                           | Description                                                                                                                                                                                                                                                                                                                                                                                                                                                                 | Threaten Lvel |
+=============================================+=============================================================================================================================================================================================================================================================================================================================================================================================================================================================================+===============+
| Omitted Variable                            | There could be factors that are `missed` in the model. For example:                                                                                                                                                                                                                                                                                                                                                                                                         | High          |
|                                             |                                                                                                                                                                                                                                                                                                                                                                                                                                                                             |               |
|                                             | -   Sleep debt of previous day. An individual may need to make up sleep today if she/he had more sleep debt than average yesterday.                                                                                                                                                                                                                                                                                                                                         |               |
|                                             |                                                                                                                                                                                                                                                                                                                                                                                                                                                                             |               |
|                                             | -   Party. Participating in a party may impact smartphone use and sleep simultaneously.                                                                                                                                                                                                                                                                                                                                                                                     |               |
+---------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+---------------+
| Simultaneity                                | Smartphone users play smartphones as they cannot fall asleep.                                                                                                                                                                                                                                                                                                                                                                                                               | High          |
+---------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+---------------+
| Measurement Error                           | Since subjects in the study wear the same devices (Fitbit) and primarly use same phones (iPhones), the measurement errors are supposed to be **systematic** if there were. This might not impact the causal effects of our argument.                                                                                                                                                                                                                                        | Low           |
+---------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+---------------+
| Selection (of treatment and/or into sample) | For the Nethealth project, students were informed that the research team would collect their social networks, physical activity and sleep obtained from Fitbit devices, physical and mental health, social-psychological states, tastes and various self-reported behaviours, and demographics and background traits through surveys. There seems not likely to be significant selection bias in terms of sleep quality and smartphone use amount when recruiting students. | Low           |
+---------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+---------------+

## Dynamic Panel Model

One's sleep debt today may be influenced by the sleep debt **yesterday** and even the sleep debt of previous few days. For example, an individual may need to sleep more and reduce phone use to make up sleep today if she/he had significant high sleep debt yesterday.

![](images/Dynamic%20Panel%20Model.png){fig-align="center"}

To control for the dynamic endogeneity, we introduce the dynamic panel model by adding the lagged dependent variables:

![](images/clipboard-1927004410.png){fig-align="center"}

However, adding lagged dependent variables may introduce extra endogeneity as lagged dependent variables may be correlated with error term[@nickell1981]. To overcome this issue, we apply the Arellano–Bond estimator, which is a general method of moments (GMM) estimator based on dynamic panel data with first differences [@huang2023]. Arellano–Bond estimator uses the lagged variables as instruments to address the endogeneity bias. For example, suppose that the sleep debt today is affected by the sleep debt yesterday but not the one of the day before yesterday. In another word, $Sleep\ Debt_{i,t-2}$ only affect $Sleep\ Debt_{i,t}$ by affecting $Sleep\ Debt_{i,t-1}$. Thus, $Sleep\ Debt_{i,t-2}$ can work as an instrument variable for $Sleep\ Debt_{i,t-1}$, namely "internal instrument" [@roodman2009] which is shown in the following figure.

![](images/AB.png){fig-align="center"}

The situation becomes complicated if the $Sleep\ Debt_{i,t-2}$ can directly affect $Sleep\ Debt_{i,t}$, as shown below:

![](images/AB2.png){fig-align="center"}

We can identify the $Sleep\ Debt_{i,t-n}$ that does not affect $Sleep\ Debt_{i,t}$ directly and take it as instrument for variables from $Sleep\ Debt_{i,t-1}$ to $Sleep\ Debt_{i,t-n-1}$. The Arellano–Bond test checks the exogeneity assumption and can tell us whether the lagged variables are correlated with error term. A Sargan test tells us whether the instruments are correctly specified.

![](images/clipboard-1903385873.png){fig-align="center"}

The Arellano–Bond test above for AR (1) is significant while AR(2) is not, indicating that the lagged one period of sleep debt is a significant estimator for the current sleep debt. We include lagged (1) sleep debt into our main estimation and obtained the following results:

![](images/clipboard-761639513.png){fig-align="center"}

-   **Arellano-Bond test for AR(1) in first differences**:

    -   z = -5.76

    -   p-value = 0.000

    -   Interpretation: This test checks for the presence of first-order serial correlation. The null hypothesis of no first-order serial correlation is rejected because the p-value is less than 0.05. This suggests that there is first-order serial correlation in the differenced errors, which is expected in first-differenced models.

-   **Arellano-Bond test for AR(2) in first differences**:

    -   z = 0.53

    -   p-value = 0.594

    -   Interpretation: This test checks for the presence of second-order serial correlation. The null hypothesis of no second-order serial correlation cannot be rejected because the p-value is greater than 0.05. This suggests that there is no second-order serial correlation in the differenced errors.

-   **Sargan test of overidentifying restrictions**:

    -   chi2(2) = 45.42

    -   p-value = 0.000

    -   Interpretation: This test checks the overall validity of the instruments. The null hypothesis is that the instruments are valid (i.e., they are not correlated with the error term). The p-value is less than 0.05, so the null hypothesis is rejected, indicating that the instruments may be invalid.

-   **Hansen test of overidentifying restrictions**:

    -   chi2(2) = 0.00

    -   p-value = 1.000

    -   Interpretation: Similar to the Sargan test, but robust to heteroskedasticity. The p-value is much greater than 0.05, so the null hypothesis cannot be rejected, indicating that the instruments are valid.

We find that one minute increase in the sleep debt of the previous day can lead to **0.095** minute decrease in the current sleep debt. We also observe that the estimation for screen time terms are significant, supporting the existence of U-shaped relationship between sleep debt and screen time.

The above process shows how GMM address endogeneity caused by **omitted variable**. In addition, The GMM model removes other **reverse causality** by “internally transforming the data”-taking the first difference of variables in the model[@ullah2018].

### 2024-12-26 docs/posts/Abortion/abortion.R

@@ -1,0 +1,81 @@
+library(ggplot2)
+library(dplyr)
+library(ggtext); library(svglite)
+# Example for installing from a local file
+install.packages("/path/to/AugSynth.tar.gz", repos = NULL, type = "source")
+install.packages("devtools")
+
+# Use devtools to install the package from GitHub
+devtools::install_github("ebenmichael/augsynth")
+
+library(augsynth)
+?augsynth
+?ggplot
+
+
+#read data
+df<-read.csv("/Users/shaokangyang/Library/CloudStorage/GoogleDrive-sky.ang510@gmail.com/My Drive/Nethealth/Data/CNSA/combine/7/df7_3hr.csv")
+df <- df %>%
+  filter(screen_time > 10)
+
+# Assuming 'df' is the original dataframe
+# Creating bins for screen time
+bins <- seq(10, 185, by = 5)
+df <- df %>%
+  mutate(screen_time_bin = cut(screen_time, breaks = bins, right = FALSE, include.lowest = TRUE))
+
+# Aggregating data
+grouped <- df %>%
+  group_by(screen_time_bin) %>%
+  summarise(
+    avg_sleep_debt = mean(sleep_debt, na.rm = TRUE),
+    avg_message = mean(message, na.rm = TRUE),
+    count = n()
+  )
+
+# Convert screen_time_bin to a factor for proper ordering
+grouped <- grouped %>%
+  mutate(screen_time_bin = factor(screen_time_bin, levels = unique(screen_time_bin)))
+
+# Plotting
+p <- ggplot(data = grouped, aes(x = screen_time_bin)) +
+  # Line plot for sleep debt trend
+  geom_line(aes(y = avg_sleep_debt, group = 1, color = "Sleep Debt"), size = 1) +
+  geom_point(aes(y = avg_sleep_debt, color = "Sleep Debt"), size = 2) +
+  geom_text(aes(y = avg_sleep_debt, label = round(avg_sleep_debt, 2)), 
+            vjust = -0.5, color = "purple", size = 3) +
+  # Line plot for message trend
+  geom_line(aes(y = avg_message, group = 1, color = "Message"), linetype = "dashed", size = 1) +
+  geom_point(aes(y = avg_message, color = "Message"), size = 2) +
+  geom_text(aes(y = avg_message, label = round(avg_message, 2)), 
+            vjust = -0.5, color = "darkorange", size = 3) +
+  # Bar plot for number of observations
[…]

### 2024-12-26 posts/Abortion/abortion.qmd
hide abortion blog

--- 2024-11-11 posts/Abortion/abortion.qmd
@@
 date-modified: last-modified
+visibility: hidden
 date-format: full

### 2024-12-26 index.qmd
mainfont: Lato monofont: Roboto

---
title: "Shaokang Yang"
mainfont: Lato
monofont: Roboto
---

-   **Ph.D. in Business Information Technology (Expected)**

Virginia Polytechnic Institute and State University

-   **M.Sc. in Data Science and Economics**

University of Milan

-   **Bachelor of Engineering/Bachelor of Economics**

Jimei University

### 2025-01-05 research.qmd
font change for teaching

---
title: "Research"
format:
  html:
    css: styles2.css
class: custom-font-pos
---

### 2025-01-05 posts.qmd
font update

---
title: "Project Blog"
listing: 
  contents: posts # all Quarto docs in the `posts` directory will be included on your listing page
  type: grid # or `default` or `table`; each type has its own set of yaml options to include
  sort: 
      - "date-modified desc" # can also sort on more than one field
      - "date desc"
  categories: true # allows you to sort posts by assigned categories
  sort-ui: [date-modified, title]
  fields: [image, date-modified, title, description, date, author]
  page-size: 6
format:
  html:
    css: styles2.css
class: custom-font-pos
website:
  favicon: Virginia_Tech_seal.svg.png
  image: Horizontal_VT_Full_Color_RGB.png

  sidebar:
    tools:
      - icon: github
        href: https://github.com/Shaokang-Yang
      - icon: linkedin
        href: https://www.linkedin.com/in/shaokang-y-52b633162/
    section: true
    contents:
      - href: index.qmd
        text: Home
      - research.qmd
      - teaching.qmd
      - posts.qmd
---

### 2025-01-05 docs/posts/Abortion/abortion.R

@@ -1,81 +1,0 @@
-library(ggplot2)
-library(dplyr)
-library(ggtext); library(svglite)
-# Example for installing from a local file
-install.packages("/path/to/AugSynth.tar.gz", repos = NULL, type = "source")
-install.packages("devtools")
-
-# Use devtools to install the package from GitHub
-devtools::install_github("ebenmichael/augsynth")
-
-library(augsynth)
-?augsynth
-?ggplot
-
-
-#read data
-df<-read.csv("/Users/shaokangyang/Library/CloudStorage/GoogleDrive-sky.ang510@gmail.com/My Drive/Nethealth/Data/CNSA/combine/7/df7_3hr.csv")
-df <- df %>%
-  filter(screen_time > 10)
-
-# Assuming 'df' is the original dataframe
-# Creating bins for screen time
-bins <- seq(10, 185, by = 5)
-df <- df %>%
-  mutate(screen_time_bin = cut(screen_time, breaks = bins, right = FALSE, include.lowest = TRUE))
-
-# Aggregating data
-grouped <- df %>%
-  group_by(screen_time_bin) %>%
-  summarise(
-    avg_sleep_debt = mean(sleep_debt, na.rm = TRUE),
-    avg_message = mean(message, na.rm = TRUE),
-    count = n()
-  )
-
-# Convert screen_time_bin to a factor for proper ordering
-grouped <- grouped %>%
-  mutate(screen_time_bin = factor(screen_time_bin, levels = unique(screen_time_bin)))
-
-# Plotting
-p <- ggplot(data = grouped, aes(x = screen_time_bin)) +
-  # Line plot for sleep debt trend
-  geom_line(aes(y = avg_sleep_debt, group = 1, color = "Sleep Debt"), size = 1) +
-  geom_point(aes(y = avg_sleep_debt, color = "Sleep Debt"), size = 2) +
-  geom_text(aes(y = avg_sleep_debt, label = round(avg_sleep_debt, 2)), 
-            vjust = -0.5, color = "purple", size = 3) +
-  # Line plot for message trend
-  geom_line(aes(y = avg_message, group = 1, color = "Message"), linetype = "dashed", size = 1) +
-  geom_point(aes(y = avg_message, color = "Message"), size = 2) +
-  geom_text(aes(y = avg_message, label = round(avg_message, 2)), 
-            vjust = -0.5, color = "darkorange", size = 3) +
-  # Bar plot for number of observations
[…]

### 2025-01-05 ProjectBlog/paper1/Clustering Anlysis/cluster.qmd
Research blog moving

---
title: "Behavior Segmentation for Smartphone Use "
date: 12/09/2023
date-modified: last-modified
date-format: full
categories: [Paper1]
image: "cluster1.png"
tbl-colwidths: [5,30,125]
format: 
  html:
    page-layout: full
---

We cluster the smartphone use behaviors based on the three major metrics of smartphone use actions: Screen time, unlock frequency and message.

## Descriptive Statistics

```{python}
#| echo: false
#| warning: false
#| output: true
import time;import pandas as pd;import numpy as np;import datetime
from datetime import datetime;from datetime import timedelta;import sqlite3;import warnings
import matplotlib.pyplot as plt;import seaborn as sns;warnings.filterwarnings('ignore')

df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/GoogleDrive-sky.ang510@gmail.com/My Drive/Nethealth/Data/CNSA/combine/7/df7_3hr.csv")
df1 = df
df1[['sleep_debt','sleep_duration','screen_time','message','unlock','especiallyclose_m','family_m','friend_m','romantic_m','naps','naps_dur']].describe(percentiles=[.10,.15,.20,.25,.50,.55,.60,.65,.70, .75,.80,.85,.90,.95]).round(2)
```

## Trend Analysis

First, we explore the relationships among variables of sleep debt, screen time (\>15 min) and message with measurement window of three hours:

```{python}
#| echo: false
#| warning: false
#| output: true

# Creating a special bin for 0
df1=df[df['screen_time']>15]
bins = [-np.inf, 0.001] + list(range(15, 185, 5))  # 0.1 to include 0 in the first bin exclusively
df1['screen_time_bin'] = pd.cut(df1['screen_time'], bins=bins, right=False, include_lowest=True)
# Recalculating the aggregated data
grouped = df1.groupby('screen_time_bin').agg({'sleep_debt':'mean', 'message':'mean', 'screen_time':'count'}).reset_index()
# Replotting with the adjusted bins
fig, ax1 = plt.subplots(figsize=(14, 8))
# Line plot for sleep debt trend
line1, = ax1.plot(grouped['screen_time_bin'].astype(str), grouped['sleep_debt'], color='blue', linestyle='-', marker='o', label='Sleep Debt')
# Adding labels for sleep debt
for x, y in zip(grouped['screen_time_bin'].astype(str), grouped['sleep_debt']):
    ax1.text(x, y, f'{y:.2f}', va='bottom', ha='center', color='blue')
# Setting the left y-axis for sleep debt
ax1.set_xlabel('Screen Time (minutes)')
ax1.set_ylabel('Average Sleep Debt')
ax1.set_title('Sleep Debt, Screen Time and Message')
ax1.tick_params(axis='x', rotation=45)
# Line plot for message count on a secondary y-axis
ax2 = ax1.twinx()
line2, = ax2.plot(grouped['screen_time_bin'].astype(str), grouped['message'], color='darkorange', linestyle='--', marker='o', label='Message')
# Adding labels for message count
for i, txt in enumerate(grouped['message']):
    ax2.annotate(f'{txt:.2f}', (grouped['screen_time_bin'].astype(str)[i], grouped['message'][i]), textcoords="offset points", xytext=(0,10), ha='center')
ax2.set_ylabel('Message')
# Bar plot for the number of observations on a secondary y-axis
ax3 = ax1.twinx()
bars = ax3.bar(grouped['screen_time_bin'].astype(str), grouped['screen_time'], width=0.4, color='lightgrey', alpha=0.5, label='Number of Observations')
ax3.spines['right'].set_position(('outward', 60))  # Offset the right spine of ax3
ax3.set_ylabel('Number of Observations')
# Labeling the number of observations above each bar
for bar in bars:
    yval = bar.get_height()
    ax3.text(bar.get_x() + bar.get_width() / 2, yval, f'{int(yval)}', va='bottom', ha='center', color='black')
# Adjusting the plot
ax1.grid(True, which='both', linestyle='--', linewidth=0.5)
ax2.grid(False)
ax3.grid(False)
# Adding legends
fig.legend(loc='upper right')
fig.tight_layout()
plt.show()
```

## Clustering Analysis

### Cluster=11

#### Front view

```{python}
#| echo: false
#| warning: false
#| output: true

from sklearn.cluster import KMeans
from sklearn.preprocessing import StandardScaler
import matplotlib.pyplot as plt
from mpl_toolkits.mplot3d import Axes3D
random_seed = 1
#df1 = df[df['message'] < 240]
df1=df
df1.loc[df1['unlock'] > 41, 'unlock'] = 41;df1.loc[df1['message'] > 96, 'message'] = 96
# Normalizing the data
scaler = StandardScaler()
df_scaled = scaler.fit_transform(df1[['screen_time', 'unlock', 'message']])
# KMeans clustering on normalized data
kmeans = KMeans(n_clusters=11,random_state=random_seed)
clusters = kmeans.fit_predict(df_scaled)
# Adding the cluster data to the original dataframe
df1['cluster'] = clusters+1
# Visualizing the clusters in 3D with normalized data
# Custom colors for each cluster (12 in total)
nature_colors = [
    '#1f77b4',  # Blue
    '#ff7f0e',  # Orange
    '#2ca02c',  # Green
    '#d62728',  # Red
    '#9467bd',  # Purple
    '#ffbb78',  # Light Orange
    '#7a876f',  # Pink
    '#17becf',  # Gray
    '#bcbd22',  # Olive
    '#c27ba0',  # Yellow
    '#aec7e8',  # Light Blue
    '#8c564b',   # Brown
    '#c27ba0'
]
fig = plt.figure(figsize=(16, 9.6))
ax = fig.add_subplot(111, projection='3d')
# Plotting each cluster with a custom color
for i in range(1, 12):  # Cluster numbers now range from 1 to 12
    cluster_data = df1[df1['cluster'] == i]
    ax.scatter(cluster_data['screen_time'], cluster_data['unlock'], cluster_data['message'], 
               color=nature_colors[i - 1], label=f'Cluster {i}', marker='o')
ax.set_title('Behavior Segmentation for Smartphone Use (Cluster=11)')
ax.set_xlabel('Screen Time (minutes)')
ax.set_ylabel('Unlock Frequency')
ax.set_zlabel('Number of Messages')
# Legend
ax.legend(title="Clusters")
plt.show()
```

#### Rear view

```{python}
#| echo: false
#| warning: false
#| output: true

from sklearn.cluster import KMeans
from sklearn.preprocessing import StandardScaler
import matplotlib.pyplot as plt
from mpl_toolkits.mplot3d import Axes3D
random_seed = 1
#df1 = df[df['message'] < 240]
df1=df
df1.loc[df1['unlock'] > 41, 'unlock'] = 41;df1.loc[df1['message'] > 96, 'message'] = 96
# Normalizing the data
scaler = StandardScaler()
df_scaled = scaler.fit_transform(df1[['screen_time', 'unlock', 'message']])
# KMeans clustering on normalized data
kmeans = KMeans(n_clusters=11,random_state=random_seed)
clusters = kmeans.fit_predict(df_scaled)
# Adding the cluster data to the original dataframe
df1['cluster'] = clusters+1
# Visualizing the clusters in 3D with normalized data
# Custom colors for each cluster (12 in total)
nature_colors = [
    '#1f77b4',  # Blue
    '#ff7f0e',  # Orange
    '#2ca02c',  # Green
    '#d62728',  # Red
    '#9467bd',  # Purple
    '#ffbb78',  # Light Orange
    '#7a876f',  # Pink
    '#17becf',  # Gray
    '#bcbd22',  # Olive
    '#c27ba0',  # Yellow
    '#aec7e8',  # Light Blue
    '#8c564b',   # Brown
    '#c27ba0'
]
fig = plt.figure(figsize=(16, 9.6))
ax = fig.add_subplot(111, projection='3d')
# Plotting each cluster with a custom color
for i in range(1, 12):  # Cluster numbers now range from 1 to 12
    cluster_data = df1[df1['cluster'] == i]
    ax.scatter(cluster_data['screen_time'], cluster_data['unlock'], cluster_data['message'], 
               color=nature_colors[i - 1], label=f'Cluster {i}', marker='o')
ax.set_title('Behavior Segmentation for Smartphone Use (Cluster=11)')
ax.set_xlabel('Screen Time (minutes)')
ax.set_ylabel('Unlock Frequency')
ax.set_zlabel('Number of Messages')
# Legend
ax.legend(title="Clusters")
ax.view_init(30, 120)
plt.show()

```

### Descriptive Statistics by Cluster

#### Sleep Debt

```{python}
#| echo: false
#| warning: false
#| output: true

summary = df.groupby('cluster')['sleep_debt'].describe().round(2)
print(summary)
```

The above summary suggests that **cluster 2** has the minimal sleep debt of **31.53** minutes. In comparison, **cluster 10** has the maximal sleep debt of **54.76** minutes.

#### Screen Time

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['screen_time'].describe().round(2)
print(summary)

```

#### Unlock

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['unlock'].describe().round(2)
print(summary)
```

#### Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['message'].describe().round(2)
print(summary)
```

The table above suggests the cluster 2 has the **second highest message frequency**, 79.57. It implies that message might reduce sleep debt.

#### Close Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['especiallyclose_m'].describe().round(2)
print(summary)
```

The table above suggests the cluster 2 has the **highest close message frequency**, 49.06. It implies that close message might reduce sleep debt.

#### Family Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['family_m'].describe().round(2)
print(summary)
```

The table above suggests the cluster 2 has the **highest family message frequency**, 5.89. It implies that family message might reduce sleep debt.

#### Friend Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['friend_m'].describe().round(2)
print(summary)
```

#### Romantic Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['romantic_m'].describe().round(2)
print(summary)
```

#### Steps

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['steps'].describe().round(1)
print(summary)
```

### Cluster=10

#### Front view

```{python}
#| echo: false
#| warning: false
#| output: true

from sklearn.cluster import KMeans
from sklearn.preprocessing import StandardScaler
import matplotlib.pyplot as plt
from mpl_toolkits.mplot3d import Axes3D
random_seed = 1
#df1 = df[df['message'] < 240]
df1=df
df1.loc[df1['unlock'] > 41, 'unlock'] = 41;df1.loc[df1['message'] > 96, 'message'] = 96
# Normalizing the data
scaler = StandardScaler()
df_scaled = scaler.fit_transform(df1[['screen_time', 'unlock', 'message']])
# KMeans clustering on normalized data
kmeans = KMeans(n_clusters=10,random_state=random_seed)
clusters = kmeans.fit_predict(df_scaled)
# Adding the cluster data to the original dataframe
df1['cluster'] = clusters+1
# Visualizing the clusters in 3D with normalized data
# Custom colors for each cluster (12 in total)
nature_colors = [
    '#1f77b4',  # Blue
    '#ff7f0e',  # Orange
    '#2ca02c',  # Green
    '#d62728',  # Red
    '#9467bd',  # Purple
    '#ffbb78',  # Light Orange
    '#7a876f',  # Pink
    '#17becf',  # Gray
    '#bcbd22',  # Olive
    '#FFC300',  # Yellow
    '#aec7e8',  # Light Blue
    '#8c564b'   # Brown
]
fig = plt.figure(figsize=(16, 9.6))
ax = fig.add_subplot(111, projection='3d')
# Plotting each cluster with a custom color
for i in range(1, 11):  # Cluster numbers now range from 1 to 12
    cluster_data = df1[df1['cluster'] == i]
    ax.scatter(cluster_data['screen_time'], cluster_data['unlock'], cluster_data['message'], 
               color=nature_colors[i - 1], label=f'Cluster {i}', marker='o')
ax.set_title('Behavior Segmentation for Smartphone Use (Cluster=10)')
ax.set_xlabel('Screen Time (minutes)')
ax.set_ylabel('Unlock Frequency')
ax.set_zlabel('Number of Messages')
# Legend
ax.legend(title="Clusters")
plt.show()
```

#### Rear view

```{python}
#| echo: false
#| warning: false
#| output: true

from sklearn.cluster import KMeans
from sklearn.preprocessing import StandardScaler
import matplotlib.pyplot as plt
from mpl_toolkits.mplot3d import Axes3D
random_seed = 1
#df1 = df[df['message'] < 240]
df1=df
df1.loc[df1['unlock'] > 41, 'unlock'] = 41;df1.loc[df1['message'] > 96, 'message'] = 96
# Normalizing the data
scaler = StandardScaler()
df_scaled = scaler.fit_transform(df1[['screen_time', 'unlock', 'message']])
# KMeans clustering on normalized data
kmeans = KMeans(n_clusters=10,random_state=random_seed)
clusters = kmeans.fit_predict(df_scaled)
# Adding the cluster data to the original dataframe
df1['cluster'] = clusters+1
# Visualizing the clusters in 3D with normalized data
# Custom colors for each cluster (12 in total)
nature_colors = [
    '#1f77b4',  # Blue
    '#ff7f0e',  # Orange
    '#2ca02c',  # Green
    '#d62728',  # Red
    '#9467bd',  # Purple
    '#ffbb78',  # Light Orange
    '#7a876f',  # Pink
    '#17becf',  # Gray
    '#bcbd22',  # Olive
    '#FFC300',  # Yellow
    '#aec7e8',  # Light Blue
    '#8c564b'   # Brown
]
fig = plt.figure(figsize=(16, 9.6))
ax = fig.add_subplot(111, projection='3d')
# Plotting each cluster with a custom color
for i in range(1, 11):  # Cluster numbers now range from 1 to 12
    cluster_data = df1[df1['cluster'] == i]
    ax.scatter(cluster_data['screen_time'], cluster_data['unlock'], cluster_data['message'], 
               color=nature_colors[i - 1], label=f'Cluster {i}', marker='o')
ax.set_title('Behavior Segmentation for Smartphone Use (Cluster=10)')
ax.set_xlabel('Screen Time (minutes)')
ax.set_ylabel('Unlock Frequency')
ax.set_zlabel('Number of Messages')
# Legend
ax.legend(title="Clusters")
ax.view_init(30, 60)
plt.show()
```

### Descriptive Statistics by Cluster

#### Sleep Debt

```{python}
#| echo: false
#| warning: false
#| output: true

summary = df.groupby('cluster')['sleep_debt'].describe().round(2)
print(summary)
```

The above summary suggests that **cluster 6** has the minimal sleep debt of **31.41** minutes. In comparison, **cluster 4** has the maximal sleep debt of **54.50** minutes.

#### Screen Time

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['screen_time'].describe().round(2)
print(summary)

```

#### Unlock

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['unlock'].describe().round(2)
print(summary)
```

#### Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['message'].describe().round(2)
print(summary)
```

The table above suggests the cluster 4 has the **second highest message frequency, 78.15**. It implies that message might reduce sleep debt.

#### Close Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['especiallyclose_m'].describe().round(2)
print(summary)
```

The table above suggests the cluster 6 has the **highest close message frequency, 47.81**. It implies that close message might reduce sleep debt.

#### Family Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['family_m'].describe().round(2)
print(summary)
```

The table above suggests the cluster 6 has the **highest family message frequency, 5.83**. It implies that family message might reduce sleep debt.

#### Friend Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['friend_m'].describe().round(2)
print(summary)
```

#### Romantic Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['romantic_m'].describe().round(2)
print(summary)
```

#### Steps

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['steps'].describe().round(1)
print(summary)
```

### Cluster=9

#### Front view

```{python}
#| echo: false
#| warning: false
#| output: true

from sklearn.cluster import KMeans
from sklearn.preprocessing import StandardScaler
import matplotlib.pyplot as plt
from mpl_toolkits.mplot3d import Axes3D
random_seed = 1
#df1 = df[df['message'] < 240]
df1=df
df1.loc[df1['unlock'] > 41, 'unlock'] = 41;df1.loc[df1['message'] > 96, 'message'] = 96
# Normalizing the data
scaler = StandardScaler()
df_scaled = scaler.fit_transform(df1[['screen_time', 'unlock', 'message']])
# KMeans clustering on normalized data
kmeans = KMeans(n_clusters=9,random_state=random_seed)
clusters = kmeans.fit_predict(df_scaled)
# Adding the cluster data to the original dataframe
df1['cluster'] = clusters+1
# Visualizing the clusters in 3D with normalized data
# Custom colors for each cluster (12 in total)
nature_colors = [
    '#1f77b4',  # Blue
    '#ff7f0e',  # Orange
    '#2ca02c',  # Green
    '#d62728',  # Red
    '#9467bd',  # Purple
    '#ffbb78',  # Light Orange
    '#7a876f',  # Pink
    '#17becf',  # Gray
    '#bcbd22',  # Olive
    '#FFC300',  # Yellow
    '#aec7e8',  # Light Blue
    '#8c564b'   # Brown
]
fig = plt.figure(figsize=(16, 9.6))
ax = fig.add_subplot(111, projection='3d')
# Plotting each cluster with a custom color
for i in range(1, 10):  # Cluster numbers now range from 1 to 12
    cluster_data = df1[df1['cluster'] == i]
    ax.scatter(cluster_data['screen_time'], cluster_data['unlock'], cluster_data['message'], 
               color=nature_colors[i - 1], label=f'Cluster {i}', marker='o')
ax.set_title('Behavior Segmentation for Smartphone Use (Cluster=9)')
ax.set_xlabel('Screen Time (minutes)')
ax.set_ylabel('Unlock Frequency')
ax.set_zlabel('Number of Messages')
# Legend
ax.legend(title="Clusters")
plt.show()
```

#### Rear view

```{python}
#| echo: false
#| warning: false
#| output: true

from sklearn.cluster import KMeans
from sklearn.preprocessing import StandardScaler
import matplotlib.pyplot as plt
from mpl_toolkits.mplot3d import Axes3D
random_seed = 1
#df1 = df[df['message'] < 240]
df1=df
df1.loc[df1['unlock'] > 41, 'unlock'] = 41;df1.loc[df1['message'] > 96, 'message'] = 96
# Normalizing the data
scaler = StandardScaler()
df_scaled = scaler.fit_transform(df1[['screen_time', 'unlock', 'message']])
# KMeans clustering on normalized data
kmeans = KMeans(n_clusters=9,random_state=random_seed)
clusters = kmeans.fit_predict(df_scaled)
# Adding the cluster data to the original dataframe
df1['cluster'] = clusters+1
# Visualizing the clusters in 3D with normalized data
# Custom colors for each cluster (12 in total)
nature_colors = [
    '#1f77b4',  # Blue
    '#ff7f0e',  # Orange
    '#2ca02c',  # Green
    '#d62728',  # Red
    '#9467bd',  # Purple
    '#ffbb78',  # Light Orange
    '#7a876f',  # Pink
    '#17becf',  # Gray
    '#bcbd22',  # Olive
    '#FFC300',  # Yellow
    '#aec7e8',  # Light Blue
    '#8c564b'   # Brown
]
fig = plt.figure(figsize=(16, 9.6))
ax = fig.add_subplot(111, projection='3d')
# Plotting each cluster with a custom color
for i in range(1, 10):  # Cluster numbers now range from 1 to 12
    cluster_data = df1[df1['cluster'] == i]
    ax.scatter(cluster_data['screen_time'], cluster_data['unlock'], cluster_data['message'], 
               color=nature_colors[i - 1], label=f'Cluster {i}', marker='o')
ax.set_title('Behavior Segmentation for Smartphone Use (Cluster=9)')
ax.set_xlabel('Screen Time (minutes)')
ax.set_ylabel('Unlock Frequency')
ax.set_zlabel('Number of Messages')
# Legend
ax.legend(title="Clusters")
ax.view_init(30, 60)
plt.show()
```

### Descriptive Statistics by Cluster

#### Sleep Debt

```{python}
#| echo: false
#| warning: false
#| output: true

summary = df.groupby('cluster')['sleep_debt'].describe().round(2)
print(summary)
```

The above summary suggests that **cluster 5** has the minimal sleep debt of **31.47** minutes. In comparison, **cluster 8** has the maximal sleep debt of **54.61** minutes.

#### Screen Time

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['screen_time'].describe().round(2)
print(summary)

```

#### Unlock

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['unlock'].describe().round(2)
print(summary)
```

#### Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['message'].describe().round(2)
print(summary)
```

The table above suggests the cluster 5 has the **second highest message frequency, 77.59**. It implies that message might reduce sleep debt.

#### Close Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['especiallyclose_m'].describe().round(2)
print(summary)
```

The table above suggests the cluster 5 has the **highest close message frequency, 47.44**. It implies that close message might reduce sleep debt.

#### Family Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['family_m'].describe().round(2)
print(summary)
```

The table above suggests the cluster 5 has the **highest family message frequency, 5.76**. It implies that family message might reduce sleep debt.

#### Friend Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['friend_m'].describe().round(2)
print(summary)
```

#### Romantic Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['romantic_m'].describe().round(2)
print(summary)
```

#### Steps

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['steps'].describe().round(1)
print(summary)
```

### Cluster=8

#### Front view

```{python}
#| echo: false
#| warning: false
#| output: true

from sklearn.cluster import KMeans
from sklearn.preprocessing import StandardScaler
import matplotlib.pyplot as plt
from mpl_toolkits.mplot3d import Axes3D
random_seed = 1
#df1 = df[df['message'] < 240]
df1=df
df1.loc[df1['unlock'] > 41, 'unlock'] = 41;df1.loc[df1['message'] > 96, 'message'] = 96
# Normalizing the data
scaler = StandardScaler()
df_scaled = scaler.fit_transform(df1[['screen_time', 'unlock', 'message']])
# KMeans clustering on normalized data
kmeans = KMeans(n_clusters=8,random_state=random_seed)
clusters = kmeans.fit_predict(df_scaled)
# Adding the cluster data to the original dataframe
df1['cluster'] = clusters+1
# Visualizing the clusters in 3D with normalized data
# Custom colors for each cluster (12 in total)
nature_colors = [
    '#1f77b4',  # Blue
    '#ff7f0e',  # Orange
    '#2ca02c',  # Green
    '#d62728',  # Red
    '#9467bd',  # Purple
    '#ffbb78',  # Light Orange
    '#7a876f',  # Pink
    '#17becf',  # Gray
    '#bcbd22',  # Olive
    '#FFC300',  # Yellow
    '#aec7e8',  # Light Blue
    '#8c564b'   # Brown
]
fig = plt.figure(figsize=(16, 9.6))
ax = fig.add_subplot(111, projection='3d')
# Plotting each cluster with a custom color
for i in range(1, 9):  # Cluster numbers now range from 1 to 12
    cluster_data = df1[df1['cluster'] == i]
    ax.scatter(cluster_data['screen_time'], cluster_data['unlock'], cluster_data['message'], 
               color=nature_colors[i - 1], label=f'Cluster {i}', marker='o')
ax.set_title('Behavior Segmentation for Smartphone Use (Cluster=8)')
ax.set_xlabel('Screen Time (minutes)')
ax.set_ylabel('Unlock Frequency')
ax.set_zlabel('Number of Messages')
# Legend
ax.legend(title="Clusters")
plt.show()
```

#### Rear view

```{python}
#| echo: false
#| warning: false
#| output: true

from sklearn.cluster import KMeans
from sklearn.preprocessing import StandardScaler
import matplotlib.pyplot as plt
from mpl_toolkits.mplot3d import Axes3D
random_seed = 1
#df1 = df[df['message'] < 240]
df1=df
df1.loc[df1['unlock'] > 41, 'unlock'] = 41;df1.loc[df1['message'] > 96, 'message'] = 96
# Normalizing the data
scaler = StandardScaler()
df_scaled = scaler.fit_transform(df1[['screen_time', 'unlock', 'message']])
# KMeans clustering on normalized data
kmeans = KMeans(n_clusters=8,random_state=random_seed)
clusters = kmeans.fit_predict(df_scaled)
# Adding the cluster data to the original dataframe
df1['cluster'] = clusters+1
# Visualizing the clusters in 3D with normalized data
# Custom colors for each cluster (12 in total)
nature_colors = [
    '#1f77b4',  # Blue
    '#ff7f0e',  # Orange
    '#2ca02c',  # Green
    '#d62728',  # Red
    '#9467bd',  # Purple
    '#ffbb78',  # Light Orange
    '#7a876f',  # Pink
    '#17becf',  # Gray
    '#bcbd22',  # Olive
    '#FFC300',  # Yellow
    '#aec7e8',  # Light Blue
    '#8c564b'   # Brown
]
fig = plt.figure(figsize=(16, 9.6))
ax = fig.add_subplot(111, projection='3d')
# Plotting each cluster with a custom color
for i in range(1, 9):  # Cluster numbers now range from 1 to 12
    cluster_data = df1[df1['cluster'] == i]
    ax.scatter(cluster_data['screen_time'], cluster_data['unlock'], cluster_data['message'], 
               color=nature_colors[i - 1], label=f'Cluster {i}', marker='o')
ax.set_title('Behavior Segmentation for Smartphone Use (Cluster=8)')
ax.set_xlabel('Screen Time (minutes)')
ax.set_ylabel('Unlock Frequency')
ax.set_zlabel('Number of Messages')
# Legend
ax.legend(title="Clusters")
ax.view_init(30, 60)
plt.show()

```

### Descriptive Statistics by Cluster

#### Sleep Debt

```{python}
#| echo: false
#| warning: false
#| output: true

summary = df.groupby('cluster')['sleep_debt'].describe().round(2)
print(summary)
```

The above summary suggests that **cluster 5** has the minimal sleep debt of **31.47** minutes. In comparison, **cluster 8** has the maximal sleep debt of **54.61** minutes.

#### Screen Time

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['screen_time'].describe().round(2)
print(summary)

```

#### Unlock

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['unlock'].describe().round(2)
print(summary)
```

#### Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['message'].describe().round(2)
print(summary)
```

The table above suggests the cluster 5 has the **second highest message frequency, 77.59**. It implies that message might reduce sleep debt.

#### Close Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['especiallyclose_m'].describe().round(2)
print(summary)
```

The table above suggests the cluster 5 has the **highest close message frequency, 47.44**. It implies that close message might reduce sleep debt.

#### Family Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['family_m'].describe().round(2)
print(summary)
```

The table above suggests the cluster 5 has the **highest family message frequency, 5.76**. It implies that family message might reduce sleep debt.

#### Friend Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['friend_m'].describe().round(2)
print(summary)
```

#### Romantic Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['romantic_m'].describe().round(2)
print(summary)
```

#### Steps

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['steps'].describe().round(1)
print(summary)
```

### Cluster=7

#### Front view

```{python}
#| echo: false
#| warning: false
#| output: true

from sklearn.cluster import KMeans
from sklearn.preprocessing import StandardScaler
import matplotlib.pyplot as plt
from mpl_toolkits.mplot3d import Axes3D
random_seed = 1
#df1 = df[df['message'] < 240]
df1=df
df1.loc[df1['unlock'] > 41, 'unlock'] = 41;df1.loc[df1['message'] > 96, 'message'] = 96
# Normalizing the data
scaler = StandardScaler()
df_scaled = scaler.fit_transform(df1[['screen_time', 'unlock', 'message']])
# KMeans clustering on normalized data
kmeans = KMeans(n_clusters=7,random_state=random_seed)
clusters = kmeans.fit_predict(df_scaled)
# Adding the cluster data to the original dataframe
df1['cluster'] = clusters+1
# Visualizing the clusters in 3D with normalized data
# Custom colors for each cluster (12 in total)
nature_colors = [
    '#1f77b4',  # Blue
    '#ff7f0e',  # Orange
    '#2ca02c',  # Green
    '#d62728',  # Red
    '#9467bd',  # Purple
    '#ffbb78',  # Light Orange
    '#7a876f',  # Pink
    '#17becf',  # Gray
    '#bcbd22',  # Olive
    '#FFC300',  # Yellow
    '#aec7e8',  # Light Blue
    '#8c564b'   # Brown
]
fig = plt.figure(figsize=(16, 9.6))
ax = fig.add_subplot(111, projection='3d')
# Plotting each cluster with a custom color
for i in range(1, 8):  # Cluster numbers now range from 1 to 12
    cluster_data = df1[df1['cluster'] == i]
    ax.scatter(cluster_data['screen_time'], cluster_data['unlock'], cluster_data['message'], 
               color=nature_colors[i - 1], label=f'Cluster {i}', marker='o')
ax.set_title('Behavior Segmentation for Smartphone Use (Cluster=7)')
ax.set_xlabel('Screen Time (minutes)')
ax.set_ylabel('Unlock Frequency')
ax.set_zlabel('Number of Messages')
# Legend
ax.legend(title="Clusters")
plt.show()
```

#### Rear view

```{python}
#| echo: false
#| warning: false
#| output: true

from sklearn.cluster import KMeans
from sklearn.preprocessing import StandardScaler
import matplotlib.pyplot as plt
from mpl_toolkits.mplot3d import Axes3D
random_seed = 1
#df1 = df[df['message'] < 240]
df1=df
df1.loc[df1['unlock'] > 41, 'unlock'] = 41;df1.loc[df1['message'] > 96, 'message'] = 96
# Normalizing the data
scaler = StandardScaler()
df_scaled = scaler.fit_transform(df1[['screen_time', 'unlock', 'message']])
# KMeans clustering on normalized data
kmeans = KMeans(n_clusters=7,random_state=random_seed)
clusters = kmeans.fit_predict(df_scaled)
# Adding the cluster data to the original dataframe
df1['cluster'] = clusters+1
# Visualizing the clusters in 3D with normalized data
# Custom colors for each cluster (12 in total)
nature_colors = [
    '#1f77b4',  # Blue
    '#ff7f0e',  # Orange
    '#2ca02c',  # Green
    '#d62728',  # Red
    '#9467bd',  # Purple
    '#ffbb78',  # Light Orange
    '#7a876f',  # Pink
    '#17becf',  # Gray
    '#bcbd22',  # Olive
    '#FFC300',  # Yellow
    '#aec7e8',  # Light Blue
    '#8c564b'   # Brown
]
fig = plt.figure(figsize=(16, 9.6))
ax = fig.add_subplot(111, projection='3d')
# Plotting each cluster with a custom color
for i in range(1, 8):  # Cluster numbers now range from 1 to 12
    cluster_data = df1[df1['cluster'] == i]
    ax.scatter(cluster_data['screen_time'], cluster_data['unlock'], cluster_data['message'], 
               color=nature_colors[i - 1], label=f'Cluster {i}', marker='o')
ax.set_title('Behavior Segmentation for Smartphone Use (Cluster=7)')
ax.set_xlabel('Screen Time (minutes)')
ax.set_ylabel('Unlock Frequency')
ax.set_zlabel('Number of Messages')
# Legend
ax.legend(title="Clusters")
ax.view_init(30, 60)
plt.show()

```

### Descriptive Statistics by Cluster

#### Sleep Debt

```{python}
#| echo: false
#| warning: false
#| output: true

summary = df.groupby('cluster')['sleep_debt'].describe().round(2)
print(summary)
```

The above summary suggests that **cluster 3** has the minimal sleep debt of **35.79** minutes. In comparison, **cluster 6** has the maximal sleep debt of **53.48** minutes.

#### Screen Time

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['screen_time'].describe().round(2)
print(summary)

```

#### Unlock

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['unlock'].describe().round(2)
print(summary)
```

#### Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['message'].describe().round(2)
print(summary)
```

The table above suggests the cluster 3 has the **a message frequency of 7.56**. It implies that message level is not necessarily associated with sleep debt level.

#### Close Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['especiallyclose_m'].describe().round(2)
print(summary)
```

The table above suggests the cluster 3 has the **a close message frequency of 2.90**. It implies that close message level is not necessarily associated with sleep debt level.

#### Family Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['family_m'].describe().round(2)
print(summary)
```

The table above suggests the cluster 3 has the **a family message frequency of 0.74**. It implies that family message might reduce sleep debt.

#### Friend Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['friend_m'].describe().round(2)
print(summary)
```

#### Romantic Message

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['romantic_m'].describe().round(2)
print(summary)
```

#### Steps

```{python}
#| echo: false
#| warning: false
#| output: true
summary = df.groupby('cluster')['steps'].describe().round(1)
print(summary)
```

### 2025-01-05 ProjectBlog/paper2/Network Looking up/lookup.qmd
Research blog moving

---
title: "Contact Information Look UP "
date: 03/10/2024
date-modified: last-modified
date-format: full
categories: [Paper1]
image: "lookup.png"
tbl-colwidths: [5,30,125]
format: 
  html:
    page-layout: full
---

In the aggregation of communication events of Paper 1, we only match the communication events with the contacts reported in the **current** wave of social network surveys. However, the current social network surveys are **not** enough to cover all the contacts in the communication events. For example, let’s say an individual communicated with contact **C** on a day in the spring semester of 2016. However, contact C was not reported in the survey of the 2016 spring; instead, contact C was reported in the survey of the 2015 Fall. Contact C is taken as **relation unknown** or **closeness unknown** if we only match communication with the current surveys. In paper 2, we meet the same issue while constructing an individual’s social networks. We solve it by looking up the missed contacts in a broaden pool of surveys. Specifically, we looking up the missed contacts in: 1) **complete** social network surveys in which the focal person participated; or, 2) surveys with limitations to the closest **N** neighboring waves. In this example, we can identify contact C’s social relationship and closeness in the survey of the fall of 2015.

In this update, we applied a similar look-up strategy for Paper 1. By doing this, the communication events from closeness unknown contacts and relationship unknown contacts decreased. In contrast, those from identified contacts increased. The following figures illustrate a comparison of the proportions of communication categories with different look-up strategies.

## Original Contacts (Without Look Up)

The following figure shows the categories of messages (SMS, MMS and WhatsApp) without look up 3 hours prior to sleep. The left column are the messages categorized by social closeness. We observe that **10.83** messages are from close unknown contacts, which accounts for **over 50%** of the total messages (20.36). The middle column shows the messages categorized by message type: SMS, MMS and WhatsApp. We find that the majority of the messages are SMS. The right column shows the messages categorized by social relationships. It suggests that **10.83** messages are from relation unknown contacts, which accounts for **over 50%** of the total messages (20.36). They are the same messages whose social closeness is unidentified in the left column.

```{python}
#| echo: false
#| warning: false
#| output: true
import time;import pandas as pd;import numpy as np;import datetime
from datetime import datetime;from datetime import timedelta;import sqlite3;import warnings
import matplotlib.pyplot as plt;import seaborn as sns;warnings.filterwarnings('ignore')

df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/OneDrive-Personal/Nethealth/Data/CNSA/combine/7/df7_3hr.csv")
import plotly.graph_objs as go
# Combine and format labels with their mean values for each category
# Close Degree labels with their means
labels_close_degree = [
    f'Especially Close: {df["especiallyclose_m"].mean():.2f}',
    f'Merely Close: {df["merelyclose_m"].mean():.2f}',
    f'Less Than Close: {df["lessthanclose_m"].mean():.2f}',
    f'Distant: {df["distant_m"].mean():.2f}',
    f'Close Unknown: {df["close_unknown_m"].mean():.2f}'
]

# Message Type labels with their means
labels_message_type = [
    f'SMS: {df["sms"].mean():.2f}',
    f'MMS: {df["mms"].mean():.2f}',
    f'WhatsApp: {df["whatsapp"].mean():.2f}'
]

# Contact Type labels with their means
labels_contact_type = [
    f'Acquaintance: {df["acquaintance_m"].mean():.2f}',
    f'Co-member Organization: {df["comemberorganization_m"].mean():.2f}',
    f'Coworker: {df["coworker_m"].mean():.2f}',
    f'Friend: {df["friend_m"].mean():.2f}',
    f'Neighbor: {df["neighbor_m"].mean():.2f}',
    f'Other Family: {df["otherfamily_m"].mean():.2f}',
    f'Romantic: {df["romantic_m"].mean():.2f}',
    f'Parent: {df["parent_m"].mean():.2f}',
    f'Step Parent: {df["stepparent_m"].mean():.2f}',
    f'Sibling: {df["sibling_m"].mean():.2f}',
    f'Step Sibling: {df["stepsibling_m"].mean():.2f}',
    f'Relation Unknown: {df["rela_unknown_m"].mean():.2f}'
]

# Combine all labels for nodes
labels = labels_close_degree + labels_message_type + labels_contact_type

# Initialize the lists for the source, target, and value arrays for the Sankey diagram
source = [
    # Close Degree to Message Type
    0, 0, 0,  # Especially Close to SMS, MMS, WhatsApp
    1, 1, 1,  # Merely Close to SMS, MMS, WhatsApp
    2, 2, 2,  # Less Than Close to SMS, MMS, WhatsApp
    3, 3, 3,  # Distant to SMS, MMS, WhatsApp
    4, 4, 4   # Close Unknown to SMS, MMS, WhatsApp
] + [
    # Message Type to Contact Type
    5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5,  # SMS to all contact types
    6, 6, 6, 6, 6, 6, 6, 6, 6, 6, 6, 6,  # MMS to all contact types
    7, 7, 7, 7, 7, 7, 7, 7, 7, 7, 7, 7   # WhatsApp to all contact types
]

target = [
    # Close Degree to Message Type
    5, 6, 7,  # Especially Close to SMS, MMS, WhatsApp
    5, 6, 7,  # Merely Close to SMS, MMS, WhatsApp
    5, 6, 7,  # Less Than Close to SMS, MMS, WhatsApp
    5, 6, 7,  # Distant to SMS, MMS, WhatsApp
    5, 6, 7   # Close Unknown to SMS, MMS, WhatsApp
] + [
    # Message Type to Contact Type
    8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19,  # SMS to all contact types
    8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19,  # MMS to all contact types
    8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19   # WhatsApp to all contact types
]

# Values for all connections (assuming you have these means calculated correctly in your DataFrame)
#Judge if any of the following columns are not in the dataframe, create them and fill them with 0
for col in ['sms_acquaintance', 'sms_comemberorganization', 'sms_coworker', 'sms_friend', 'sms_neighbor', 'sms_otherfamily', 'sms_romanticpartner', 'sms_parent', 'sms_stepparent', 'sms_sibling', 'sms_stepsibling', 'sms_blank', 'mms_acquaintance', 'mms_comemberorganization', 'mms_coworker', 'mms_friend', 'mms_neighbor', 'mms_otherfamily', 'mms_romanticpartner', 'mms_parent', 'mms_stepparent', 'mms_sibling', 'mms_stepsibling', 'mms_blank', 'whatsapp_acquaintance', 'whatsapp_comemberorganization', 'whatsapp_coworker', 'whatsapp_friend', 'whatsapp_neighbor', 'whatsapp_otherfamily', 'whatsapp_romanticpartner', 'whatsapp_parent', 'whatsapp_stepparent', 'whatsapp_sibling', 'whatsapp_stepsibling', 'whatsapp_blank']:
    if col not in df.columns:
        df[col] = 0
value = [
    # Close Degree to Message Type values
    df['sms_especiallyclose'].mean(), df['mms_especiallyclose'].mean(), df['whatsapp_especiallyclose'].mean(),
    df['sms_merelyclose'].mean(), df['mms_merelyclose'].mean(), df['whatsapp_merelyclose'].mean(),
    df['sms_lessthanclose'].mean(), df['mms_lessthanclose'].mean(), df['whatsapp_lessthanclose'].mean(),
    df['sms_distant'].mean(), df['mms_distant'].mean(), df['whatsapp_distant'].mean(),
    df['sms_blank'].mean(), df['mms_blank'].mean(), df['whatsapp_blank'].mean()
] + [

    df['sms_acquaintance'].mean(), df['sms_comemberorganization'].mean(), df['sms_coworker'].mean(), df['sms_friend'].mean(),
    df['sms_neighbor'].mean(), df['sms_otherfamily'].mean(), df['sms_romanticpartner'].mean(), df['sms_parent'].mean(),
    df['sms_stepparent'].mean(), df['sms_sibling'].mean(), df['sms_stepsibling'].mean(), df['sms_blank'].mean(),
    df['mms_acquaintance'].mean(), df['mms_comemberorganization'].mean(), df['mms_coworker'].mean(), df['mms_friend'].mean(),
    df['mms_neighbor'].mean(), df['mms_otherfamily'].mean(), df['mms_romanticpartner'].mean(), df['mms_parent'].mean(),
    df['mms_stepparent'].mean(), df['mms_sibling'].mean(), df['mms_stepsibling'].mean(), df['mms_blank'].mean(),
    df['whatsapp_acquaintance'].mean(), df['whatsapp_comemberorganization'].mean(),df['whatsapp_coworker'].mean(), df['whatsapp_friend'].mean(), df['whatsapp_neighbor'].mean(),
    df['whatsapp_otherfamily'].mean(), df['whatsapp_romanticpartner'].mean(),
    df['whatsapp_parent'].mean(), df['whatsapp_stepparent'].mean(), df['whatsapp_sibling'].mean(), df['whatsapp_stepsibling'].mean(),df['whatsapp_blank'].mean()
]

# Create and display the Sankey diagram
fig = go.Figure(data=[go.Sankey(
    node=dict(
        pad=15,
        thickness=20,
        line=dict(color='black', width=0.5),
        label=labels
    ),
    link=dict(
        source=source,
        target=target,
        value=value
    ))])

fig.update_layout(
    title_text='Message Communication Within 3 Hours Before Sleep',
    title_font_size=18,
    title_x=0.5,  # Centers the title
    font_size=14,
    width=1000,
    height=750,
    paper_bgcolor='white',
    plot_bgcolor='white',
    margin=dict(l=30, r=30, t=30, b=30)  # Adjust margins (left, right, top, bottom)
)
fig.show()
```

## Look Up With Limitation to 1 Neighbor

The following figure shows the categories of messages (SMS, MMS and WhatsApp) with **look up limited to closest one wave** of surveys three hours prior to sleep. We observe that messages with unidentified contacts decreased from **10.83** to **8.27.** The categories of identified contacts increased correspondingly.

```{python}
#| echo: false
#| warning: false
#| output: true
df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/OneDrive-Personal/Nethealth/Data/CNSA/combine/7/df7_3hr_br1.csv")
import plotly.graph_objs as go
# Combine and format labels with their mean values for each category
# Close Degree labels with their means
labels_close_degree = [
    f'Especially Close: {df["especiallyclose_m"].mean():.2f}',
    f'Merely Close: {df["merelyclose_m"].mean():.2f}',
    f'Less Than Close: {df["lessthanclose_m"].mean():.2f}',
    f'Distant: {df["distant_m"].mean():.2f}',
    f'Close Unknown: {df["close_unknown_m"].mean():.2f}'
]

# Message Type labels with their means
labels_message_type = [
    f'SMS: {df["sms"].mean():.2f}',
    f'MMS: {df["mms"].mean():.2f}',
    f'WhatsApp: {df["whatsapp"].mean():.2f}'
]

# Contact Type labels with their means
labels_contact_type = [
    f'Acquaintance: {df["acquaintance_m"].mean():.2f}',
    f'Co-member Organization: {df["comemberorganization_m"].mean():.2f}',
    f'Coworker: {df["coworker_m"].mean():.2f}',
    f'Friend: {df["friend_m"].mean():.2f}',
    f'Neighbor: {df["neighbor_m"].mean():.2f}',
    f'Other Family: {df["otherfamily_m"].mean():.2f}',
    f'Romantic: {df["romantic_m"].mean():.2f}',
    f'Parent: {df["parent_m"].mean():.2f}',
    f'Step Parent: {df["stepparent_m"].mean():.2f}',
    f'Sibling: {df["sibling_m"].mean():.2f}',
    f'Step Sibling: {df["stepsibling_m"].mean():.2f}',
    f'Relation Unknown: {df["rela_unknown_m"].mean():.2f}'
]

# Combine all labels for nodes
labels = labels_close_degree + labels_message_type + labels_contact_type

# Initialize the lists for the source, target, and value arrays for the Sankey diagram
source = [
    # Close Degree to Message Type
    0, 0, 0,  # Especially Close to SMS, MMS, WhatsApp
    1, 1, 1,  # Merely Close to SMS, MMS, WhatsApp
    2, 2, 2,  # Less Than Close to SMS, MMS, WhatsApp
    3, 3, 3,  # Distant to SMS, MMS, WhatsApp
    4, 4, 4   # Close Unknown to SMS, MMS, WhatsApp
] + [
    # Message Type to Contact Type
    5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5,  # SMS to all contact types
    6, 6, 6, 6, 6, 6, 6, 6, 6, 6, 6, 6,  # MMS to all contact types
    7, 7, 7, 7, 7, 7, 7, 7, 7, 7, 7, 7   # WhatsApp to all contact types
]

target = [
    # Close Degree to Message Type
    5, 6, 7,  # Especially Close to SMS, MMS, WhatsApp
    5, 6, 7,  # Merely Close to SMS, MMS, WhatsApp
    5, 6, 7,  # Less Than Close to SMS, MMS, WhatsApp
    5, 6, 7,  # Distant to SMS, MMS, WhatsApp
    5, 6, 7   # Close Unknown to SMS, MMS, WhatsApp
] + [
    # Message Type to Contact Type
    8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19,  # SMS to all contact types
    8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19,  # MMS to all contact types
    8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19   # WhatsApp to all contact types
]

# Values for all connections (assuming you have these means calculated correctly in your DataFrame)
#Judge if any of the following columns are not in the dataframe, create them and fill them with 0
for col in ['sms_acquaintance', 'sms_comemberorganization', 'sms_coworker', 'sms_friend', 'sms_neighbor', 'sms_otherfamily', 'sms_romanticpartner', 'sms_parent', 'sms_stepparent', 'sms_sibling', 'sms_stepsibling', 'sms_blank', 'mms_acquaintance', 'mms_comemberorganization', 'mms_coworker', 'mms_friend', 'mms_neighbor', 'mms_otherfamily', 'mms_romanticpartner', 'mms_parent', 'mms_stepparent', 'mms_sibling', 'mms_stepsibling', 'mms_blank', 'whatsapp_acquaintance', 'whatsapp_comemberorganization', 'whatsapp_coworker', 'whatsapp_friend', 'whatsapp_neighbor', 'whatsapp_otherfamily', 'whatsapp_romanticpartner', 'whatsapp_parent', 'whatsapp_stepparent', 'whatsapp_sibling', 'whatsapp_stepsibling', 'whatsapp_blank']:
    if col not in df.columns:
        df[col] = 0
value = [
    # Close Degree to Message Type values
    df['sms_especiallyclose'].mean(), df['mms_especiallyclose'].mean(), df['whatsapp_especiallyclose'].mean(),
    df['sms_merelyclose'].mean(), df['mms_merelyclose'].mean(), df['whatsapp_merelyclose'].mean(),
    df['sms_lessthanclose'].mean(), df['mms_lessthanclose'].mean(), df['whatsapp_lessthanclose'].mean(),
    df['sms_distant'].mean(), df['mms_distant'].mean(), df['whatsapp_distant'].mean(),
    df['sms_blank'].mean(), df['mms_blank'].mean(), df['whatsapp_blank'].mean()
] + [

    df['sms_acquaintance'].mean(), df['sms_comemberorganization'].mean(), df['sms_coworker'].mean(), df['sms_friend'].mean(),
    df['sms_neighbor'].mean(), df['sms_otherfamily'].mean(), df['sms_romanticpartner'].mean(), df['sms_parent'].mean(),
    df['sms_stepparent'].mean(), df['sms_sibling'].mean(), df['sms_stepsibling'].mean(), df['sms_blank'].mean(),
    df['mms_acquaintance'].mean(), df['mms_comemberorganization'].mean(), df['mms_coworker'].mean(), df['mms_friend'].mean(),
    df['mms_neighbor'].mean(), df['mms_otherfamily'].mean(), df['mms_romanticpartner'].mean(), df['mms_parent'].mean(),
    df['mms_stepparent'].mean(), df['mms_sibling'].mean(), df['mms_stepsibling'].mean(), df['mms_blank'].mean(),
    df['whatsapp_acquaintance'].mean(), df['whatsapp_comemberorganization'].mean(),df['whatsapp_coworker'].mean(), df['whatsapp_friend'].mean(), df['whatsapp_neighbor'].mean(),
    df['whatsapp_otherfamily'].mean(), df['whatsapp_romanticpartner'].mean(),
    df['whatsapp_parent'].mean(), df['whatsapp_stepparent'].mean(), df['whatsapp_sibling'].mean(), df['whatsapp_stepsibling'].mean(),df['whatsapp_blank'].mean()
]

# Create and display the Sankey diagram
fig = go.Figure(data=[go.Sankey(
    node=dict(
        pad=15,
        thickness=20,
        line=dict(color='black', width=0.5),
        label=labels
    ),
    link=dict(
        source=source,
        target=target,
        value=value
    ))])

fig.update_layout(
    title_text='Message Communication Within 3 Hours Before Sleep (Neighbor 1 Network)',
    title_font_size=18,
    title_x=0.5,  # Centers the title
    font_size=14,
    width=1000,
    height=750,
    paper_bgcolor='white',
    plot_bgcolor='white',
    margin=dict(l=30, r=30, t=30, b=30)  # Adjust margins (left, right, top, bottom)
)
fig.show()
```

## Look Up With Full Network

The following figure shows the categories of messages (SMS, MMS and WhatsApp) with look up in **full** social network surveys three hours prior to sleep. We observe that messages with unidentified contacts further decreased from **8.27** to **6.73.** The categories of identified contacts increased correspondingly.

```{python}
#| echo: false
#| warning: false
#| output: true
df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/OneDrive-Personal/Nethealth/Data/CNSA/combine/7/df7_3hr_full.csv")
import plotly.graph_objs as go
# Combine and format labels with their mean values for each category
# Close Degree labels with their means
labels_close_degree = [
    f'Especially Close: {df["especiallyclose_m"].mean():.2f}',
    f'Merely Close: {df["merelyclose_m"].mean():.2f}',
    f'Less Than Close: {df["lessthanclose_m"].mean():.2f}',
    f'Distant: {df["distant_m"].mean():.2f}',
    f'Close Unknown: {df["close_unknown_m"].mean():.2f}'
]

# Message Type labels with their means
labels_message_type = [
    f'SMS: {df["sms"].mean():.2f}',
    f'MMS: {df["mms"].mean():.2f}',
    f'WhatsApp: {df["whatsapp"].mean():.2f}'
]

# Contact Type labels with their means
labels_contact_type = [
    f'Acquaintance: {df["acquaintance_m"].mean():.2f}',
    f'Co-member Organization: {df["comemberorganization_m"].mean():.2f}',
    f'Coworker: {df["coworker_m"].mean():.2f}',
    f'Friend: {df["friend_m"].mean():.2f}',
    f'Neighbor: {df["neighbor_m"].mean():.2f}',
    f'Other Family: {df["otherfamily_m"].mean():.2f}',
    f'Romantic: {df["romantic_m"].mean():.2f}',
    f'Parent: {df["parent_m"].mean():.2f}',
    f'Step Parent: {df["stepparent_m"].mean():.2f}',
    f'Sibling: {df["sibling_m"].mean():.2f}',
    f'Step Sibling: {df["stepsibling_m"].mean():.2f}',
    f'Relation Unknown: {df["rela_unknown_m"].mean():.2f}'
]

# Combine all labels for nodes
labels = labels_close_degree + labels_message_type + labels_contact_type

# Initialize the lists for the source, target, and value arrays for the Sankey diagram
source = [
    # Close Degree to Message Type
    0, 0, 0,  # Especially Close to SMS, MMS, WhatsApp
    1, 1, 1,  # Merely Close to SMS, MMS, WhatsApp
    2, 2, 2,  # Less Than Close to SMS, MMS, WhatsApp
    3, 3, 3,  # Distant to SMS, MMS, WhatsApp
    4, 4, 4   # Close Unknown to SMS, MMS, WhatsApp
] + [
    # Message Type to Contact Type
    5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5,  # SMS to all contact types
    6, 6, 6, 6, 6, 6, 6, 6, 6, 6, 6, 6,  # MMS to all contact types
    7, 7, 7, 7, 7, 7, 7, 7, 7, 7, 7, 7   # WhatsApp to all contact types
]

target = [
    # Close Degree to Message Type
    5, 6, 7,  # Especially Close to SMS, MMS, WhatsApp
    5, 6, 7,  # Merely Close to SMS, MMS, WhatsApp
    5, 6, 7,  # Less Than Close to SMS, MMS, WhatsApp
    5, 6, 7,  # Distant to SMS, MMS, WhatsApp
    5, 6, 7   # Close Unknown to SMS, MMS, WhatsApp
] + [
    # Message Type to Contact Type
    8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19,  # SMS to all contact types
    8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19,  # MMS to all contact types
    8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19   # WhatsApp to all contact types
]

# Values for all connections (assuming you have these means calculated correctly in your DataFrame)
#Judge if any of the following columns are not in the dataframe, create them and fill them with 0
for col in ['sms_acquaintance', 'sms_comemberorganization', 'sms_coworker', 'sms_friend', 'sms_neighbor', 'sms_otherfamily', 'sms_romanticpartner', 'sms_parent', 'sms_stepparent', 'sms_sibling', 'sms_stepsibling', 'sms_blank', 'mms_acquaintance', 'mms_comemberorganization', 'mms_coworker', 'mms_friend', 'mms_neighbor', 'mms_otherfamily', 'mms_romanticpartner', 'mms_parent', 'mms_stepparent', 'mms_sibling', 'mms_stepsibling', 'mms_blank', 'whatsapp_acquaintance', 'whatsapp_comemberorganization', 'whatsapp_coworker', 'whatsapp_friend', 'whatsapp_neighbor', 'whatsapp_otherfamily', 'whatsapp_romanticpartner', 'whatsapp_parent', 'whatsapp_stepparent', 'whatsapp_sibling', 'whatsapp_stepsibling', 'whatsapp_blank']:
    if col not in df.columns:
        df[col] = 0
value = [
    # Close Degree to Message Type values
    df['sms_especiallyclose'].mean(), df['mms_especiallyclose'].mean(), df['whatsapp_especiallyclose'].mean(),
    df['sms_merelyclose'].mean(), df['mms_merelyclose'].mean(), df['whatsapp_merelyclose'].mean(),
    df['sms_lessthanclose'].mean(), df['mms_lessthanclose'].mean(), df['whatsapp_lessthanclose'].mean(),
    df['sms_distant'].mean(), df['mms_distant'].mean(), df['whatsapp_distant'].mean(),
    df['sms_blank'].mean(), df['mms_blank'].mean(), df['whatsapp_blank'].mean()
] + [

    df['sms_acquaintance'].mean(), df['sms_comemberorganization'].mean(), df['sms_coworker'].mean(), df['sms_friend'].mean(),
    df['sms_neighbor'].mean(), df['sms_otherfamily'].mean(), df['sms_romanticpartner'].mean(), df['sms_parent'].mean(),
    df['sms_stepparent'].mean(), df['sms_sibling'].mean(), df['sms_stepsibling'].mean(), df['sms_blank'].mean(),
    df['mms_acquaintance'].mean(), df['mms_comemberorganization'].mean(), df['mms_coworker'].mean(), df['mms_friend'].mean(),
    df['mms_neighbor'].mean(), df['mms_otherfamily'].mean(), df['mms_romanticpartner'].mean(), df['mms_parent'].mean(),
    df['mms_stepparent'].mean(), df['mms_sibling'].mean(), df['mms_stepsibling'].mean(), df['mms_blank'].mean(),
    df['whatsapp_acquaintance'].mean(), df['whatsapp_comemberorganization'].mean(),df['whatsapp_coworker'].mean(), df['whatsapp_friend'].mean(), df['whatsapp_neighbor'].mean(),
    df['whatsapp_otherfamily'].mean(), df['whatsapp_romanticpartner'].mean(),
    df['whatsapp_parent'].mean(), df['whatsapp_stepparent'].mean(), df['whatsapp_sibling'].mean(), df['whatsapp_stepsibling'].mean(),df['whatsapp_blank'].mean()
]

# Create and display the Sankey diagram
fig = go.Figure(data=[go.Sankey(
    node=dict(
        pad=15,
        thickness=20,
        line=dict(color='black', width=0.5),
        label=labels
    ),
    link=dict(
        source=source,
        target=target,
        value=value
    ))])
fig.update_layout(
    title_text='Message Communication Within 3 Hours Before Sleep (Full Network)',
    title_font_size=18,
    title_x=0.5,  # Centers the title
    font_size=14,
    width=1000,
    height=750,
    paper_bgcolor='white',
    plot_bgcolor='white',
    margin=dict(l=30, r=30, t=30, b=30)  # Adjust margins (left, right, top, bottom)
)
fig.show()
```

## Estimation Results with Different Lookup Scopes

In this section, we show the estimation results with different lookup scopes.

### Main Results without Lookup (3 Hrs)

![Impact of Smartphone Use On Sleep Debt without Lookup (3 Hrs)](images/original.png){fig-align="center"}

### Main Results with Lookup in Neighbor 1 Network (3 Hrs)

![Impact of Smartphone Use On Sleep Debt with Lookup in Neighbor 1 Network (3 Hrs)](images/neighbor1.png){fig-align="center"}

### Main Results with Lookup in Full Network (3 Hrs)

![Impact of Smartphone Use On Sleep Debt with Lookup in Full Network (3 Hrs)](images/full.png){fig-align="center"}

In general, we find that the estimation results are generally consistent across different lookup strategies.

### 2025-01-05 posts.qmd
Research blog moving

@@
 title: "Project Blog"
-listing: 
-  contents: posts # all Quarto docs in the `posts` directory will be included on your listing page
-  type: grid # or `default` or `table`; each type has its own set of yaml options to include
-  sort: 
-      - "date-modified desc" # can also sort on more than one field
-      - "date desc"
-  categories: true # allows you to sort posts by assigned categories
-  sort-ui: [date-modified, title]
-  fields: [image, date-modified, title, description, date, author]
-  page-size: 6
-format:
-  html:
-    css: styles2.css
-class: custom-font-pos
+
 website:
@@
   image: Horizontal_VT_Full_Color_RGB.png
-
   sidebar:

### 2025-01-05 posts.qmd
(ProjectBlog/paper2.qmd)

@@
 title: "Project Blog"
-
+listing: 
+  contents: posts # all Quarto docs in the `posts` directory will be included on your listing page
+  type: grid # or `default` or `table`; each type has its own set of yaml options to include
+  sort: 
+      - "date-modified desc" # can also sort on more than one field
+      - "date desc"
+  categories: true # allows you to sort posts by assigned categories
+  sort-ui: [date-modified, title]
+  fields: [image, date-modified, title, description, date, author]
+  page-size: 6
+format:
+  html:
+    css: styles2.css
+class: custom-font-pos
 website:

### 2025-01-05 ProjectBlog/paper2.qmd
paper 1 and 2 exchange

---
title: "Smartphone Use, Social Support, and Sleep Health"
listing: 
  contents: paper2 # all Quarto docs in the `posts` directory will be included on your listing page
  type: grid # or `default` or `table`; each type has its own set of yaml options to include
  sort: 
      - "date-modified desc" # can also sort on more than one field
      - "date desc"
  categories: false # allows you to sort posts by assigned categories
  sort-ui: [date-modified, title]
  fields: [image, date-modified, title, description, date, author]
  page-size: 6
format:
  html:
    css: styles2.css
class: custom-font-pos
website:
  favicon: Virginia_Tech_seal.svg.png
  image: Horizontal_VT_Full_Color_RGB.png
  sidebar:
    tools:
      - icon: github
        href: https://github.com/Shaokang-Yang
      - icon: linkedin
        href: https://www.linkedin.com/in/shaokang-y-52b633162/
    section: true
    contents:
      - href: index.qmd
        text: Home
      - research.qmd
      - teaching.qmd
      - posts.qmd
---

### 2025-01-06 posts/Meidation/.vdoc.py
delete posts

@@ -1,194 +1,0 @@
-# type: ignore
-# flake8: noqa
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| echo: false
-#| warning: false
-#| output: false
-import time;import pandas as pd;import numpy as np ;import datetime
-from datetime import datetime;from datetime import timedelta;import stata_setup
-stata_setup.config('/Applications/Stata', 'mp')
-#
-#
-#
-#
-#
-#| echo: true
-#| warning: false
-#| output: false
-#| code-fold: false
-#| code-overflow: wrap
-%%stata
-
-clear all
-set maxvar 120000, permanently
-set more off
-
-import delimited "/Users/shaokangyang/Library/CloudStorage/GoogleDrive-shaokang@vt.edu/My Drive/Nethealth/Data/CNSA/combine/7/df7_22-5.csv"
-gen date2 = date(date, "YMD")
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#

### 2025-01-06 ProjectBlog/paper1/Hypotheses/hypo.qmd
delete posts

---
title: "Review for Production and Operations Management(2024)"
date: 09/16/2024
date-modified: last-modified
date-format: full
categories: [Others]
#image: "search.png"
tbl-colwidths: [5,50,75]
format: 
  html:
    page-layout: full
---

# Review for Production and Operations Management(2024)

The latest review report for the manuscript **Breaking Barriers: Improving Patient Adherence to Appointments and Provider Productivity through Telehealth(POM-Jul-24-OA-1071)** is as follows:

<iframe src="pdfs/Reviewer_Report_POM_2024.pdf" style="width:100%; height:1500px;" frameborder="0">

</iframe>

### 2025-01-06 posts/Abortion/abortion.qmd
delete posts

--- 2024-11-11 posts/Abortion/abortion.qmd
@@
 date-modified: last-modified
+draft: true
 date-format: full

### 2025-01-06 posts/Meidation/Mediation.qmd
delete posts

---
title: "Causal Inference"
date: 01/08/2024
date-modified: last-modified
date-format: full
categories: [Paper1]
format:
  html:
    code-overflow: wrap
bibliography: references.bib
---

# Causal Mediation Analysis Based on Two-way Fixed Effects Model

Since we find the screen time has a U-shape impact on sleep debt, we may wonder what mechanisms behind it. The following figure implies that sleep debt may have a reverse shape of sleep debt. Therefore, we may want to explore whether the U-Shape of sleep debt is caused by the reverse U-shape of message.

![](images/paste-10.png){fig-align="center"}

First of all, one may be concered the rise of sleep debt after turning point may be driven by the potential outliers in the last two bars (screen time \> 80 minutes). However, whether these observations are outliers cannot be determined solely by their proportion of the total dataset. We have 506 unique participants in our final data set. There are **353 (69.76% of total participants)** unique participants whose screen time has ever been greater than 80 minutes; **293 (57.91% of total participants)**participants whose screen time has ever been greater than 85 minutes. It suggests that a large proportion of participants contributed to the data of last two bars. This might mean that those observations are not anomalies but a representation of a segment of the population, which reflects the inherent nature of the data [@osborne]. Moreover, the U-shape persists in all the variations of measurement window:

![](images/9main-2.png){fig-align="center"}

The above figure suggest that the U-shape always **converge** in the predictive models over the variation of measurement windows. Therefore, we believe those observations reflects the real-world variability. Maintaining outliers can sometimes contribute to the integrity and reliability of research findings​[@bakker2014].

Causal mediation analysis can help us to understand how an independent variable (IV) affects a dependent variable (DV) through a mediator variable (MV).

![Meiation Effect of Message](images/mediation-6.png){fig-align="center"}

![](images/paste-5.png){fig-align="center"}

```{python}
#| echo: false
#| warning: false
#| output: false
import time;import pandas as pd;import numpy as np ;import datetime
from datetime import datetime;from datetime import timedelta;import stata_setup
stata_setup.config('/Applications/Stata', 'mp')
```

### Import Dataset

```{python}
#| echo: true
#| warning: false
#| output: false
#| code-fold: false
#| code-overflow: wrap
%%stata

clear all
set maxvar 120000, permanently
set more off

import delimited "/Users/shaokangyang/Library/CloudStorage/GoogleDrive-sky.ang510@gmail.com/My Drive/Nethealth/Data/CNSA/combine/7/df7_22-5.csv"
gen date2 = date(date, "YMD")
```

### Caual mediation analysis

``` python
#| echo: true
#| warning: false
#| output: false
#| code-overflow: wrap
%%stata

sgmediation2 sleep_debt, iv(screen_time) mv(message_q) cv(i.egoid i.date2 unlock call bytes length duration steps100 floors meanrate calorie_sum sedentaryminutes lightlyactiveminutes fairlyactiveminutes veryactiveminutes light_exposure  insession#weekday#time_wakeuphour i.studyweeks)
```

## Sobel-Goodman Mediation Tests

-   **Sobel, Aroian, Goodman Tests**: All three tests show a significant mediation effect. The estimates are -0.015 with very small standard errors, and the z-values are large with p-values of 0.000, indicating a highly significant mediation effect.

###

## Before turning point

![](images/paste-9.png){fig-align="center"}

###

![](images/mediation%20-%20before-3.png){fig-align="center"}

### Interpretation:

1.  **Mediator (Message) Model:** Message=⍺+0.014×Screen Time+ϵ1​

    -   For every unit increase in screen time, message increases by 0.014 units, assuming message is quantifiable. This relationship is highly significant (p \< 0.001).

2.  **Dependent Variable (Sleep Debt) Model:** Sleep Debt=𝛃−0.730×Screen Time−1.149×Message+ϵ2

    -   Screen time has a significant negative direct effect on sleep debt (-0.730), suggesting that increased screen time reduces sleep debt.

    -   Message also has a significant negative effect on sleep debt (-1.149), indicating that higher message is associated with reduced sleep debt.

    -   These effects are statistically significant (p \< 0.001).

3.  **Total Effect of Screen Time on Sleep Debt:** Sleep Debt=𝛄−0.746×Screen Time+ϵ3​

    -   The total effect of screen time on sleep debt is significant and negative (-0.746), indicating that increased screen time is associated with reduced sleep debt overall.

4.  **Mediation Analysis:**

    -   The indirect effect of screen time on sleep debt through message is -0.016 (a \* b), and it's significant (p \< 0.001). This suggests that part of the effect of screen time on sleep debt operates through its impact on message frequency. Although the impact on the message is relatively small (0.014), since the message is measured in quartiles, it still could have a big impact.

    -   The proportion of the total effect that is mediated (approx. 2.2%) indicates that a small but significant portion of the relationship between screen time and sleep debt is explained by message frequency.

5.  **Summary:**

    -   Increased screen time is associated with both increased message and reduced sleep debt.

    -   The direct effect of screen time on sleep debt is strong and negative, meaning screen time directly contributes to reducing sleep debt.

    -   There is a significant but small mediation effect through message frequency, suggesting that part of the way screen time affects sleep debt is by influencing message frequency.

    -   Overall, the total effect of screen time on sleep debt, considering both direct and indirect pathways, is significant and negative.

## After turning point

![](images/paste-7.png){fig-align="center"}

![](images/mediation%20-%20after-5.png){fig-align="center"}

### **Sobel-Goodman Mediation Tests**

1.  **Indirect, Direct, and Total Effects:**

    -   **a_coefficient (Effect of IV on MV):** The effect of the independent variable on the mediator is -0.001, which is not statistically significant (p = 0.209).

    -   **b_coefficient (Effect of MV on DV):** The effect of the mediator on the dependent variable is -2.531 and is statistically significant (p \< 0.001).

    -   **Indirect_effect_aXb (Mediation Effect):** The indirect effect, calculated as the product of a and b coefficients, is 0.003 but not statistically significant (p = 0.220).

    -   **Direct_effect_c' (Direct Effect of IV on DV):** The direct effect of the independent variable on the dependent variable is 0.310, which is significant (p \< 0.001).

    -   **Total_effect_c (Total Effect of IV on DV):** The total effect is 0.313, also significant (p \< 0.001).

2.  **Proportions and Ratios:**

    -   **Proportion of total effect that is mediated:** About 0.9% of the total effect is mediated, which is quite small.

    -   **Ratio of indirect to direct effect:** The indirect effect is approximately 0.9% of the direct effect.

    -   **Ratio of total to direct effect:** The total effect is 1.009 times the direct effect.

### **Interpretation:**

-   **Mediation Effect:** The results suggest that the mediation effect in the model is not statistically significant. This implies that the relationship between the independent and dependent variables is not significantly channeled through the mediator.

-   **Direct Effect:** The direct relationship between the independent variable and the dependent variable is significant and represents the main pathway of influence.

-   **Total Effect:** The overall effect of the independent variable on the dependent variable is significant, predominantly driven by the direct pathway.

-   Messages still help reduce sleep debt **(-2.531\*\*\*),** but the mediation effect is not significant anymore because the channel from screen time to message is cut off (**not significant**). This is a bit different from our earlier results since the interaction term (screen time \* message) earlier suggests that their combination could negatively impact sleep debt.

-   **Mediation Proportion:** The small proportion of mediation suggests that the mediator plays a negligible role in the relationship between the independent and dependent variables in this particular analysis.

### Outlier Handling

According to the **1.5 IQR rule**, observations with messages \> 20 or unlocks \> 23.5 should be taken as outliers. Therefore, I take 20 as the message frequency for those that are greater than 20. Similarly, I take 23.5 as unlocking outliers' values.

![](images/paste-13.png){fig-align="center"}

![](images/mediation%20-%20after%20outlier-3.png){fig-align="center"}

### **Indirect, Direct, and Total Effects**

-   **a_coefficient**: The effect of the independent variable on the mediator is significant (Est = 0.019, p \< 0.001).

-   **b_coefficient**: The effect of the mediator on the dependent variable, controlling for the independent variable, is also significant (Est = -0.454, p \< 0.001).

-   **Indirect_effect_aXb**: The estimated indirect effect is -0.009, which is significant (p = 0.003). This suggests that the mediator carries some of the influence of the independent variable to the dependent variable.

-   **Direct_effect_c'**: The direct effect of the independent variable on the dependent variable is significant and positive (Est = 0.308, p \< 0.001).

-   **Total_effect_c**: The total effect (considering both direct and mediated pathways) is also significant (Est = 0.299, p \< 0.001).

### **Proportions and Ratios**

-   **Proportion of total effect that is mediated**: -0.029. This negative value is somewhat unusual in mediation analysis. It suggests that the indirect effect works in the opposite direction to the total effect.

-   **Ratio of indirect to direct effect**: -0.029, indicating that the magnitude of the indirect effect is small compared to the direct effect.

-   **Ratio of total to direct effect**: 0.971, suggesting that the majority of the total effect is due to the direct effect.

### **Overall Interpretation**

-   The mediation effect in the model is statistically significant, but its impact is relatively small compared to the direct effect of the independent variable on the dependent variable.

-   The negative value for the proportion of the total effect that is mediated indicates a complex relationship between the variables, potentially involving suppression effects or other intricate dynamics in the model. It could suggest that while the mediator transmits some of the influence, it does so in a way that partially offsets or reduces the total effect of the independent variable on the dependent variable. This warrants a closer examination of the nature of the variables and their interactions.

### 2025-01-06 posts/Paper 1/paper1.qmd
delete posts

---
title: "Smartphone Use, Social Support, and Sleep Health"
date: 10/09/2023
date-modified: last-modified
date-format: full
categories: [Paper1]
image: "Go2Bed-02.png"
format: revealjs
---

## Falling Asleep Hours Distribution

![](images/Go2Bed-02.png){fig-align="center"}

Normal Sleep: fall asleep from 22 pm to 6 am. (**95.99** % of Total.)

## Falling Wake Hours Distribution

![](images/wake.png){fig-align="center"}

## Interaction of Time terms

::: incremental
-   **Insession** x **Day of Week** x **Go2Bed Hour**:\
    1 x 5 x 2: [2 am on Friday of a Semester]{.underline}
-   Abnormal Screen Time Threshold: 12 -\> 3.5 hours
-   Screen time as control: We focus on **Technology** impact under the influence of **Human** factors
:::

## Conclusion

::: incremental
-   Social interaction via smartphone can **benefit** sleep quality
-   Interaction with **close** contacts prolong sleep
-   Interaction with certain **relationships** of contacts (e.g. family) prolong sleep
:::

## Moderating Impact: The Way of Interaction

::: incremental
-   Message: **Positive** moderation
-   Call: Depends on the **relationship** and **closeness**
:::

## Result 1: Social Closeness via Message

![](images/MsgClose.png){fig-align="center"}

## Result 2: Social Closeness via Call

![](images/Close_Cal.png){fig-align="center"}

## Result 3: Relationship via Message

![](images/Rel_Msg.png){fig-align="center"}

## Result 4: Relationship via Call

![](images/Rel_Cal.png)

## Result 5: Pre-Sleep Communication benefit Sleep Quality

![](images/ComCM.png){fig-align="center"}

### 2025-01-06 teaching.qmd
delete posts

---
title: "Teaching"
format:
  html:
    css: styles2.css
class: custom-font-pos
---

### 2025-01-06 posts/Mediation Effect of Steps/.vdoc.py

@@ -1,0 +1,58 @@
+# type: ignore
+# flake8: noqa
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| echo: false
+#| warning: false
+#| output: false
+import time;import pandas as pd;import numpy as np;import datetime
+from datetime import datetime;from datetime import timedelta;import sqlite3
+import warnings;warnings.filterwarnings('ignore')
+vt=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/OneDrive-Personal/Nethealth/Data/overlap_rate.csv")
+#
+#
+#
+#
+#| echo: false
+#| warning: false
+#| output: true
+vt10237=vt[vt['egoid']==10237]
+cols = list(vt.columns)
+# Move the 'egoid' column to the start of the list
+cols.insert(0, cols.pop(cols.index('egoid')))
+# Reindex the DataFrame with the new column order
+vt10237 = vt10237.reindex(columns=cols)
+# Display the DataFrame
+vt10237
+#
+#
+#
+#| echo: false
+#| warning: false
+#| output: true
+cols = list(vt.columns)
+# Move the 'egoid' column to the start of the list
+cols.insert(0, cols.pop(cols.index('egoid')))
+# Reindex the DataFrame with the new column order
+vt = vt.reindex(columns=cols)
+# Display the DataFrame
+#
+#
+#

### 2025-01-06 ProjectBlog/paper2/Mediation Effect of Steps/.vdoc.py
abortion

@@ -1,58 +1,0 @@
-# type: ignore
-# flake8: noqa
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| echo: false
-#| warning: false
-#| output: false
-import time;import pandas as pd;import numpy as np;import datetime
-from datetime import datetime;from datetime import timedelta;import sqlite3
-import warnings;warnings.filterwarnings('ignore')
-vt=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/OneDrive-Personal/Nethealth/Data/overlap_rate.csv")
-#
-#
-#
-#
-#| echo: false
-#| warning: false
-#| output: true
-vt10237=vt[vt['egoid']==10237]
-cols = list(vt.columns)
-# Move the 'egoid' column to the start of the list
-cols.insert(0, cols.pop(cols.index('egoid')))
-# Reindex the DataFrame with the new column order
-vt10237 = vt10237.reindex(columns=cols)
-# Display the DataFrame
-vt10237
-#
-#
-#
-#| echo: false
-#| warning: false
-#| output: true
-cols = list(vt.columns)
-# Move the 'egoid' column to the start of the list
-cols.insert(0, cols.pop(cols.index('egoid')))
-# Reindex the DataFrame with the new column order
-vt = vt.reindex(columns=cols)
-# Display the DataFrame
-#
-#
-#

### 2025-01-06 posts/IV/.vdoc.py

@@ -1,173 +1,0 @@
-# type: ignore
-# flake8: noqa
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| echo: false
-#| warning: false
-#| output: true
-import time;import pandas as pd;import numpy as np;import datetime
-from datetime import datetime;from datetime import timedelta;import sqlite3;import warnings
-import matplotlib.pyplot as plt;import seaborn as sns;warnings.filterwarnings('ignore')
-
-df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/OneDrive-Personal/Nethealth/Data/CNSA/combine/7/bt7_1.5r.csv")
-
-df[['egoid','count_begin90', 'time_fallsleep','battery','battery_time','charging','binterval']]
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| echo: false
-#| warning: false
-#| output: true
-
-df[['egoid','count_begin90', 'time_fallsleep','battery','charging','battery_time','binterval']].describe()
-#
-#
-#
-#
-#
-#
-#
-#| echo: false
-#| warning: false
-#| output: true
-df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/OneDrive-Personal/Nethealth/Data/CNSA/combine/7/df7_22-5s.csv")
-df[['egoid','screen_time', 'unlock','message','count_begin90', 'time_fallsleep','battery','charging','battery_time','binterval']].describe()
-#
-#
-#
-#
-#
-#| echo: false
-#| warning: false
-#| output: true
-df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/OneDrive-Personal/Nethealth/Data/CNSA/combine/7/df7_22-5b.csv")
-df[['egoid','screen_time', 'unlock','message','count_begin90', 'time_fallsleep','battery','charging','battery_time','binterval']].describe()
-#
-#
-#
-#| echo: false
-#| warning: false
-#| output: false
-import time;import pandas as pd;import numpy as np ;import datetime
-from datetime import datetime;from datetime import timedelta;import stata_setup
-stata_setup.config('/Applications/Stata', 'mp')
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| echo: false
-#| warning: false
-#| output: false
-#| code-fold: false
-#| code-overflow: wrap
-%%stata
-#| echo: true
-clear all
[…]

### 2025-01-06 posts/Battery levels as IV (3 hours)/batteryIV.qmd
abortion add

---
title: "Instrument Variable for Screen Time"
date: 03/19/2024
date-modified: last-modified
date-format: full
categories: [Paper1]
format:
  html:
    code-overflow: wrap
comments:
  hypothesis: true
#bibliography: references.bib
---

# Social Network Control

![](images/clipboard-3769634593.png){fig-align="center"}

``` python
global id egoid
global t date2
global ylist sleep_debt
global mainIV  c.screen_time##c.screen_time  message_q c.screen_time#c.message_q unlock
global Call_Control call duration_x length bytes
global Fitness_Control steps100 floors sedentaryminutes lightlyactiveminutes fairlyactiveminutes veryactiveminutes lowrangecal100 fatburncal100 cardiocal100 peakcal100
global Network_Control friend_no parent_no  sibling_no  blank_no    otherfamily_no  romanticpartner_no  acquaintance_no neighbor_no coworker_no stepsibling_no  comemberorganization_no stepparent_no degree_centrality core_number trust position num_nodes num_edges duration_y contacts_y
global Other_Control naps naps_dur light_exposure insession##weekday##time_wakeuphour
global fe i.studyweeks

*Set data as panel data
sort $id $t
xtset $id $t

xtreg $ylist  $fe $Fitness_Control $Network_Control $Other_Control $mainIV $Call_Control call, fe robust
outreg2 using 3hour.xls, append dec(5) addtext(Turning Point, Yes) keep($mainIV $Network_Control) title("Impact of Smartphone Use On Sleep Debt")
```

In this update, we try to find an instrument variable to justify the causal effect of screen time on sleep debt. First, we introduce the related variables:

```{python}
#| echo: false
#| warning: false
#| output: true
import time;import pandas as pd;import numpy as np;import datetime
from datetime import datetime;from datetime import timedelta;import sqlite3;import warnings
import matplotlib.pyplot as plt;import seaborn as sns;warnings.filterwarnings('ignore')

df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/OneDrive-Personal/Nethealth/Data/CNSA/combine/7/bt7_3hr.csv")

df[['egoid','count_begin3','battery','battery_time','charging','binterval']]
```

# Instrument Variable for Screen Time
## Charging as Instrument Variable

### Impact of Battery Level on Screen Use

![](images/clipboard-2236990828.png){fig-align="center"}

![](images/clipboard-3667078777.png){fig-align="center"}

![](images/clipboard-3413638920.png){fig-align="center"}

![](images/clipboard-2256328779.png){fig-align="center" width="963"}

![](images/clipboard-617947198.png){fig-align="center"}

The figures show that charging may positively impact screen time. I tried to take charging as IV for screen time, however, the estimated coefficient is not significant, although it passed the relevance test:

Before Turning Point:

![](images/image.png){fig-align="center"}

![](images/image (1).png){fig-align="center"}

After Turning Point:

![](images/image (2).png){fig-align="center"}

![](images/image (3).png){fig-align="center"}

## Battery as Instrument Variable

### Impact of Battery Level on Screen Use

![](images/clipboard-1091683936.png){fig-align="center"}

![](images/clipboard-1091683936.png){fig-align="center"}

#### Visualization of the U-Shape Impact

![](images/battery.png){fig-align="center"}

``` python

clear all
set maxvar 120000, permanently
set more off

import delimited "/Users/shaokangyang/Library/CloudStorage/OneDrive-Personal/Nethealth/Data/CNSA/combine/7/bt7_3hr.csv"
gen date2 = date(date, "YMD")
**********************************************
global id egoid
global t date2
global ylist sleep_debt
global mainIV  c.screen_time##c.screen_time  message_q c.screen_time#c.message_q unlock
global Call_Control call duration_x length bytes
global Fitness_Control steps100 floors sedentaryminutes lightlyactiveminutes fairlyactiveminutes veryactiveminutes lowrangecal100 fatburncal100 cardiocal100 peakcal100
global Network_Control friend_no parent_no  sibling_no  blank_no    otherfamily_no  romanticpartner_no  acquaintance_no neighbor_no coworker_no stepsibling_no  comemberorganization_no stepparent_no degree_centrality core_number trust position num_nodes num_edges duration_y contacts_y
global Other_Control naps naps_dur light_exposure insession##weekday##time_wakeuphour
global fe i.studyweeks

*Set data as panel data
sort $id $t
xtset $id $t

ivreghdfe $ylist $Fitness_Control $Network_Control $Other_Control $Call_Contro message_q unlock charging (c.screen_time##c.screen_time=c.battery##c.battery), absorb(egoid studyweeks) robust endog(screen_time)
```

#### Impact of Screen Time on Sleep Debt

![](images/clipboard-2139860948.png){fig-align="center"}

### Evaluation of IV

![](images/clipboard-3440018871.png){fig-align="center"}

1.  **Underidentification Test (Kleibergen-Paap rk LM Statistic):**

    -   This test checks whether the instruments are correlated with the endogenous regressors—in the case, whether 'battery_levels' is correlated with 'screen_time' and 'screen_time\^2'. A failure to reject the null hypothesis would indicate that the instruments are not relevant, and hence the model is underidentified (meaning t**he IV approach cannot be validly used**).

    -   In the results, the Kleibergen-Paap rk LM statistic is 105.271 with a p-value of 0.0000, indicating strong rejection of the null hypothesis of underidentification. This means the **instruments are likely relevant**.

2.  **Weak Identification Tests (Cragg-Donald Wald F statistic and Kleibergen-Paap rk Wald F statistic):**

    -   These tests check whether the instruments are sufficiently correlated with the endogenous regressors. While the instruments may be correlated (not underidentified), they might not be strong enough to provide reliable estimates (weak instruments).

    -   The critical values provided by Stock and Yogo help determine whether the instruments are weak. If the test statistic (Cragg-Donald or Kleibergen-Paap) is above the critical value for a given maximal IV size (size of a test for a given level of IV bias), **the instruments are not considered weak**.

    -   In the case, the Cragg-Donald Wald F statistic is 57.995, and the Kleibergen-Paap rk Wald F statistic is 52.396. These are both above the highest listed Stock-Yogo critical value of 7.03 for a maximal IV size of 10%. This indicates that the instrument is not weak according to the Stock-Yogo weak identification test standards.

**Interpretation:**

-   The underidentification test indicates that the model is properly identified, meaning that there is a statistical relationship between the instruments and the endogenous variables.

-   The weak identification tests suggest that the **instruments are strong**, as indicated by the test statistics significantly exceeding the Stock-Yogo critical values.

Therefore, based on these diagnostics, it appears that the instrument (battery levels) is both relevant (related to the endogenous variable screen time) and strong (provides sufficient information to estimate the causal effect reliably). This lends credibility to the IV estimates obtained from the model. However, remember that these tests do not address other potential issues such as exogeneity (whether the instruments are correlated with the error term) and overidentification (having more instruments than endogenous variables, which can be tested with a different set of tests). Always consider the theoretical justification for the instruments in addition to these statistical tests.

### Battery IV with Turning Point

#### IV Before Turning Point

![](images/clipboard-769146924.png){fig-align="center"}

![](images/clipboard-1425622386.png){fig-align="center"}

#### IV After Turning Point

# Alternative IVs: Number of Contacts

![](images/clipboard-2448270006.png)

### 2025-01-06 ProjectBlog/others/Abortion/abortion.qmd
abortion add

--- 2025-01-06 posts/Abortion/abortion.qmd
@@
 date-modified: last-modified
-draft: true
+draft: false
 date-format: full

### 2025-01-06 posts/SP2 Review Response/ReviewResponse.qmd
delete project text

---
title: "SP2 Reveiw Response: Social Network Activation: \\The Application in Smartphone Use"
date: 12/23/2023
date-modified: last-modified
date-format: full
categories: [Paper2]
image: "search.png"
tbl-colwidths: [5,50,75]
format: 
  html:
    page-layout: full
bibliography: references.bib
---

We thank Dr.Adjerid, Dr.Liu, and Dr.Lowry for your insightful and valuable feedback and for the opportunity to submit a revision. In addition to highlighting the areas that need to be improved, all of you gave detailed suggestions and intensive oral/written instructions I might take to address the concerns. I sincerely appreciate your constructive comments and advice. The manuscript has been substantially revised in response to the review team's comments. Below I provide an overview of the main changes.

### **\[Development of Motivation\]**

In revising the manuscript, we conduct a comprehensive literature review about social engagement, social network activation, and smartphone overuse, through which we can better identify the practical problems and gaps in the previous literature and clarify the contributions of this study. Specifically, we summarize three major practical and research motivations in the area.

1.  Practical problem. The literature on social engagement and smartphone overuse suggests that lack of social engagement can lead to negative health outcomes. A primary consequence of social isolation that is increasingly popular in life but can be easily neglected is smartphone overuse. It is important to examine how to strategically activate social ties so that smartphone users can improve their social engagement level and reduce the excessive time spent on smartphones.

2.  Research gaps. The research gaps of the study are reflected in the following aspects:

-   Previous research on social engagement has largely focused on the volume of social interaction, such as the number of contacts and the frequency of interactions, little attention has been given to the impact of social network structure or topology on an individual's behavior and well-being.

-   An equally important, but understudied, aspect of social engagement is dynamic evolutions in engagement with different parts of the social network-- the phenomenon termed social network activation. Most social networks in the current literature possess a static and cross-sectional nature, potentially causing them to overlook the intrinsic dynamics in social interactions. We leverage a longitudinal study to meticulously craft a dynamic social network framework. This innovative approach allows us to meticulously trace the progression of individuals' social networks over time, capturing the essence of their evolving connections and interactions.

In addition to the above modification, we introduce and emphasize the technology components in the process of social network activation to make the manuscript fit IS research journals.

### **\[Theorizing and hypothesis development\]**

As suggested by the review team, we conduct a theoretical development for the network features we extracted (degree centrality and K-core), which allows us to develop three hypotheses. Drawing on the three streams of literature on social engagement and smartphone overuse, we first hypothesize that **activating social networks reduces smartphone screen time; the reduction in screen time increases with the number of contacts activated (H1)**. Furthermore, we identify key nodes with high social influence. We infer that contacts with a high degree centrality have a high capacity to motivate social engagement, therefore, our second hypothesis is: **Activating social networks with a higher score of average degree centrality in a social network reduces the time spent on a smartphone (H2)**. Nevertheless, we speculate that degree centrality cannot represent a contact's comprehensive influence in a social network as it may neglect a contact's indirect influence, which is the capacity to form social groups and mobilize other contacts. Thus, we utilize another essential social network feature, "K-core," to measure a contact's social influence by considering the connectivity of the contact as well as the cohesiveness of the group in which the contact exists. Therefore, we propose our third hypothesis: **Activating social networks with a higher average core number score can reduce the time spent on a smartphone (H3)**.

### \[Analysis\]

Our analysis has been improved in several ways. In addition, multiple robustness checks are conducted to validate our estimation results.

1.  We adjust the threshold of activation. In the first version of this manuscript, the activation threshold is communication event \> 0. However, there could be a situation in which the contacts did not respond to the information, which lead to a failed activation. We adjust the activation threshold to ensure a two-way communication (an effective activation) exists between two smartphone users. This eliminates the possibility of one-way communication: one only sends or receives communication information. Overall, the estimation results are mostly consistent with earlier results after the adjustment.

2.  We identified smartphone users who are addicted to smartphones. To the best of my knowledge, there is no quantitative definition of smartphone addiction. We define smartphone addiction based on multiple criteria. Finally, we conduct additional robustness checks to rule out alternative explanations and to check reverse causality. All estimation results show that the increase in core number is associated with a decrease in the likelihood of smartphone addiction.

3.  We conducted a lookup operation to search for the missing contacts’ social network information from the closest neighbors’ social network surveys. We also conducted an alternative lookup approach by searching for the missing contacts backward first and then forward. In both cases, we borrow the missed contacts’ network features from the closest wave that the contact exists. By doing this, we could have a relatively complete social network.  The estimation with an adjusted approach is mostly consistent with earlier estimations.

### **\[Writting\]**

In an effort to increase the readability of the paper, we have overhauled the structure and logic of the paper, tightened the analysis, and checked all the grammatical errors and citations.

::: panel-tabset
## Dr.Idris Adjerid {#sec-dr.idris-adjerid}

Thank you for your valuable comments and feedback. Please refer to the manuscript for the writing update.

+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| No. | Comments                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           | Responses                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |
+=====+====================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================+==============================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================+
| 1   | Does the analysis differ much with and without this approach, could be better as robustness. Could address the issue of up to date social network.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                 | Thank you for your constructive comments. Yes, the analysis with this approach and an alternative approach show similar estimation results. The objective of the approach is to search for the missing contacts' social network information from the closest neighbors' social network surveys. This approach starts from a forward lookup followed by a backward lookup for missed contacts in the current wave of social networks. We also conducted an alternative lookup approach by searching for the missing contacts backward first and then forward, which could work as robustness checks.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     | ![](images/search.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             | ![](images/search%20-%20bf-01.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | In both cases, we borrow the missed contacts' network features from the closest wave that the contact exists. By doing this, we could have a relatively complete social network.  The estimation with an adjusted approach is **mostly consistent** with earlier estimations:                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | ![](images/clipboard-2450557691.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | The results suggest that an increase in core number could lead to a decrease in screen time, which is consistent with the original estimation.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                               |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 2   | *"dynamic social network"*                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         | Thank you for pointing that out. It sill should be noted that there are two levels of social network features in our study:                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     | Actually this definition is not clear. Social networks can be dynamically measured (i.e. they are repeated snapshots). Would these be dynamic? In reality, you are taking a cross-sectional snapshot of a social network and dynamically measuring activation. You actually do not have dynamic social network data.                                                                                                                                                                                                                                                                                                               | 1.  **Individual level**. Contacts' original network features come from the social network survey, therefore, they are updated over the waves of surveys.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | 2.  **Cluster/group level**. Everyday, participants selectively activate a group of individual contacts. The network features of the activated cluster change day by day.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | It is true that individual's social network features evolve survey by survey rather than day by day. Nevertheless, our **independent variables** are the average social network features of the entire **cluster** of contacts that are activated on a certain day. Depending on which contacts are activated, the characteristics of the activated cluster change on daily level. For example, if a participant activate the following contacts on day t:                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                   |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | | Participant | Contacts activated | Date | K-Core (Individual ) | K-Core (Group) |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | |-------------|--------------------|------|----------------------|----------------|                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | | S           | A                  | t    | 5                    | 6              |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | | S           | B                  | t    | 6                    | 6              |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | | S           | C                  | t    | 7                    | 6              |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | The K-core for S on day t is (5+6+7)/3=6. On day t+1, the participant activate the following contacts:                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | | Participant | Contacts activated | Date | K-Core (Individual ) | K-Core (Group) |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | |-------------|--------------------|------|----------------------|----------------|                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | | S           | C                  | t+1  | 7                    | 4              |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | | S           | E                  | t+1  | 2                    | 4              |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | | S           | H                  | t+1  | 3                    | 4              |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | The K-core for S on day t+1 is (7+2+3)/3=4. As we can see, the features of contacts A, B, C, E, H does not change in the current wave of survey. However, the feature of the activated cluster comprised of those contacts sill vary day by day.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | In general, I can feel that the terminology "dynamic social network" could still be controversial or inaccurate, therefore, I have replaced it with "social network" in the manuscript for now.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 3   | *" Moreover, it helps us capture the evolution of one’s contact list and their position in the network over time, which is the common nature of one’s social interaction. "*                                                                                                                                                                                                                                                                                                                                                                                                                                                       |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     | In some sense, the social network measurement is dynamic both in the evolving structure and the activation. These both need to be highlighted and cleanly separated.                                                                                                                                                                                                                                                                                                                                                                                                                                                               |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 4   | *"smartphone addiction"*                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           | Thanks for your correction, since there is no universal or quantitative definition for smartphone addiction, I have used the term "smartphone overuse" to substitute "smartphone addiction" in the manuscript.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                               |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     | Unless we define this (super clearly it could be confusing, we may want to use another, less loaded term (e.g. “phone overuse”                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 5   | *"Our findings reveal that activating contacts who are embraced by the other contacts in one’s social network helps reduce smartphone use. The findings advance the understanding of social engagement from volume to the structure of social networks."*                                                                                                                                                                                                                                                                                                                                                                          | Thanks for your comments.  I modified the statement as follows by adding an explanation of the results:                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     | How to interpret these results is still unclear, need to have a coherent explanation of results and why these would or would not be expected.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      | Our findings reveal that the topology or structure of one's social network impacts individuals' behavior. Specifically, activating contacts embraced by the community of one’s social network **could motivate broader social engagement**, which helps curb smartphone overuse. Our study advances the understanding of social engagement from volume to the structure of social communities.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                               |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 6   | *"......we contextualize the research prob- lems in the context of smartphone addiction, which is an emerging social and technical prob- lem and is broadly thought to be associated with the lack of social engagement."*                                                                                                                                                                                                                                                                                                                                                                                                         | Thank you for your comments. The statement has been corrected as:                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     | Here there is this argument again. I’m not sure what we are saying. At points it sounds like we are saying that smartphone addiction is related to social isolation. Alternatively, social isolation could lead to smartphone overuse, both seem credible but the latter is more sensical for our story so we should be clear about this throughout the paper.                                                                                                                                                                                                                                                                     | "......we narrow down the research questions to smartphone overuse, which is an emerging social and technical problem that is broadly thought to be a consequence of social isolation[@zeng2022]".                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 7   | *" ......we measure a social network member’s core number, which measures how well a contact is connected with other contacts and how active the contact’s community is."*                                                                                                                                                                                                                                                                                                                                                                                                                                                         | Thank you for your thorough advice. I think the following theoretical construct could be related to our study:                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                               |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     | This is crucial and should be more clearly described. What about centrality? There is a key theoretical construct here which is measured in different ways. So we should identify the key construct and how the two measures we have differ (and by extension setting up why they may different effects).                                                                                                                                                                                                                                                                                                                          | 1.  Social influence. The construct reflects the capacity of certain nodes in a social network to affect others' behavior, opinion, and decisions-making process [@izuma2017]. (Social influence. could be a construct for degree centrality and K-Core)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | 2.  Group cohesion. The construct describes to which degree group members are attracted and connected in their group. Group cohesion can be based on shared goals or interests, emotion support, and group pride. Evidence suggests that group cohesion is positively correlated with team performance [@paulus2011]. (The constructs fits better for K-Core)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | I take "social influence" as the theoretical construct for now. The statement is modified as follow:                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | *In addition to the fundamental network metrics such as size and number of edges, we utilize degree centrality and K-core to identify the vital contacts with high social influence in a network that could have the potential to motivate broader social engagement. The former feature captures the degree to which a contact itself is connected to other contacts. Meanwhile, the latter further considers the connectivity degree of the sub-network to which a contact belongs.*                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | I wonder if we should identify one theoretical construct for both degree centrality and K-core. Or, should we use two theoretical constructs for degree centrality and K-core separately.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 8   | *"However, the number of connections of an activated network does not contribute to curbing smartphone use. Moreover, our results suggest that activating contacts in one’s social network can curb smart- phone use."*                                                                                                                                                                                                                                                                                                                                                                                                            | This interpretation is not so clear. Here is the more detailed interpretation of the current results:                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     | These seem like opposite results, are they? Is the first result suggesting that network size does not have an effect? More generally, I wonder if we should kick things off with the more basic measures and then lead into the new more comprehensive measures. The story is that social networks are rich constructs with some simpler measures (number of nodes, size, etc.) and some more advanced measures that capture richer dynamics. Part of the contribution is leaning into the richer context and using real time data reveal more insight compared to the simple stuff. Need to tell this story more comprehensively. | Our results show that activating contacts with high K-core can significantly reduce smartphone overuse time, with a more substantial reduction effect on non-communicative use than communication-driven use. Specifically, one standard deviation increase in core number leads to a 5.7-minute decrease in non-communication screen and a 5.34% decrease in overuse rate. However, activating contacts with a high degree centrality does not help curb smartphone overuse. The distinction between the effects of the two features suggests that contacts with a high K-core, which are those embedded in a cohesive group, have a stronger capability to motivate social engagement and project social influence. Furthermore, we find that the size of an activated social network reduces non-communicative screen time but increases communicative screen time. The two types of effects offset each other and result in no significant impact on overall screen time. The two types of effects offset each other and result in no significant impact on overall screen time. Moreover, we find that the impact of social network features does not vary with mobile communication level. Our results reveal that once a cluster of social networks is activated, the communication level does not influence the impact of the activated cluster, even though the activation itself is based on communication events. |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 9   | *"There are generally two types of social isolation: social disconnectedness and perceived isolation. Social disconnectedness refers to the status that someone lacks contacts or social con- nections. "*                                                                                                                                                                                                                                                                                                                                                                                                                         | It is interesting to explore the distinction between social disconnectedness and perceived isolation. In our data, there are three types of perceived loneliness: romantic loneliness, family loneliness and social loneliness. We can use the number of activated contacts per day as a proxy of social disconnectedness. Here is some descriptive results:                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                 |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     | These are interesting constructs which waiver in their centrality to the story. Do they correlate with our social network measures, are there other measures that capture these distinctions?                                                                                                                                                                                                                                                                                                                                                                                                                                      | The correlation between family loneliness and social disconnectedness:                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | ![](images/paste-8.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | ![](images/paste-2.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | The figure suggests that high family loneliness is correlated with more screen time regardless of the number of contacts activated.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | The correlation between romantic loneliness and social disconnectedness:                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | ![](images/paste-9.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | ![](images/paste-4.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | The figure suggests that low romantic loneliness is correlated with high screen time regardless of the number of contacts activated.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | The correlation between social loneliness and social disconnectedness:                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | ![](images/paste-10.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | ![](images/paste-3.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | The figure suggests that high social loneliness is correlated with high screen time when participants' activated contacts are at bottom 20% or top 20%.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+

: Review Response for Dr.Idris Adjerid

## Dr.Jiayi Liu {#sec-dr.jiayi-liu}

Thank you for your valuable comments and feedback.

+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| No. | Comments                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         | Responses                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                 |
+=====+==================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================+===========================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================+
| 1   | It appears to be that those with higher core-number are mostly close friends. Then one could say that the story is actually much simpler: merely engaging with close friends is what matters. Can you argue for using network features, like core-number, against more intuitive metrics such as contact closeness in this context?                                                                                                                                                                                                                                                                              | Thank you for your constructive comments. We measured the social distance of smartphone users with their contacts, as well as their level of trust in those contacts, which are the common measurement of interpersonal relationships.                                                                                                                                                                                                                                                                    |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | The estimation of the above two constructs suggest that they do not have significant impact on participants smartphone use behavior. Please refer to Table 5:                                                                                                                                                                                                                                                                                                                                             |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | ![](images/close_trust.png){width="35cm"}                                                                                                                                                                                                                                                                                                                                                                                                                                                                 |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 2   | A fundamental assumption is that social interactions mainly occur through calls and messages. Although the author has presented data showing a link between self-reported interaction levels and observed call/message frequencies, this doesn't establish that calls/messages are the primary channels of interaction. People could have spent more time on other social platforms and offline activities (with the time spent also aligning with the self-reported interaction levels). How do you plan to address these potential unobserved interactions? Or can you justify they don't affect your results? | This is an important issue that we need to address. Thanks for pointing this out. Indeed, there could be unobservable social engagements that are not based on phone call and message: 1) social interactions on other mobile applications; 2) physical interactions that are not based on phone call or messages.                                                                                                                                                                                        |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | First, for the social interactions happening on other platforms, it is indeed unobservable in our data set. However, based on the market share of the most popular mobile messaging channels, our data covered the leading four channels (Whatsapp, Phone calls, Facebook messager and Texting (SMS):![](images/channel.png)                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | Therefore, we suppose that our data has covered the majority of mobile communication activities.                                                                                                                                                                                                                                                                                                                                                                                                          |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | Second, in terms of the unobserved offline social interactions, there could be two categories:                                                                                                                                                                                                                                                                                                                                                                                                            |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | 1.  Smartphone users' offline social interactions were initiated by online communication and then it was swithed to offline social interaction. In this situation , the activation of social network is activated by smartphone communication. This scenario could support our 1 & and 2 hypothesis: activating embedded contacts and interacting with them could facilitate offline social engagement.                                                                                                   |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | 2.  The primary concern is the **offline social interaction is independent of smartphone communication**. In another word, the activation of social network is not based on smartphone communication. Nevertheless, 67.91% (90134/132709) of our observations are in session, which means students are on campus. For those observations, unobserved social interactions within family are ruled out. We speculate that students started with online social engagement except those with their roommates. |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 3   | The implications from your findings are also not clear. The current results show reduced smartphone use when engaging high "core-number" contacts. Does this suggest that one should have more interactions with such contacts to minimize their screen time? But the effect seems to be muted for the heaviest smartphone users, meaning this strategy wouldn't be effective for those who might be really addicted.                                                                                                                                                                                            | We identified smartphone users who are addicted to smartphone. To the best of knowledge, there is no quantitative definition of smartphone addiction. We define smartphone addiction based on multiple criterias:                                                                                                                                                                                                                                                                                         |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | 1.  Observations with daily screen time that are greater than 5 hours (300 minutes).                                                                                                                                                                                                                                                                                                                                                                                                                      |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | 2.  Observations with daily screen time that are ranked top 10%, 20%, 30% among population.                                                                                                                                                                                                                                                                                                                                                                                                               |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | 3.  Top 10 % screen time observations for each individuals' observations.                                                                                                                                                                                                                                                                                                                                                                                                                                 |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | We then estimated the probability of addiction with a logit model:                                                                                                                                                                                                                                                                                                                                                                                                                                        |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | $\begin{align} \ln \left(\frac{\operatorname{Pr}\left(\text { Addiction }_{i t}=1 \mid \boldsymbol{X}_{i t}\right)}{1-\operatorname{Pr}\left(\text { Addiction }_{i t}=1 \mid \boldsymbol{X}_{i t}\right)}\right) &= \nonumber \\ &\quad \beta_{0} + \beta_{1} \cdot \text{Social Network Features}_{it} \nonumber \\ &\quad+ \alpha \cdot X_{it} + \theta_{i} +\lambda_{t} + \varepsilon_{it}\end{align}$                                                                                                |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | All estimation results show that the increase in core number is associated with a decrease in the likelihood of smartphone addiction. For example:                                                                                                                                                                                                                                                                                                                                                        |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | ![](images/clipboard-2847711747.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                      |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 4   | Does a single interaction by call/text suffice to trigger this effect?                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           | **In the first version of this paper, the activation threshold is communication event \> 0. However, there could be a situation that the contacts did not respond to the information, which lead to a failed activation. I adjust it as follows: a contact is activated if any of the two conditions is met:**                                                                                                                                                                                            |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     | Can you provide more thoughts on the results?                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | 1\) the communication event type is a Call;                                                                                                                                                                                                                                                                                                                                                                                                                                                               |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | 2\) the communication event type is a message (SMS, MMS, or WhatsApp) and there are both '**outgoing**" and'**incoming**" messages (SMS, MMS, or WhatsApp).                                                                                                                                                                                                                                                                                                                                               |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | The above two conditions could ensure a **two-way communication (an effective activation)** exists between two smartphone users. This eliminates the possibility of one-way communication: one only sends or receives communication information. Overall, the estimation results are **mostly consistent with earlier results** after the adjustment.                                                                                                                                                     |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | ![](images/clipboard-2882367026.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                      |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 5   | It could be also interesting to explore how this effect vary by individual's perceived loneliness, their social interaction level, or maybe the timing of activation (e.g., morning vs night), etc.                                                                                                                                                                                                                                                                                                                                                                                                              | The third hypothesis is adjusted as follow:                                                                                                                                                                                                                                                                                                                                                                                                                                                               |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | An increase in communication with contacts with a high degree centrality improves the effectiveness of degree centrality in reducing smartphone usage.                                                                                                                                                                                                                                                                                                                                                    |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 6   | Smartphone addiction is measured by duration of smartphone use. But certain usages like seeking information or connecting can be productive. Why not consider defining addiction as screentime over a certain threshold?                                                                                                                                                                                                                                                                                                                                                                                         | Please refer to response 3.                                                                                                                                                                                                                                                                                                                                                                                                                                                                               |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 7   | "Activation" of a contact in a social media is determined by a single message or call. Shouldn't the frequency of interactions be considered? Would a weighted average make more sense here?                                                                                                                                                                                                                                                                                                                                                                                                                     | In robustness check, we adjust the activtion threshold as two-way communication. Please refer to response 4.                                                                                                                                                                                                                                                                                                                                                                                              |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 8   | In Figure 5, you handle missing contact information by referencing from the past or future. How often does such missing information happen? Wouldn't it be more appropriate to rely on the most recent survey only in order to capture the dynamic relationship?                                                                                                                                                                                                                                                                                                                                                 | We conducted a lookup operation to search for the missing contacts' social network information from the closest neighbors' social network surveys.                                                                                                                                                                                                                                                                                                                                                        |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | ![](images/search.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | We also conducted an alternative lookup approach by searching for the missing contacts backward first and then forward.                                                                                                                                                                                                                                                                                                                                                                                   |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | ![](images/search%20-%20bf-01.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                        |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | Both results are consistent with our original analysis:                                                                                                                                                                                                                                                                                                                                                                                                                                                   |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | ![](images/clipboard-2450557691.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                      |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 9   | Following the above point, how did you handle new relationships that emerged between biannual surveys?                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           | Please refer to response 8.                                                                                                                                                                                                                                                                                                                                                                                                                                                                               |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 10  | Figure 7 exemplifies social network activation. I'm curious about the repeated communications with a few out-of-network contacts: are these inbound or outbound? If these are mostly inbound with no response or occurred at regular times, it might be more reasonable to classify them as potential ads/promotions and exclude them from analysis.                                                                                                                                                                                                                                                             | 1.  Non-human contacts (promotions, advertising, fishing) are ruled out.                                                                                                                                                                                                                                                                                                                                                                                                                                  |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | 2.  We conducted two-way activation threshold to ensure that activation of social network is successful.                                                                                                                                                                                                                                                                                                                                                                                                  |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 11  | Personality was included as a control. Shouldn't it remain consistent for an individual? If so, you should drop it from the fixed-effect model.                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | Personalities are measured based on social surveys so they could change over surveys. Due to the missing information for certain participants, we excluded the information for now.                                                                                                                                                                                                                                                                                                                       |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 12  | It's not necessary to write three functions for total, communication, and non-communication screen time; the model is the same.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | Thank you, it is corrected in the manuscript.                                                                                                                                                                                                                                                                                                                                                                                                                                                             |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 13  | Based on the \# observations, the unit of analysis seems to be person-week, but in your model and results, "t" indicates day. Please clarify.                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | Thank you, the structure of the data is individual \* day. However, time fixed effect is at the **week level** (**`studyweeks`**), even though our panel data is structured at potentially a more granular (daily) level with **`date`**                                                                                                                                                                                                                                                                  |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 14  | Your hypothesis 3 is about perceived loneliness but the results are missing.  What is the relationship between the perceived loneliness and one's actual communication pattern?                                                                                                                                                                                                                                                                                                                                                                                                                                  | The third hypothesis is adjusted as follow:                                                                                                                                                                                                                                                                                                                                                                                                                                                               |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | An increase in communication with contacts with a high degree centrality improves the effectiveness of degree centrality in reducing smartphone usage.                                                                                                                                                                                                                                                                                                                                                    |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 15  | Please make the tables/figures self-explanatory. For example, in Table 6 it's unclear which column corresponds to which subsample. In Table 4, please specify the units for each variable.                                                                                                                                                                                                                                                                                                                                                                                                                       | Thank you, please refer to the manuscript for the recent correction in formats.                                                                                                                                                                                                                                                                                                                                                                                                                           |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+

: Review Response for Dr.Jiayi Liu
:::

### 2025-01-06 ProjectBlog/paper1/screen time/screentime.qmd
delete project text

---
title: "RQ2: Effects of Communication-Driven Use"
date: 05/21/2024
date-modified: last-modified
date-format: full
categories: [Paper1]
image: "images/msg_level-mean_winsor_screen.png"
tbl-colwidths: [5,50,75]
format: 
  html:
    toc: true
    toc-location: right
    page-layout: full
bibliography: references.bib
---

# Hypothesis Development

For the hypotheses development, I referred to the  paper  “Thinking about U: Theorizing and testing U- and inverted U-shaped relationships in strategy research” [@haans2016]to motivate and develop our paper. he measure- ment of smartphone usage can be measured by:

1.  Duration

2.  Frequency [@marciano2022]

## The Effects of Overall Smartphone Usage

### Positive Effects (Increasing pathway)

1.  Crowding-out effect on sleep time

2.  Increases exposure time to blue light

### Negative Effects (Decreasing pathway)

Using smartphones for leisure activities increases psycho- logical detachment from work/study [@hülsheger2014]. In addition, “The dose makes the poison.” The impact of overall smartphone use on sleep debt may depend on the amount of use, and moderate smartphone use could benefit sleep:

![](images/U-Shape.png){fig-align="center"}

We hypothesize that:

**Hypothesis 1:** There exists a U-shaped relationship between sleep debt and the amount of smartphone use before sleep.

## Moderating Effects of Social Interaction Usage

We measure social interaction usage by two indicators: message count and network size (contact count). We create a moderator Message Level: The message level is created based on the mean of message frequency(1 if \> mean, 0 if $<$ mean). Same for Network Size Level.

[![Topologies of Socialization](images/clipboard-1010489237.png){fig-alt="Source: flickr" fig-align="center"}](https://www.flickr.com/photos/joelogs/89627794/)

[![Technology and Relationships](images/Relationship_Tech.png){fig-align="center"}](https://andrewsobel.com/article/technology-and-relationships-where-should-you-spend-your-time/)

Based on the topologies about interaction and intimacy, we propose that:

![](images/clipboard-3692274076.png){fig-align="center"}

We estimate the moderating effects of message level and network size with the following specifications:

![](images/clipboard-3930394300.png){fig-align="center"}

The estimation results are as follow:

![](images/clipboard-681847467.png){fig-align="center"}

### Social Interaction as Moderator

![](images/message_moderator.png){fig-align="center"}

### Social Intimacy as Moderator

![](images/Intimacy_moderator.png){fig-align="center"}

### Social Intimacy as Moderator

![](images/Socialization_Moderator.png){fig-align="center"}

## Robustness Checks

![](images/clipboard-2673833856.png)

### ![](images/clipboard-874171734.png)

### ![](images/clipboard-2840737469.png)

### Contact Level as Moderator

![](images/contact_moderator.png){fig-align="center"}

### InnerContact Level as Moderator

![](images/InnerContact-Moderator.png){fig-align="center"}

### Socialization as Moderator

![](images/AlterSocialization_Moderator.png){fig-align="center"}

### Family as Moderator

![](images/contact_family50mp.png)

# Model and Results

## Descriptive Statistics

```{python}
#| echo: false
#| warning: false
#| output: true
import time;import pandas as pd;import numpy as np;import datetime
from datetime import datetime;from datetime import timedelta;import sqlite3;import warnings
import matplotlib.pyplot as plt;import seaborn as sns;warnings.filterwarnings('ignore')

df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/GoogleDrive-sky.ang510@gmail.com/My Drive/Nethealth/Data/CNSA/combine/7/df7_3hr.csv")

df[['sms','mms','whatsapp','message','length','bytes','screen_time','screen_com','screen_nocom','sc_com_pct','screen_com_level2','com_level']].describe(percentiles=[.10,.15,.20,.25,.50,.55,.60,.65,.70, .75,.80,.85,.90,.95]).round(2)
```

1.  **sms:** SMS message

2.  **mms:** MMS message

3.  **whatsapp:** Whatsapp message

4.  **message:** sms+mms+whatsapp

5.  **length:** Total Length of message in characters within 3 hours

6.  **bytes (KB):** Total Size of image (MMS) in bytes within 3 hours

7.  **screen_time:** overall screen time (minutes) within 3 hours

8.  **screen_com:** communication screen time (minutes) within 3 hours

9.  **screen_nocom:** non-communication screen time (minutes) within 3 hours

10. **sc_com_pct:** percentage of communication screen time (screen_com/screen_time, 0-100)

11. **screen_com_level2:** dummy variable for communication screen time (0: sc_com_pct\<50 %; 1: sc_com_pct ≥ 50 %)

12. **com_level:** dummy variable for message frequency (0: message \<average message ; 1: message ≥ average message)

Since the communication screen time depends on SMS messaging time and MMS messaging time. We calculate the approximate communication time as follow:

![](images/clipboard-3772066647.png){fig-align="center"}

SMS messaging time depends on

-   the text characters (length),

-   SMS texting speed (the number of characters one can text per minute),

-   SMS (the number of SMSs within 3 hours).

MMS messaging time depends on

-   the size of MMS (Bytes),

-   MMS messaging speed (the Bytes one can communicate per minute),

-   MMS (the number of MMSs within 3 hours).

## Communication Vs No-Communication (with Assumptions)

### Impact of Overall Screen Time

![](images/clipboard-1725006988.png){fig-align="center"}

The predicted sleep debt is based on the third column (highlighted), the turning pint for the overall screen time is **90.348** minutes.

![](images/overall_10-01.png){fig-align="center"}

### Comm. vs Non-Comm.

![](images/clipboard-1663320982.png){fig-align="center"}

### Predicted Sleep Debt by NoComm. Screen Time (Interval = 10 min)

![](images/clipboard-3848216028.png){fig-align="center"}

### Predicted Sleep Debt by Comm. Screen Time(Interval = 10 min)

![](images/clipboard-2518025618.png){fig-align="center"}

![](images/ComNocom-02.png){fig-align="center"}

We observe that:

1.  The turning pint of communication screen time comes **later** than that of non-communication screen time, which suggests that communication screen time becomes problematic later than that of non-communication screen time.

2.  The predicted sleep debt of communication screen time is **lower** than that of non-communication screen time

## Moderating Effect of Communication (without Assumptions)

In the the second column, we add an interaction term Message(High/Low) for screen time variables. The predicted sleep debt under low and high message levels are shown as follow:

![](images/msg_level-mean_winsor_screen.png){fig-align="center"}

We observe that:

1.  The turning pint of screen time with **high** message level **later** than that with **low** message level, which suggests that screen time with **high** message level becomes problematic later than that with **low** message level.

2.  The predicted sleep debt of screen time with **high** message level is **lower** than that with **low** message level.

The message level is created based on the mean of message frequency(1 if \> mean, 0 if \< mean). We can observe that message level moderates the impact of screen time by

1) **moving the turning point right**, and

2) **flattening the curve,** which are the two ways of moderation effects in U-shape effects [@haans2016].

## Appendix

### Predicted Sleep Debt by Screen Time Intervals

![](images/clipboard-2036136209.png)

### Predicted Sleep Debt with Moderating Effects by Screen Time Intervals

![](images/clipboard-1013317902.png)

![](images/clipboard-2164487531.png)

### 2025-01-06 posts/IV/IV.qmd
delete project text

---
title: "Instrument Variable for Screen Time"
date: 02/06/2024
date-modified: last-modified
date-format: full
categories: [Paper1]
format:
  html:
    page-layout: full
    code-overflow: wrap
comments:
  hypothesis: true
bibliography: references.bib
---

In this update, we try to find an instrument variable to justify the causal effect of screen time on sleep debt. First, we introduce the related variables:

```{python}
#| echo: false
#| warning: false
#| output: true
import time;import pandas as pd;import numpy as np;import datetime
from datetime import datetime;from datetime import timedelta;import sqlite3;import warnings
import matplotlib.pyplot as plt;import seaborn as sns;warnings.filterwarnings('ignore')

df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/OneDrive-Personal/Nethealth/Data/CNSA/combine/7/bt7_1.5r.csv")

df[['egoid','count_begin90', 'time_fallsleep','battery','battery_time','charging','binterval']]
```

-   **egoid:** individual identifier

-   **count_begin90:** starting time of measurement window of 90 minutes

-   **time_fallsleep:** time of falling asleep for an egoid on a certain day

-   **battery:** battery level at the closest measuring point before the starting point of measurement window, namely "**count_begin90"**

-   **battery_time:** the measuring time point of battery level. We only maintain the observations with '**battery_time' that is within 30 minutes from 'time_fallsleep'** for the purpose of measurement accuracy

-   **charging:** dummy indicating the charging status of smartphone at time 'battery_time' with **'1' for charging and '0' for unpluged**

-   **binterval:** the time interval (minutes) between 'battery_time' and 'count_begin90'

The following table shows descriptive statistics:

```{python}
#| echo: false
#| warning: false
#| output: true

df[['egoid','count_begin90', 'time_fallsleep','battery','charging','battery_time','binterval']].describe()
```

We speculate that the charging status is positively associated with screen time as one may need to charge his/her phone if the user anticipate that he/she was going to use smartphone intensively in the next 90 minutes. To examine whether "charging" could work as and instrument variable for 'screen time", we first regress "screen time" on "charging". Since our earlier results show that screen time has U-shape impact on sleep debt, we divide the data into two subgroups based on the turning point of screen time.

Here is the descriptive statistics for observations before turning point:

```{python}
#| echo: false
#| warning: false
#| output: true
df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/OneDrive-Personal/Nethealth/Data/CNSA/combine/7/df7_22-5s.csv")
df[['egoid','screen_time', 'unlock','message','count_begin90', 'time_fallsleep','battery','charging','battery_time','binterval']].describe()
```

The following table shows the descriptive statistics for observations after turning point:

```{python}
#| echo: false
#| warning: false
#| output: true
df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/OneDrive-Personal/Nethealth/Data/CNSA/combine/7/df7_22-5b.csv")
df[['egoid','screen_time', 'unlock','message','count_begin90', 'time_fallsleep','battery','charging','battery_time','binterval']].describe()
```

```{python}
#| echo: false
#| warning: false
#| output: false
import time;import pandas as pd;import numpy as np ;import datetime
from datetime import datetime;from datetime import timedelta;import stata_setup
stata_setup.config('/Applications/Stata', 'mp')
```

## Empiricial Strategy

### Screen Time \< Turning Point

We first check whether charging status could work as an instrument variable for screen time for observations with screen time \< turning point (50 minutes)

```{python}
#| echo: false
#| warning: false
#| output: false
#| code-fold: false
#| code-overflow: wrap
%%stata
#| echo: true
clear all
set maxvar 120000, permanently
set more off

import delimited "/Users/shaokangyang/Library/CloudStorage/OneDrive-Personal/Nethealth/Data/CNSA/combine/7/df7_22-5s.csv"
gen date2 = date(date, "YMD")
```

### **First Stage: Test the Relevance of the Instrument**

```{python}
#| echo: true
#| warning: false
#| output: false
#| code-fold: false
#| code-overflow: wrap
%%stata

global id egoid
global t date2
global ylist sleep_debt
global mainIV  c.screen_time##c.screen_time iimessage unlock
global Call_Control call duration length bytes
global Fitness_Control steps100 floors sedentaryminutes lightlyactiveminutes fairlyactiveminutes veryactiveminutes lowrangecal100 fatburncal100 cardiocal100 peakcal100
global Other_Control naps naps_dur light_exposure insession##weekday##time_wakeuphour c.studyweeks#id
global fe i.studyweeks

*Set data as panel data
sort $id $t
xtset $id $t

regress screen_time charging battery $fe $Fitness_Control $Other_Control $Call_Control message unlock i.egoid

```

```{python}
#| echo: true
#| warning: false
#| output: true
#| code-fold: false
#| code-overflow: wrap
%%stata

esttab, keep(charging battery message unlock) stats(N r2 F p, labels("Observations" "R-squared" "F statistic" "Prob > F")) replace
```

The results shows charging status is positively associated with screen time. Moreover, the F-statistics of 35.34 indicate that 'charging' is a valid IV for screen time.

#### **IV Estimation**

```{python}
#| echo: true
#| warning: false
#| output: false
#| code-fold: false
#| code-overflow: wrap
%%stata

ivregress 2sls sleep_debt (screen_time = charging) $fe $Fitness_Control $Other_Control $Call_Control i.egoid message unlock battery
```

```{python}
#| echo: true
#| warning: false
#| output: true
#| code-fold: false
#| code-overflow: wrap
%%stata

esttab, keep(screen_time battery message unlock) stats(N r2 F p, labels("Observations" "R-squared" "F statistic" "Prob > F")) replace
```

The IV estimation results suggest that screen time reduces sleep debt when screen time \< turning point. \### Screen Time \> Turning Point

We first check whether charging status could work as an instrument variable for screen time for observations with screen time \< turning point (50 minutes)

```{python}
#| echo: false
#| warning: false
#| output: false
#| code-fold: false
#| code-overflow: wrap
%%stata
#| echo: true
clear all
set maxvar 120000, permanently
set more off

import delimited "/Users/shaokangyang/Library/CloudStorage/OneDrive-Personal/Nethealth/Data/CNSA/combine/7/df7_22-5b.csv"
gen date2 = date(date, "YMD")
```

### **First Stage: Test the Relevance of the Instrument**

```{python}
#| echo: true
#| warning: false
#| output: false
#| code-fold: false
#| code-overflow: wrap
%%stata

global id egoid
global t date2
global ylist sleep_debt
global mainIV  c.screen_time##c.screen_time iimessage unlock
global Call_Control call duration length bytes
global Fitness_Control steps100 floors sedentaryminutes lightlyactiveminutes fairlyactiveminutes veryactiveminutes lowrangecal100 fatburncal100 cardiocal100 peakcal100
global Other_Control naps naps_dur light_exposure insession##weekday##time_wakeuphour c.studyweeks#id
global fe i.studyweeks

*Set data as panel data
sort $id $t
xtset $id $t

regress screen_time charging battery $fe $Fitness_Control $Other_Control $Call_Control message unlock i.egoid

```

```{python}
#| echo: true
#| warning: false
#| output: true
#| code-fold: false
#| code-overflow: wrap
%%stata

esttab, keep(charging battery message unlock) stats(N r2 F p, labels("Observations" "R-squared" "F statistic" "Prob > F")) replace
```

The results shows charging status is positively associated with screen time, indicating that 'charging' is a valid IV for screen time.

#### **IV Estimation**

```{python}
#| echo: true
#| warning: false
#| output: false
#| code-fold: false
#| code-overflow: wrap
%%stata

ivregress 2sls sleep_debt (screen_time = charging) $fe $Fitness_Control $Other_Control $Call_Control i.egoid message unlock battery
```

```{python}
#| echo: true
#| warning: false
#| output: true
#| code-fold: false
#| code-overflow: wrap
%%stata

esttab, keep(screen_time battery message unlock) stats(N r2 F p, labels("Observations" "R-squared" "F statistic" "Prob > F")) replace
```

The estimation for screen time is significant when p\<0.1 although not significant when p\<0.05. The IV estimation results suggest that screen time increases sleep debt when screen time \> turning point.

### 2025-01-06 posts/Paper 2/paper2.tex
delete project text

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Social Network Activation: Application in Smartphone Use},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Social Network Activation: \The Application in Smartphone Use}
\author{}
\date{2023-11-28}

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, enhanced, sharp corners, borderline west={3pt}{0pt}{shadecolor}, breakable, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi

\hypertarget{social-network-activation}{%
\subsection{Social Network Activation}\label{social-network-activation}}

\begin{figure}

{\centering \includegraphics{inout.png}

}

\end{figure}

\hypertarget{hypothesis-1}{%
\subsection{Hypothesis 1}\label{hypothesis-1}}

\begin{figure}

{\centering \includegraphics{images/centrality-01.png}

}

\end{figure}

\begin{itemize}
\tightlist
\item
  H1: Activating social networks with a higher \textbf{Degree
  Centrality} score \textbf{reduces} the time spent on a smartphone.
\end{itemize}

\hypertarget{hypothesis-2}{%
\subsection{Hypothesis 2}\label{hypothesis-2}}

\begin{figure}

{\centering \includegraphics{images/core_number.png}

}

\end{figure}

\begin{itemize}
\tightlist
\item
  H2: Activating social networks with a higher \textbf{K-Core} score
  \textbf{reduces} the time spent on a smartphone.
\end{itemize}

\hypertarget{hypothesis-3}{%
\subsection{Hypothesis 3}\label{hypothesis-3}}

\begin{itemize}
\tightlist
\item
  H3 (1): An \textbf{increase in communication} with contacts with high
  degree centrality \textbf{improves the effectiveness} of degree
  centrality in reducing smartphone usage.
\item
  H3 (2): An \textbf{increase in communication} with contacts with high
  K-Core \textbf{improves the effectiveness} of K-Core in reducing
  smartphone usage.
\end{itemize}

\hypertarget{specification-1}{%
\subsection{Specification 1}\label{specification-1}}

\hfill\break

\(\begin{equation} \begin{split} \text{Screen Time}_{it} = \beta_0 + \beta_1 \cdot \text{Social Network Features}_{it} + \\ \alpha \cdot X_{it} + \theta_i + \lambda_t + \varepsilon_{it} \end{split} \label{e1}\end{equation}\)\\

\begin{itemize}
\tightlist
\item
  \(\text{Screen Time}_{it}\): Smartphone use time before users fall
  asleep
\item
  \(\text{Social Network Features}_{it}\): Degree Centrality and K-Core
\item
  \(\text{X}_{it}\): Control variables: Steps, sleep duration, naps,
  etc.
\item
  \(\theta_i\): Individual fixed effect (students)
\item
  \(\lambda_t\): Time fixed effect (day)
\end{itemize}

\hypertarget{result-1-main-centrality-k-core}{%
\subsection{Result 1: Main (Centrality \&
K-Core)}\label{result-1-main-centrality-k-core}}

\begin{figure}

{\centering \includegraphics{images/2table5.png}

}

\end{figure}

\hypertarget{conclusion-h1-h2}{%
\subsection{Conclusion (H1 \& H2)}\label{conclusion-h1-h2}}

~

\begin{itemize}
\tightlist
\item
  Degree Centrality \textbf{does not} affect non-communication
  smartphone use but \textbf{improve}s overall smartphone use by
  increasing the time spent on communication.~\textbf{H1 is not
  supported.}
\item
  K-Core \textbf{reduces} overall smartphone use( Communication, others
  and overall). ~\textbf{H2 is supported.}
\end{itemize}

\hypertarget{result-3-moderating-impact-of-communication}{%
\subsection{Result 3: Moderating Impact of
Communication}\label{result-3-moderating-impact-of-communication}}

\begin{figure}

{\centering \includegraphics{images/2table6.png}

}

\end{figure}

\hypertarget{conclusion-3-h3}{%
\subsection{Conclusion 3 (H3)}\label{conclusion-3-h3}}

~

\begin{itemize}
\tightlist
\item
  Communication frequency shows \textbf{NO moderating impact} on the
  effectiveness of network features. ~\textbf{H3 is not supported.}
\end{itemize}

\hypertarget{result-4-addiction-esimation-logistic}{%
\subsection{Result 4: Addiction Esimation
(Logistic)}\label{result-4-addiction-esimation-logistic}}

\hfill\break
Addiction is defined as:

\begin{itemize}
\item
  \textbf{Overall} addiction: overall screen time \textgreater{} 300 min
\item
  \textbf{Non-communication-drive} addiction: Non-communication screen
  time \textgreater{} 240 min
\item
  \textbf{Communication-drive} addiction: Communication screen time
  \textgreater{} 40 min
\end{itemize}

\hypertarget{specification-2}{%
\subsection{Specification 2}\label{specification-2}}

~

\(\begin{equation} \begin{split} \ln \left(\frac{\operatorname{Pr}\left(\text { Addiction }_{it}=1 \mid \boldsymbol{X}_{i t}\right)}{1-\operatorname{Pr}\left(\text { Addiction }_{it}=1 \mid \boldsymbol{X}_{i t}\right)}\right) = \beta_{0}+\beta_{1} \cdot \text{Social Network Features}_{it}+ \\ \alpha \cdot X_{it}+\theta_{i} +\lambda_{t}+\varepsilon_{it} \end{split} \label{e2} \end{equation}\)\\

\begin{itemize}
\tightlist
\item
  \(\text{Screen Time}_{it}\): Smartphone use time before users fall
  asleep
\item
  \(\text{Social Network Features}_{it}\): Degree Centrality and K-Core
\item
  \(\text{X}_{it}\): Control variables: Steps, sleep duration, naps,
  etc.
\item
  \(\theta_i\): Individual fixed effect (students)
\item
  \(\lambda_t\): Time fixed effect (day)
\end{itemize}

\hypertarget{result-4-addiction-esimation-logistic-1}{%
\subsection{Result 4: Addiction Esimation
(Logistic)}\label{result-4-addiction-esimation-logistic-1}}

\begin{Shaded}
\begin{Highlighting}[numbers=left,,]
\KeywordTok{global} \BuiltInTok{id}\NormalTok{ egoid}
\KeywordTok{global}\NormalTok{ t date2}
\KeywordTok{global}\NormalTok{ ylist addic\_noncom90}
\KeywordTok{global}\NormalTok{ mainIV  active\_nodes out\_contacts  num\_edges  steps minsasleep trust close position duration}
\KeywordTok{global}\NormalTok{ Social\_Control degree\_centrality core\_number}
\KeywordTok{global}\NormalTok{ Other\_Control i.insession i.weekday community naps nap\_minsasleep}
\KeywordTok{global}\NormalTok{ fe i.studyweek}
\OperatorTok{*}\NormalTok{Set data }\ImportTok{as}\NormalTok{ panel data}
\NormalTok{sort $id $t}
\NormalTok{xtset $id $t}

\NormalTok{xtreg $ylist $fe  $Other\_Control $Social\_Control  $mainIV , fe cluster($id) }
\NormalTok{xtlogit $ylist $fe  $Other\_Control $Social\_Control  $mainIV , fe cluster($id) }\KeywordTok{or}
\NormalTok{outreg2 using SoUnAcSl.tex, append dec(}\DecValTok{3}\NormalTok{) addtext(Communication, Full, Unit F.E., YES, Week F.E, YES) keep($mainIV $Social\_Control)  title(}\StringTok{"90 Addiction Estimation"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\hypertarget{result-4-addiction-esimation-logistic-2}{%
\subsection{Result 4: Addiction Esimation
(Logistic)}\label{result-4-addiction-esimation-logistic-2}}

\begin{figure}

{\centering \includegraphics{images/addiction.png}

}

\end{figure}

\hypertarget{result-4-addiction-esimation-logistic-3}{%
\subsection{Result 4: Addiction Esimation
(Logistic)}\label{result-4-addiction-esimation-logistic-3}}

\begin{figure}

{\centering \includegraphics{images/addiction2-02.png}

}

\end{figure}

\hypertarget{conclusion-4-h4}{%
\subsection{Conclusion 4 (H4)}\label{conclusion-4-h4}}

~

\begin{itemize}
\tightlist
\item
  Network features \textbf{outperform} traditional constructs (Trust,
  Social Distance (Closeness)).
\end{itemize}

\hypertarget{result-4-sleep-as-dv}{%
\subsection{Result 4: Sleep as DV}\label{result-4-sleep-as-dv}}

\begin{itemize}
\tightlist
\item
  \includegraphics{images/2sleep.png}
\end{itemize}

\end{document}

### 2025-01-06 ProjectBlog/others/Natality/natality.qmd
natality

---
title: "Dobbs' Decision And Abortion"
date: 01/05/2025
date-modified: last-modified
draft: false
date-format: full
categories: [Others]
website:
  comments: 
    utterances:
      repo: quarto-dev/quarto-web
#image: "cluster1.png"
tbl-colwidths: [5,30,125]
format: 
  html:
    page-layout: full
bibliography: references.bib
---

## Background

Restrictions on abortion have rendered significant impact on abortion decision and the number of births. Texas launched two abortion policies:

Senate Bill 8 of Texas is a bill that forbidden abortions for pregnancy over six weeks.

### 2025-01-06 ProjectBlog/others/Natality/natality.qmd
natality

@@
 
-Restrictions on abortion have rendered significant impact on abortion decision and the number of births. Texas launched two abortion policies:
+Restrictions on abortion have rendered significant impact on abortion decision and the number of births. For example, Texas launched two abortion policies:
 
-Senate Bill 8 of Texas is a bill that forbidden abortions for pregnancy over six weeks.
+-   Senate Bill 8 of Texas: The bill launched on September 2021 forbidden abortions for pregnancy over six weeks.
+
+-   Dobbs' decision: The decision passed on June 22, 2022 allows states to make their own abortion policies.
+
+Any impact on the number of abortions will be captured by the number of births around ten months later.
+
+As the paralle trend assumption is hard to satisfy in this study, I made a synthetic Texas with states with abortion free policies to examine the effects of the two policies on abortions.

### 2025-01-06 ProjectBlog/others/Natality/natality.qmd
abortion policy
natality data

@@
 
-As the paralle trend assumption is hard to satisfy in this study, I made a synthetic Texas with states with abortion free policies to examine the effects of the two policies on abortions.
+## Methodology
+
+### Data
+
+County by month level natality observations.
+
+### Model
+
+As the parall trend assumption is hard to satisfy in this study, I made a synthetic Texas with states (e.g., New York and California) with abortion free policies and take it as control group.
+I use a synthetic difference-in-difference estimator to examine the effects of the two policies on abortions.
+
+## Results
+
+My preliminary anticipation is that Dobbs' decision make one third of women that would chose to terminate pregnancy change their mind to give birth to a baby.

### 2025-01-07 ProjectBlog/others/Natality/natality.qmd
sdid

@@
     page-layout: full
+    default-image-extension: svg
 bibliography: references.bib
@@
 
--   Senate Bill 8 of Texas: The bill launched on September 2021 forbidden abortions for pregnancy over six weeks.
+-   Senate Bill 8 of Texas: The bill launched on **September 1st, 2021** forbidden abortions for pregnancy over six weeks.
 
--   Dobbs' decision: The decision passed on June 22, 2022 allows states to make their own abortion policies.
+-   Dobbs' decision: The decision passed on **June 24, 2022** allows states to make their own abortion policies.
 
@@
 As the parall trend assumption is hard to satisfy in this study, I made a synthetic Texas with states (e.g., New York and California) with abortion free policies and take it as control group.
-I use a synthetic difference-in-difference estimator to examine the effects of the two policies on abortions.
+I use a synthetic difference-in-difference estimator [@arkhangelsky2021] to examine the effects of the two policies on abortions.
+The matrix for the estimator is as follows:
+
+$$
+Y = \begin{bmatrix}
+    \pmb{Y}_{pre, co} & \pmb{Y}_{pre, tr} \\
+    \pmb{Y}_{post, co} & \pmb{Y}_{post, tr} \\
+\end{bmatrix}
+$$
+
+Recall the Diff-in-Diff estimator:
+
+$$
+Y_{it} = \beta_0 + \beta_1 Post_t + \beta_2 Treated_i + \beta_3 Treated_i  Post_t + e_{it}
+$$
+
+we fit unit ($\alpha_i$) and time ($\beta_t$) averages, alongside the treatment indicator.
+
+$$
+\hat{\tau}^{did} = \underset{\mu, \alpha, \beta, \tau}{argmin} \bigg\{ \sum_{i=1}^N \sum_{t=1}^T \big(Y_{it} - (\mu + \alpha_i + \beta_t + \tau D_{it}\big)^2 \bigg\}
+$$
+
+and the Synthetic Controls:
+
+$$
+\hat{w}^{sc} = \underset{w}{\mathrm{argmin}} \ ||\pmb{\bar{y}}_{pre, tr} - \pmb{Y}_{pre, co} \pmb{w}_{co}||^2_2 
+$$ $$
+\text{s.t } \ \sum w_i = 1 \text{ and } \ w_i > 0 \ \forall \ i
+$$
+
+where the outcome $\pmb{Y}_{pre, co}$ is a $T_{pre}$ by $N_{co}$ matrix, where the columns are the units and the rows are the time periods.
+$\pmb{w}_{co}$ is a $N_{co}$ by 1 column vector, with one entry for each unit.
+Finally, $\pmb{\bar{y}}_{pre, tr}$ is a $T_{pre}$ by 1 column vector, where each entry is the time average of the treated units in the pre-treatment period.
+
+The **values of synthetic control group** before and after treatment is:
+
+$$
+\pmb{y}_{sc} = \pmb{Y}_{co}\hat{\pmb{w}}^{sc}
+$$
+
+the average treatment effects ($ATT$) are as follows:
+
+$$
+\hat{\tau} =  \bar{y}_{post, tr} - \bar{y}_{post, sc}
+$$
+
+Let's say we have a matrix of treatment assignments $D$, where the **columns of the matrix are units** and **rows of the matrix are time periods**.
+
+$$
+D = \begin{bmatrix}
+    0 & 0 & 0 & \dots & 0 & 0 \\
+    0 & 0 & 0 & \dots & 0 & 0 \\
+    \vdots \\
+    0 & 0 & 0 & \dots & 1 & 1 \\
+    0 & 0 & 0 & \dots & 1 & 1 \\
+\end{bmatrix}
+$$
+
+We merge the equations of DiD and SC and obtain the estimator of SDiD:
+
+$$
+\hat{\tau}^{sdid} = \underset{\mu, \alpha, \beta, \tau}{argmin}  \bigg\{ \sum_{i=1}^N \sum_{t=1}^T \big(Y_{it} - (\mu + \alpha_i + \beta_t + \tau D_{it}\big)^2 \hat{w}^{sdid}_i \hat{\lambda}^{sdid}_t \bigg\}
+$$
 
@@
 My preliminary anticipation is that Dobbs' decision make one third of women that would chose to terminate pregnancy change their mind to give birth to a baby.
+
+Non-Parallel Trend
+
+![](images/non-parallel-04.svg){fig-align="center"}
+
+Estimation:
+
+![](images/sdid.svg){fig-align="center"}

### 2025-01-15 ProjectBlog/others/Ipynb/ipynb.qmd
Dobbs' Decision And Abortion2

--- 2025-01-07 ProjectBlog/others/Natality/natality.qmd
@@
 ---
-title: "Dobbs' Decision And Abortion"
+title: "Dobbs' Decision And Abortion2"
 date: 01/05/2025

### 2025-01-22 ProjectBlog/paper1/Clustering Anlysis/cluster.qmd
interflex
cluster analysis

@@
 
-# Creating a special bin for 0
-df1=df[df['screen_time']>15]
-bins = [-np.inf, 0.001] + list(range(15, 185, 5))  # 0.1 to include 0 in the first bin exclusively
-df1['screen_time_bin'] = pd.cut(df1['screen_time'], bins=bins, right=False, include_lowest=True)
-# Recalculating the aggregated data
-grouped = df1.groupby('screen_time_bin').agg({'sleep_debt':'mean', 'message':'mean', 'screen_time':'count'}).reset_index()
-# Replotting with the adjusted bins
+import pandas as pd
+import matplotlib.pyplot as plt
+from matplotlib.lines import Line2D
+
+# Assuming df1 is already defined as df
+df1 = df
+
+# Data preparation steps (as per your instructions)
+df1['screen_time_bin'] = None
+
+# Creating bins as [0, 10), [10, 20), ...
+bins = list(range(0, 190, 10))  # Define bins from 0 to 180 in steps of 10
+labels = [f"[{bins[i]},{bins[i+1]})" for i in range(len(bins)-1)]  # Create labels like '[0,10)', '[10,20)', etc.
+
+# Creating screen_time_bin column using pd.cut
+df1['screen_time_bin'] = pd.cut(df1['screen_time'], bins=bins, labels=labels, right=False, include_lowest=True)
+
+# Aggregating data for each bin
+grouped = df1.groupby('screen_time_bin').agg({
+    'sleep_debt': 'mean',
+    'message': 'mean',
+    'screen_time': 'count'
+}).reset_index()
+
+# Plotting
+plt.rcParams['font.family'] = 'Times New Roman'
 fig, ax1 = plt.subplots(figsize=(14, 8))
+
 # Line plot for sleep debt trend
-line1, = ax1.plot(grouped['screen_time_bin'].astype(str), grouped['sleep_debt'], color='blue', linestyle='-', marker='o', label='Sleep Debt')
-# Adding labels for sleep debt
-for x, y in zip(grouped['screen_time_bin'].astype(str), grouped['sleep_debt']):
-    ax1.text(x, y, f'{y:.2f}', va='bottom', ha='center', color='blue')
-# Setting the left y-axis for sleep debt
-ax1.set_xlabel('Screen Time (minutes)')
-ax1.set_ylabel('Average Sleep Debt')
-ax1.set_title('Sleep Debt, Screen Time and Message')
-ax1.tick_params(axis='x', rotation=45)
-# Line plot for message count on a secondary y-axis
+line1, = ax1.plot(grouped['screen_time_bin'], grouped['sleep_debt'], color='purple',
+                  linestyle='-', marker='o', label='Sleep Debt')
+for x, y in zip(grouped['screen_time_bin'], grouped['sleep_debt']):
+    ax1.annotate(f'{y:.2f}', (x, y), textcoords="offset points", xytext=(0, 10), ha='center', color='purple')
+
+# X and Y labels
+ax1.set_xlabel('Screen Time (minutes)', fontsize=14, color='black')
+ax1.set_ylabel('Sleep Debt (minutes)', fontsize=14, color='black')
+ax1.tick_params(axis='x', rotation=30, labelcolor='black', labelsize=10)
+ax1.tick_params(axis='y', labelcolor='black', labelsize=12)
+# ax1.set_title('Sleep Debt, Screen Time and Message')
+
+# Secondary axis for message count
 ax2 = ax1.twinx()
-line2, = ax2.plot(grouped['screen_time_bin'].astype(str), grouped['message'], color='darkorange', linestyle='--', marker='o', label='Message')
-# Adding labels for message count
+line2, = ax2.plot(grouped['screen_time_bin'], grouped['message'], color='darkorange',
+                  linestyle='-', marker='o', label='Message')
 for i, txt in enumerate(grouped['message']):
-    ax2.annotate(f'{txt:.2f}', (grouped['screen_time_bin'].astype(str)[i], grouped['message'][i]), textcoords="offset points", xytext=(0,10), ha='center')
-ax2.set_ylabel('Message')
-# Bar plot for the number of observations on a secondary y-axis
+    ax2.annotate(f'{txt:.2f}', (grouped['screen_time_bin'][i], grouped['message'][i]),
+                 textcoords="offset points", xytext=(0, 10), ha='center', color='darkorange')
+ax2.set_ylabel('Message', fontsize=14, color='black')
+ax2.tick_params(axis='y', labelcolor='black', labelsize=12)
+
+# Tertiary axis for bar plot of observations
 ax3 = ax1.twinx()
-bars = ax3.bar(grouped['screen_time_bin'].astype(str), grouped['screen_time'], width=0.4, color='lightgrey', alpha=0.5, label='Number of Observations')
-ax3.spines['right'].set_position(('outward', 60))  # Offset the right spine of ax3
-ax3.set_ylabel('Number of Observations')
-# Labeling the number of observations above each bar
+bars = ax3.bar(grouped['screen_time_bin'], grouped['screen_time'], width=0.4, color='lightblue',
+               alpha=0.3, label='Number of Observations')
+ax3.spines['right'].set_position(('outward', 60))
+
+# Hide the axis for Number of Observations
+ax3.get_yaxis().set_visible(False)
+ax3.spines['right'].set_visible(False)
+
+# Draw connection lines from bar bottoms to the x-axis range
+for bar, bin_label in zip(bars, grouped['screen_time_bin']):
+    bar_x = bar.get_x() + bar.get_width() / 2
+    bar_bottom = bar.get_y()
+    ax1.add_line(Line2D([bar_x, bar_x], [bar_bottom, -10], color='gray', linestyle='-'))
+
 for bar in bars:
@@
     ax3.text(bar.get_x() + bar.get_width() / 2, yval, f'{int(yval)}', va='bottom', ha='center', color='black')
-# Adjusting the plot
-ax1.grid(True, which='both', linestyle='--', linewidth=0.5)
-ax2.grid(False)
-ax3.grid(False)
-# Adding legends
-fig.legend(loc='upper right')
+
+# Legend
+lines = [line1, line2]
+bars_proxy = plt.Line2D([0], [0], color='lightblue', alpha=0.3, lw=8)
+labels = ['Sleep Debt', 'Message', 'Number of Observations']
+fig.legend(lines + [bars_proxy], labels, loc='upper right', bbox_to_anchor=(0.96, 0.99), fontsize=12)
+
+# Tight layout and save
 fig.tight_layout()
+plt.savefig('/Users/shaokangyang/Downloads/model-free.svg', format='svg', dpi=300)
 plt.show()
 ```
+
+### **Marginal effect estimates with multiplicative interaction models**
+
+![](images/nonparametric%20rela.svg){fig-align="center"}
 

### 2025-01-28 ProjectBlog/paper2/DV Adjust/DV Adjust.qmd
p2 dv adjustment < 21:00

---
title: "DV Adjustment"
date: 01/29/2024
date-modified: last-modified
date-format: full
categories: [Paper2]
#image: "cluster1.png"
tbl-colwidths: [5,30,125]
format: 
  html:
    page-layout: full
---

Distribution of going to be times.

![](images/Go2Bed-02.png){fig-align="center"}

Distribution of waking up times.

![](images/wake.png){fig-align="center"}

### 2025-02-04 ProjectBlog/paper2/Paper 2 Slides/P2 Slides.qmd
paper 2 slides

---
title: "Social Network Activation: \\The Application in Smartphone Use"
date: 02/04/2025
date-modified: last-modified
date-format: full
categories: [Paper2]
image: "inout.png"
format:
  revealjs: 
    theme: default
smaller: true
bibliography: references.bib
---

### Background

-   Humans are inherently **social beings**. Social engagement improves feeling of belongingness, social fulfillment, etc., which enhance mental health. [@luo2020].

-   In contrast, social isolation can results in anxiety, depression [@robb2020], and suicide [@garnettf.2023].

### **Research Gap**

-   To address the consequences of lack of social engagement, prior studies primarily focus on social interaction volume. However, little attention is paid the the structure of one's social network.

-   Specifically, it is not clear whether activating different parts (e.g., core vs.periphery) of social network impact individuals differently.

### Context:

Social isolation ➟ Smartphone Addiction

##

###

![](inout.png){fig-align="center"}

## Hypothesis 1

-   **H1:** Activating social networks reduces smartphone screen time; the reduction in screen time increases with the number of contacts activated. <br /> <br /> <br />

## Whom to activate?

Identification of Social Influence

-   Social person VS. Non-social person
-   Central VS. Peripheral

## Connectedness

![](images/centrality-01.png){fig-align="center"}

-   **H2:** Activating social networks with a higher **Degree Centrality** score **reduces** the time spent on a smartphone.

## Consider group cohesiveness

![](images/core_number.png){fig-align="center"}

-   **H3:** Activating social networks with a higher **K-Core** score **reduces** the time spent on a smartphone.

## Specification 1

\

$\begin{equation} \begin{split} \text{Screen Time}_{it} = \beta_0 + \beta_1 \cdot \text{Social Network Features}_{it} + \alpha \cdot X_{it} + \theta_i + \lambda_t + \varepsilon_{it} \end{split} \label{e1}\end{equation}$\

-   $\text{Screen Time}_{it}$: Smartphone use time before users fall asleep
-   $\text{Social Network Features}_{it}$: Degree Centrality and K-Core
-   $\text{X}_{it}$: Control variables: Steps, sleep duration, naps, etc.
-   $\theta_i$: Individual fixed effect (students)
-   $\lambda_t$: Time fixed effect (week)

## Result 1 & 2 (Centrality & K-Core):

![](images/2table5.png){fig-align="center"}

## Interpretation

::: incremental
-   Degree Centrality **does not** affect non-communication smartphone use but **improve**s overall smartphone use by increasing the time spent on communication. **H1 is not supported.**
-   K-Core **reduces** overall smartphone use( Communication, others and overall).  **H2 is supported.**
:::

## Mediation of Physical Activity

![](images/paste-1.png){fig-align="center"}

## Sobel-Goodman Mediation Tests

![](/posts/Mediation%20Effect%20of%20Steps/images/paste-6.png){fig-align="center"}

## Mediation of Physical Activity

![](/posts/Mediation%20Effect%20of%20Steps/images/mediation%20-%20before.png){fig-align="center"}

## Interpretation

::: incremental
-   ::: incremental
    Core number reduces screen time by increasing individuals' physical active level

    15.8% of reductive effects of core number come from steps
    :::
:::

## Result 4: Addiction Esimation (Logistic)

\
Addiction is defined as:

-   **Overall** addiction: overall screen time \> 300 min

-   **Non-communication-drive** addiction: Non-communication screen time \> 240 min

-   **Communication-drive** addiction: Communication screen time \> 40 min

## Specification 2

$\begin{equation} \begin{split} \ln \left(\frac{\operatorname{Pr}\left(\text { Addiction }_{it}=1 \mid \boldsymbol{X}_{i t}\right)}{1-\operatorname{Pr}\left(\text { Addiction }_{it}=1 \mid \boldsymbol{X}_{i t}\right)}\right) = \beta_{0}+ \beta_{1} \cdot \text{Social Network Features}_{it}+ \\ \alpha \cdot X_{it}+\theta_{i} +\lambda_{t}+\varepsilon_{it} \end{split} \label{e2} \end{equation}$\

-   $\text{Screen Time}_{it}$: Smartphone use time before users fall asleep
-   $\text{Social Network Features}_{it}$: Degree Centrality and K-Core
-   $\text{X}_{it}$: Control variables: Steps, sleep duration, naps, etc.
-   $\theta_i$: Individual fixed effect (students)
-   $\lambda_t$: Time fixed effect (day)

## Smartphone Addiction Esimation (Logistic)

``` {.python code-line-numbers="12-13"}
global id egoid
global t date2
global ylist addic_noncom90
global mainIV  active_nodes out_contacts  num_edges  steps minsasleep trust close position duration
global Social_Control degree_centrality core_number
global Other_Control i.insession i.weekday community naps nap_minsasleep
global fe i.studyweek
*Set data as panel data
sort $id $t
xtset $id $t

xtreg $ylist $fe  $Other_Control $Social_Control  $mainIV , fe cluster($id) 
xtlogit $ylist $fe  $Other_Control $Social_Control  $mainIV , fe cluster($id) or
outreg2 using SoUnAcSl.tex, append dec(3) addtext(Communication, Full, Unit F.E., YES, Week F.E, YES) keep($mainIV $Social_Control)  title("90 Addiction Estimation")
```

## Result 4: Addiction Esimation (Logistic)

![](images/paste-2.png){fig-align="center"}

##

## Interpretation

::: incremental
-   Network features **outperform** traditional constructs (Trust, Social Distance (Closeness)).
:::

##

### 2025-02-04 ProjectBlog/paper2/Paper 2 Slides/P2 Slides.qmd
paper 2 slides

@@
 
-### Background
+### Motivation
 
@@
 
-### **Research Gap**
+### **Gap**
 
--   To address the consequences of lack of social engagement, prior studies primarily focus on social interaction volume. However, little attention is paid the the structure of one's social network.
+-   To address the consequences of lack of social engagement, prior studies primarily focus on social interaction volume.
 
--   Specifically, it is not clear whether activating different parts (e.g., core vs.periphery) of social network impact individuals differently.
+-   However, little attention is paid the the structure of one's social network.
+Specifically, it is not clear whether activating different parts (e.g., core vs.periphery) of social network impact individuals differently.
 
-### Context:
+### Study/Methodology
+
+-   We examine whether activating the core parts of social networks, as measured by K-Core, affects smartphone usage activities differently than activating peripheral parts.
+
+##
+### Study/Methodology
+-   We leverage data sets collected from a series of longitudinal studies that tracked participants’ smartphone use, social networks, and physical activities.
+We measure social network activation in real-time and track its evolution for each participant, combining self-reported social network structure information and real-time mobile communications.
 

### 2025-02-04 ProjectBlog/paper2/Network Paper/p2literature.qmd
is studies on network

---
title: "IS Studies on Social Network"
date: 02/04/2025
date-modified: last-modified
draft: true
date-format: full
categories: [Others]
#image: "search.png"
tbl-colwidths: [5,50,75]
format: 
  html:
    page-layout: full
---

# Network Dynamics: How Can We Find Patients Like Us

**Lu (Lucy) Yan, Jianping Peng, Yong Tan**

<iframe src="pdfs/Yan et al. - 2015 - Network Dynamics How Can We Find Patients Like Us.pdf" style="width:100%; height:1500px;" frameborder="0">

</iframe>

### 2025-02-04 ProjectBlog/paper2/Paper 2 Slides/P2 Slides.qmd
is studies on network

@@
 ##
+
 ### Study/Methodology
+
 -   We leverage data sets collected from a series of longitudinal studies that tracked participants’ smartphone use, social networks, and physical activities.
 We measure social network activation in real-time and track its evolution for each participant, combining self-reported social network structure information and real-time mobile communications.
+-   Related studies:
 
-Social isolation ➟ Smartphone Addiction
+<iframe src="pdfs/Yan et al. - 2015 - Network Dynamics How Can We Find Patients Like Us.pdf" style="width:100%; height:1500px;" frameborder="0">
+
+</iframe>
 

### 2025-02-04 ProjectBlog/paper2/Network Paper/p2literature.qmd
is network

@@
 </iframe>
+
+# Feeling Blue? Go Online: An Empirical Study of Social Support Among Patients
+
+**Lu (Lucy) Yan, Yong Tan**
+
+<iframe src="pdfs/Yan and Tan - 2014 - Feeling Blue Go Online An Empirical Study of Social Support Among Patients.pdf" style="width:100%; height:1500px;" frameborder="0">
+
+</iframe>
+
+# Social Networks and the Diffusion of UserGenerated Content: Evidence from YouTube
+
+**Anjana Susarla, Jeong-Ha Oh, Yong Tan**
+
+<iframe src="pdfs/Susarla et al. - 2012 - Social Networks and the Diffusion of User-Generated Content Evidence from YouTube.pdf" style="width:100%; height:1500px;" frameborder="0">
+
+</iframe>
+
+# Network Effects: The Influence of Structural Capital on Open Source Project Success
+
+**Param Vir Singh, Yong Tan, Vijay Mookerjee**
+
+<iframe src="pdfs/Singh et al. - 2011 - Network Effects The Influence of Structural Capital on Open Source Project Success.pdf" style="width:100%; height:1500px;" frameborder="0">
+
+</iframe>
+
+# Location, Location, Location: How Network Embeddedness Affects Project Success in Open Source Systems
+
+**Rajdeep Grewal, Gary L. Lilien, Girish Mallapragada,**
+<iframe src="pdfs/Grewal et al. - 2006 - Location, Location, Location How Network Embeddedness Affects Project Success in Open Source System.pdf" style="width:100%; height:1500px;" frameborder="0">
+
+</iframe>

### 2025-02-05 ProjectBlog/paper2/Paper 2 Slides/P2 Slides.qmd
is network studies

@@
 
-##
-
 ###
-
-![](inout.png){fig-align="center"}
 
@@
 -   **H1:** Activating social networks reduces smartphone screen time; the reduction in screen time increases with the number of contacts activated. <br /> <br /> <br />
-
-## Whom to activate?
-
-Identification of Social Influence
-
--   Social person VS. Non-social person
--   Central VS. Peripheral
-
-## Connectedness
-
-![](images/centrality-01.png){fig-align="center"}
-
--   **H2:** Activating social networks with a higher **Degree Centrality** score **reduces** the time spent on a smartphone.
-
-## Consider group cohesiveness
-
-![](images/core_number.png){fig-align="center"}
-
--   **H3:** Activating social networks with a higher **K-Core** score **reduces** the time spent on a smartphone.
 

### 2025-02-11 ProjectBlog/paper2/Paper 2 Slides/P2 Slides.qmd
Extraversion as control

@@
 -   $\theta_i$: Individual fixed effect (students)
--   $\lambda_t$: Time fixed effect (week)
-
-## Result 1 & 2 (Centrality & K-Core):
-
-![](images/2table5.png){fig-align="center"}
-
-## Interpretation
-
-::: incremental
--   Degree Centrality **does not** affect non-communication smartphone use but **improve**s overall smartphone use by increasing the time spent on communication. **H1 is not supported.**
--   K-Core **reduces** overall smartphone use( Communication, others and overall).  **H2 is supported.**
-:::
-
-## Mediation of Physical Activity
-
-![](images/paste-1.png){fig-align="center"}
-
-## Sobel-Goodman Mediation Tests
-
-![](/posts/Mediation%20Effect%20of%20Steps/images/paste-6.png){fig-align="center"}
-
-## Mediation of Physical Activity
-
-![](/posts/Mediation%20Effect%20of%20Steps/images/mediation%20-%20before.png){fig-align="center"}
-
-## Interpretation
-
-::: incremental
--   ::: incremental
-    Core number reduces screen time by increasing individuals' physical active level
-
-    15.8% of reductive effects of core number come from steps
-    :::
-:::
-
-## Result 4: Addiction Esimation (Logistic)
-
-\
-Addiction is defined as:
-
--   **Overall** addiction: overall screen time \> 300 min
-
--   **Non-communication-drive** addiction: Non-communication screen time \> 240 min
-
--   **Communication-drive** addiction: Communication screen time \> 40 min
-
-## Specification 2
-
-$\begin{equation} \begin{split} \ln \left(\frac{\operatorname{Pr}\left(\text { Addiction }_{it}=1 \mid \boldsymbol{X}_{i t}\right)}{1-\operatorname{Pr}\left(\text { Addiction }_{it}=1 \mid \boldsymbol{X}_{i t}\right)}\right) = \beta_{0}+ \beta_{1} \cdot \text{Social Network Features}_{it}+ \\ \alpha \cdot X_{it}+\theta_{i} +\lambda_{t}+\varepsilon_{it} \end{split} \label{e2} \end{equation}$\
-
--   $\text{Screen Time}_{it}$: Smartphone use time before users fall asleep
--   $\text{Social Network Features}_{it}$: Degree Centrality and K-Core
--   $\text{X}_{it}$: Control variables: Steps, sleep duration, naps, etc.
--   $\theta_i$: Individual fixed effect (students)
 -   $\lambda_t$: Time fixed effect (day)
 
-## Smartphone Addiction Esimation (Logistic)
+## Alternative Explanation
 
-``` {.python code-line-numbers="12-13"}
-global id egoid
-global t date2
-global ylist addic_noncom90
-global mainIV  active_nodes out_contacts  num_edges  steps minsasleep trust close position duration
-global Social_Control degree_centrality core_number
-global Other_Control i.insession i.weekday community naps nap_minsasleep
-global fe i.studyweek
-*Set data as panel data
-sort $id $t
-xtset $id $t
+![](images/clipboard-3408104519.png){fig-align="center"}
 
-xtreg $ylist $fe  $Other_Control $Social_Control  $mainIV , fe cluster($id) 
-xtlogit $ylist $fe  $Other_Control $Social_Control  $mainIV , fe cluster($id) or
-outreg2 using SoUnAcSl.tex, append dec(3) addtext(Communication, Full, Unit F.E., YES, Week F.E, YES) keep($mainIV $Social_Control)  title("90 Addiction Estimation")
-```
+-   Extraverted individuals may incline to activate embeded contacts for group activities.
 
-## Result 4: Addiction Esimation (Logistic)
+## Subsample Analysis (Network Size)
 
-![](images/paste-2.png){fig-align="center"}
+![](images/clipboard-2421990295.png){fig-align="center"}
 
-##
+-   K-Core is more effective in reducing screen time for one with small social network**.**
 
-## Interpretation
+## Subsample Analysis (Steps)
 
-::: incremental
--   Network features **outperform** traditional constructs (Trust, Social Distance (Closeness)).
-:::
+![](images/clipboard-997836528.png){fig-align="center"}
 
-##
+-   K-Core is more effective in reducing screen time for one with high level steps**.**
+
+## Subsample Analysis (Screen Time)
+
+![](images/clipboard-894895312.png){fig-align="center"}
+
+-   K-Core is more effective in reducing screen time for heavy screen users**.**

### 2025-02-25 ProjectBlog/paper2/Paper 2 Slides 2/p2literature.qmd
paper 2 slides

---
title: "Slides for Social Network Paper"
date: 02/25/2025
date-modified: last-modified
draft: false
date-format: full
categories: [Paper2]
#image: "search.png"
tbl-colwidths: [5,50,75]
format: 
  html:
    page-layout: full
---

# Slides for Social Network Paper

<iframe src="pdfs/Social_Network_Paper_Slides.pdf" style="width:100%; height:1500px;" frameborder="0">

</iframe>

### 2025-03-11 ProjectBlog/paper2/Paper 2 Slides 2/p2literature.qmd
paper 2 update
p2 updates

@@
 </iframe>
+
+# Outline for Social Network Paper
+
+<iframe src="pdfs/2_27_Paper_2_Outline.pdf" style="width:100%; height:1500px;" frameborder="0">
+
+</iframe>
+
+Conference: https://2025.cswimworkshop.org/
+
+# Mechanism Paper
+
+<iframe src="pdfs/send-down.pdf" style="width:100%; height:1500px;" frameborder="0">
+
+</iframe>
+
+# Causal Inference Methods
+
+<iframe src="pdfs/Machine learning in causal inference for epidemiology.pdf" style="width:100%; height:1500px;" frameborder="0">
+
+</iframe>

### 2025-04-15 ProjectBlog/paper2/Paper 2 Slides 2/p2literature.qmd
paper 2
paper 2 by break

@@
 
+# Mechanism
+
+![](images/clipboard-4127087002.png){fig-align="center"}
+
+![](images/clipboard-2231454442.png){fig-align="center"}
+
+# Restults with Comm Vs NoComm Screen Time
+
+![](images/clipboard-1110454764.png){fig-align="center"}
+
+![](images/clipboard-1333816286.png)
+
 # Slides for Social Network Paper
 
-<iframe src="pdfs/Social_Network_Paper_Slides.pdf" style="width:100%; height:1500px;" frameborder="0">
+<iframe src="pdfs/Social_Network_Paper_Slides___CHITA.pdf" style="width:100%; height:1500px;" frameborder="0">
 
@@
 
+## Economic Analysis and Policy
+
+![](images/Camera_XHS_17447327922881040g2sg312icvo3s0c7g48uveq05df6k24ft9o8.jpg){fig-align="center"}
+
 # Causal Inference Methods

### 2025-04-22 ProjectBlog/Ipynb/Ipynb/ipynb.qmd
p1 plot and CHITA Slides

--- 2025-01-07 ProjectBlog/others/Natality/natality.qmd
@@
 tbl-colwidths: [5,30,125]
-format: 
-  html:
-    page-layout: full
-    default-image-extension: svg
-bibliography: references.bib
+format: ipynb
 ---

### 2025-04-22 ProjectBlog/others.qmd
p1 plot and CHITA Slides

---
title: "Others"
listing: 
  contents: others # all Quarto docs in the `posts` directory will be included on your listing page
  type: grid # or `default` or `table`; each type has its own set of yaml options to include
  sort: 
      - "date-modified desc" # can also sort on more than one field
      - "date desc"
  categories: false # allows you to sort posts by assigned categories
  sort-ui: [date-modified, title]
  fields: [image, date-modified, title, description, date, author]
  page-size: 6
format:
  html:
    css: styles2.css
class: custom-font-pos
website:
  favicon: Virginia_Tech_seal.svg.png
  image: Horizontal_VT_Full_Color_RGB.png
  sidebar:
    tools:
      - icon: github
        href: https://github.com/Shaokang-Yang
      - icon: linkedin
        href: https://www.linkedin.com/in/shaokang-y-52b633162/
    section: true
    contents:
      - href: index.qmd
        text: Home
      - research.qmd
      - teaching.qmd
      - posts.qmd
---

### 2025-04-22 ProjectBlog/paper2/DV Adjust/DV Adjust.qmd
p1 plot and CHITA Slides

@@
 
-Distribution of going to be times.
+## Distribution of Going to Bed Times
 
@@
 
-Distribution of waking up times.
+It is not likely that social network activation affects screen time **right before sleep**.
+
+## Distribution of Waking Up Times
 
 ![](images/wake.png){fig-align="center"}
+
+## Results with 24 hours Screen Time Measurement
+
+![](images/clipboard-1540611184.png){fig-align="center"}
+
+## Screen Time \< 21:00
+
+![](images/clipboard-2412859547.png){fig-align="center"}
+
+Results with Lagged Core Number
+
+![](images/clipboard-310908795.png){fig-align="center"}
+
+## Potential Mediation Effects
+
+![](images/clipboard-4063857286.png){fig-align="center"}

### 2025-04-22 ProjectBlog/paper2/Paper 2/paper2.qmd
p1 plot and CHITA Slides

---
title: "Social Network Activation: \\The Application in Smartphone Use"
date: 10/09/2023
date-modified: last-modified
date-format: full
categories: [Paper2]
image: "inout.png"
format:
  revealjs: 
    theme: default
smaller: true
bibliography: references.bib
---

### Background

Humans are inherently **social beings**.

-   Social engagement ➟ belongingness, social fulfillment, etc [@luo2020].

-   Social isolation ➟ anxiety, depression [@robb2020], and suicide [@garnettf.2023].

### **Research Gap**

-   Social interaction volume VS. **Structure/Topology** ➟ Behavior/Health?

-   Social network **activation/evolution** ➟ Behavior/Health?

### Context:

Social isolation ➟ Smartphone Addiction

##

###

![](inout.png){fig-align="center"}

## Hypothesis 1

-   **H1:** Activating social networks reduces smartphone screen time; the reduction in screen time increases with the number of contacts activated. <br /> <br /> <br />

## Whom to activate?

Identification of Social Influence

-   Social person VS. Non-social person
-   Central VS. Peripheral

## Connectedness

![](images/centrality-01.png){fig-align="center"}

-   **H2:** Activating social networks with a higher **Degree Centrality** score **reduces** the time spent on a smartphone.

## Consider group cohesiveness

![](images/core_number.png){fig-align="center"}

-   **H3:** Activating social networks with a higher **K-Core** score **reduces** the time spent on a smartphone.

## Methodology

<br> ![](images/method.png){fig-align="center"}

## How SNA features are calculated

![Survey t-1](images/Demo-t-1-2.png){fig-align="center"}

## How SNA features are calculated

![Survey t-1](images/Demo-t-1.png){fig-alt="The normalized degree centrality for a node in an undirected network is calculated by dividing the degree of the node (the number of its connections) by the maximum possible degree in the network. The maximum possible degree is N−1, where N is the total number of nodes in the network." fig-align="center"}

| Node        | Connections | Max Degree N−1 | Degree Centrality |
|-------------|-------------|----------------|-------------------|
| A           | 2           | 3              | 2/3               |
| B           | 2           | 3              | 2/3               |
| C           | 3           | 3              | 1                 |
| Participant | 3           | 3              | 1                 |

## How SNA features are calculated

![Survey t](images/Demo-t.png){fig-align="center"}

## How SNA features are extracted

![Survey t+1](images/Demo-t+1.png){fig-align="center"}

## Specification 1

\

$\begin{equation} \begin{split} \text{Screen Time}_{it} = \beta_0 + \beta_1 \cdot \text{Social Network Features}_{it} + \alpha \cdot X_{it} + \theta_i + \lambda_t + \varepsilon_{it} \end{split} \label{e1}\end{equation}$\

-   $\text{Screen Time}_{it}$: Smartphone use time before users fall asleep
-   $\text{Social Network Features}_{it}$: Degree Centrality and K-Core
-   $\text{X}_{it}$: Control variables: Steps, sleep duration, naps, etc.
-   $\theta_i$: Individual fixed effect (students)
-   $\lambda_t$: Time fixed effect (week)

## Result 1 & 2 (Centrality & K-Core):

![](images/2table5.png){fig-align="center"}

## Interpretation

::: incremental
-   Degree Centrality **does not** affect non-communication smartphone use but **improve**s overall smartphone use by increasing the time spent on communication. **H1 is not supported.**
-   K-Core **reduces** overall smartphone use( Communication, others and overall).  **H2 is supported.**
:::

## Mediation of Physical Activity

![](images/paste-1.png){fig-align="center"}

## Sobel-Goodman Mediation Tests

![](/posts/Mediation%20Effect%20of%20Steps/images/paste-6.png){fig-align="center"}

## Mediation of Physical Activity

![](/posts/Mediation%20Effect%20of%20Steps/images/mediation%20-%20before.png){fig-align="center"}

## Interpretation

::: incremental
-   ::: incremental
    Core number reduces screen time by increasing individuals' physical active level

    15.8% of reductive effects of core number come from steps
    :::
:::

## Result 4: Addiction Esimation (Logistic)

\
Addiction is defined as:

-   **Overall** addiction: overall screen time \> 300 min

-   **Non-communication-drive** addiction: Non-communication screen time \> 240 min

-   **Communication-drive** addiction: Communication screen time \> 40 min

## Specification 2

$\begin{equation} \begin{split} \ln \left(\frac{\operatorname{Pr}\left(\text { Addiction }_{it}=1 \mid \boldsymbol{X}_{i t}\right)}{1-\operatorname{Pr}\left(\text { Addiction }_{it}=1 \mid \boldsymbol{X}_{i t}\right)}\right) = \beta_{0}+ \beta_{1} \cdot \text{Social Network Features}_{it}+ \\ \alpha \cdot X_{it}+\theta_{i} +\lambda_{t}+\varepsilon_{it} \end{split} \label{e2} \end{equation}$\

-   $\text{Screen Time}_{it}$: Smartphone use time before users fall asleep
-   $\text{Social Network Features}_{it}$: Degree Centrality and K-Core
-   $\text{X}_{it}$: Control variables: Steps, sleep duration, naps, etc.
-   $\theta_i$: Individual fixed effect (students)
-   $\lambda_t$: Time fixed effect (day)

## Smartphone Addiction Esimation (Logistic)

``` {.python code-line-numbers="12-13"}
global id egoid
global t date2
global ylist addic_noncom90
global mainIV  active_nodes out_contacts  num_edges  steps minsasleep trust close position duration
global Social_Control degree_centrality core_number
global Other_Control i.insession i.weekday community naps nap_minsasleep
global fe i.studyweek
*Set data as panel data
sort $id $t
xtset $id $t

xtreg $ylist $fe  $Other_Control $Social_Control  $mainIV , fe cluster($id) 
xtlogit $ylist $fe  $Other_Control $Social_Control  $mainIV , fe cluster($id) or
outreg2 using SoUnAcSl.tex, append dec(3) addtext(Communication, Full, Unit F.E., YES, Week F.E, YES) keep($mainIV $Social_Control)  title("90 Addiction Estimation")
```

## Result 4: Addiction Esimation (Logistic)

![](images/paste-2.png){fig-align="center"}

##

## Interpretation

::: incremental
-   Network features **outperform** traditional constructs (Trust, Social Distance (Closeness)).
:::

##

### 2025-04-22 ProjectBlog/others/Frame Theory/index.qmd
CHITA

---
title: "Frame Theory"
date: 02/04/2024
date-modified: last-modified
date-format: full
categories: [Others]
website:
  comments: 
    utterances:
      repo: quarto-dev/quarto-web
#image: "cluster1.png"
tbl-colwidths: [5,30,125]
format: 
  html:
    page-layout: full
---

## Understanding involution with mental accounting

The term involution is originally used to describe a society or economic system that becomes increasingly competitive inside but does not generate more output. Nowadays, it has been adopted to describe a situation where intense competition and the pressure to succeed lead to overwork at the cost of personal well-being and quality of life, without resulting in meaningful societal or individual advancement. In some contexts, involution is interpreted as "rat race". Involution may cause negative mental outcomes such as anxiety and derpression.

In the context of involution, individuals may disproportionately allocate their time and effort towards activities that are believed to enhance their competitiveness, like studying for entrance exams or working overtime. Evidence implies that the situation may be driven by individuals' homogeneous goals and perceived social expectations.

Since mental accounting describes the way people categorize, perceive and prioritize money, time or effort. We conjecture that homogeneous mental accounting strategy increases involution in a occupational setting and thus increase anxiety level. In contrast, heterogeneous mental accounting strategy decreases involution and thus reduce anxiety. In this paper, our objective is to understand how mental accounting impact the involution within a team.

## Does social media make anxiety?

In the era of digitalization, social media has become so pervasive that the number of users has reached 5.04 billion as of January, 2024, which accounts for 62.3% of the total population. While multiple studies show that using social media may cause anxiety for users,. One reason is that individuals tend to selectively post or disclose the best about themselves, which may change other users' reference points. For example, job candidates may share their offers and packages on social media. However, those who are willing to share the information are usually those above average. This may improve the other individual's reference point , decrease their self-efficacy, and increase anxiety. According to social comparison theory, this may impact an individual's self-evaluation. Therefore, we conjecture that social media positively improves individuals reference points and increases anxiety levels.

### 2025-04-22 ProjectBlog/paper1/IV/.vdoc.py

@@ -1,0 +1,173 @@
+# type: ignore
+# flake8: noqa
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| echo: false
+#| warning: false
+#| output: true
+import time;import pandas as pd;import numpy as np;import datetime
+from datetime import datetime;from datetime import timedelta;import sqlite3;import warnings
+import matplotlib.pyplot as plt;import seaborn as sns;warnings.filterwarnings('ignore')
+
+df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/OneDrive-Personal/Nethealth/Data/CNSA/combine/7/bt7_1.5r.csv")
+
+df[['egoid','count_begin90', 'time_fallsleep','battery','battery_time','charging','binterval']]
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| echo: false
+#| warning: false
+#| output: true
+
+df[['egoid','count_begin90', 'time_fallsleep','battery','charging','battery_time','binterval']].describe()
+#
+#
+#
+#
+#
+#
+#
+#| echo: false
+#| warning: false
+#| output: true
+df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/OneDrive-Personal/Nethealth/Data/CNSA/combine/7/df7_22-5s.csv")
+df[['egoid','screen_time', 'unlock','message','count_begin90', 'time_fallsleep','battery','charging','battery_time','binterval']].describe()
+#
+#
+#
+#
+#
+#| echo: false
+#| warning: false
+#| output: true
+df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/OneDrive-Personal/Nethealth/Data/CNSA/combine/7/df7_22-5b.csv")
+df[['egoid','screen_time', 'unlock','message','count_begin90', 'time_fallsleep','battery','charging','battery_time','binterval']].describe()
+#
+#
+#
+#| echo: false
+#| warning: false
+#| output: false
+import time;import pandas as pd;import numpy as np ;import datetime
+from datetime import datetime;from datetime import timedelta;import stata_setup
+stata_setup.config('/Applications/Stata', 'mp')
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| echo: false
+#| warning: false
+#| output: false
+#| code-fold: false
+#| code-overflow: wrap
+%%stata
+#| echo: true
+clear all
[…]

### 2025-08-17 index.qmd
mainfont: Lato monofont: Roboto
css font
styles2.css
job website

@@
 title: "Shaokang Yang"
-mainfont: Lato
-monofont: Roboto
+format:
+  html:
+    css: styles2.css
+class: custom-font-pos
 ---
 
--   **Ph.D. in Business Information Technology (Expected)**
+Department of Business Information Technology
 
-Virginia Polytechnic Institute and State University
+Pamplin College of Business, Virginia Tech
 
--   **M.Sc. in Data Science and Economics**
+Blacksburg, VA 24061
 
-University of Milan
+Website: [shaokang-yang.net](shaokang-yang.net)
 
--   **Bachelor of Engineering/Bachelor of Economics**
+-   **Virginia Polytechnic Institute and State University**
 
-Jimei University
+    Ph.D. in Business Information Technology (2026, Expected)
+
+    M.A. in Data Analysis and Applied Statistics
+
+-   **University of Milan**
+
+    M.Sc. in Data Science and Economics
+
+-   **Jimei University**
+
+    Bachelor of Engineering; Bachelor of Economics

### 2025-08-17 research.qmd
Research blog moving
job website

@@
 ---
+
+## Research Interests
+
+-   Topics: Healthcare policy analysis, healthcare IT
+-   Methodologies: Causal inference with econometrics, machine learning, statistical learning
+
+## Working Papers
+
+-   **Smartphone Use, Social Support, and Sleep Health** Shaokang Yang, Idris Adjerid.
+\[[SSRN](https://papers.ssrn.com/sol3/papers.cfm?abstract_id=5368531)\] –*Under Review at Information Systems Research*
+
+-   **Friends over Feeds: How Social Smartphone Use Reduces Screen Time** Shaokang Yang, Idris Adjerid. – *In preparation for submission*\
+
+<!-- -->
+
+-   ***The Abortion War: When Restrictions Meet Technology** Shaokang Yang, Idris Adjerid.* – *In preparation for submission*
+
+## Presentations
+
+-   **Friends over Feeds: How Social Smartphone Use Reduces Screen Time.**\
+    Shaokang Yang, Idris Adjerid
+    -   Conference on Health IT and Analytics (CHITA) — Apr 2025, Austin, TX
+    -   INFORMS Annual Meeting — Oct 2024, Seattle, WA
+-   **Smartphone Use, Social Support, and Sleep Health.**\
+    Shaokang Yang, Idris Adjerid
+    -   Conference on Health IT and Analytics (CHITA) — May 2024, Washington, DC
+    -   33rd Annual POMS Conference — May 2023, Orlando, FL
+    -   Conference on Health IT and Analytics (CHITA) — May 2023, Washington, DC

### 2025-09-01 research.qmd
research update

--- 2025-01-05 research.qmd
@@
 ---
+
+## Research Interests
+
+-   Topics: Policy evaluation on health IT, Digital technologies, Economics of AI
+-   Methodologies: Causal inference with econometrics, machine learning, statistical learning
+
+## Working Papers
+
+### Digital Technologies and Well-being
+
+1. **Smartphone Use, Social Support, and Sleep Health.** Shaokang Yang, Idris Adjerid. [SSRN](http://dx.doi.org/10.2139/ssrn.5368531) -- *Under Review at Information Systems Research*
+
+2. **Friends over Feeds: How Social Smartphone Use Reduces Screen Time.** Shaokang Yang, Idris Adjerid. -- *In preparation for submission (target: Organization Science)*
+
+3. **Pet Ownership and Mental Health During the Pandemic: Evidence from an E-Commerce Platform** Li Lin, Shaokang Yang -- *Data collection phase*
+
+### Policy Evaluation on Health IT
+
+1. **The Abortion War: When Restrictions Meet Technology.** Shaokang Yang, Idris Adjerid. -- *Data collected, working on empirical analysis*
+
+2. **Pro-Choice Vs Pro-Life: The Impact of Telehealth Abortion on Infant Health.** -- *Data collected, working on empirical analysis*
+
+## Presentations
+
+-   **Friends over Feeds: How Social Smartphone Use Reduces Screen Time.**\
+    Shaokang Yang, Idris Adjerid
+    -   Conference on Health IT and Analytics (CHITA) — Apr 2025, Austin, TX
+    -   INFORMS Annual Meeting — Oct 2024, Seattle, WA
+-   **Smartphone Use, Social Support, and Sleep Health.**\
+    Shaokang Yang, Idris Adjerid
+    -   Conference on Health IT and Analytics (CHITA) — May 2024, Washington, DC
+    -   33rd Annual POMS Conference — May 2023, Orlando, FL
+    -   Conference on Health IT and Analytics (CHITA) — May 2023, Washington, DC

### 2025-09-03 index.qmd
job website
website

@@
 
-Department of Business Information Technology
+<table style="width:100%">
+  <tr>
+    <td>Department of Business Information Technology</td>
+    <td align="right">Tel: 540-824-8612</td>
+  </tr>
+  <tr>
+    <td>Pamplin College of Business, Virginia Tech</td>
+    <td align="right">Email: shaokang@vt.edu</td>
+  </tr>
+  <tr>
+    <td>Blacksburg, VA 24061</td>
+    <td align="right"><a href="https://wholehealth.isce.vt.edu/members-directory/yang-shaokang-bio.html">Whole Health Consortium</a></td>
+  </tr>
+</table>
 
-Pamplin College of Business, Virginia Tech
+------------------------------------------------------------------------
 
-Blacksburg, VA 24061
+**Virginia Polytechnic Institute and State University**
 
-Website: [shaokang-yang.net](shaokang-yang.net)
+-   Ph.D. in Business Information Technology (2026, Expected)
 
--   **Virginia Polytechnic Institute and State University**
+-   M.A. in Data Analysis and Applied Statistics
 
-    Ph.D. in Business Information Technology (2026, Expected)
+**University of Milan**
 
-    M.A. in Data Analysis and Applied Statistics
+-   M.Sc. in Data Science and Economics
 
--   **University of Milan**
+**Jimei University**
 
-    M.Sc. in Data Science and Economics
-
--   **Jimei University**
-
-    Bachelor of Engineering; Bachelor of Economics
+-   Bachelor of Engineering; Bachelor of Economics

### 2025-09-17 ProjectBlog/paper2/SP2 Review Response/ReviewResponse.qmd
font palatino

--- 2025-01-06 posts/SP2 Review Response/ReviewResponse.qmd
@@
 ---
-title: "SP2 Reveiw Response: Social Network Activation: \\The Application in Smartphone Use"
+title: "Response Strategy for CIST and HICSS Feedback"
 date: 12/23/2023
@@
 
-We thank Dr.Adjerid, Dr.Liu, and Dr.Lowry for your insightful and valuable feedback and for the opportunity to submit a revision.
-In addition to highlighting the areas that need to be improved, all of you gave detailed suggestions and intensive oral/written instructions I might take to address the concerns.
-I sincerely appreciate your constructive comments and advice.
-The manuscript has been substantially revised in response to the review team's comments.
-Below I provide an overview of the main changes.
-
-### **\[Development of Motivation\]**
-
-In revising the manuscript, we conduct a comprehensive literature review about social engagement, social network activation, and smartphone overuse, through which we can better identify the practical problems and gaps in the previous literature and clarify the contributions of this study.
-Specifically, we summarize three major practical and research motivations in the area.
-
-1.
-Practical problem.
-The literature on social engagement and smartphone overuse suggests that lack of social engagement can lead to negative health outcomes.
-A primary consequence of social isolation that is increasingly popular in life but can be easily neglected is smartphone overuse.
-It is important to examine how to strategically activate social ties so that smartphone users can improve their social engagement level and reduce the excessive time spent on smartphones.
-
-2.  Research gaps. The research gaps of the study are reflected in the following aspects:
-
--   Previous research on social engagement has largely focused on the volume of social interaction, such as the number of contacts and the frequency of interactions, little attention has been given to the impact of social network structure or topology on an individual's behavior and well-being.
-
--   An equally important, but understudied, aspect of social engagement is dynamic evolutions in engagement with different parts of the social network-- the phenomenon termed social network activation.
-Most social networks in the current literature possess a static and cross-sectional nature, potentially causing them to overlook the intrinsic dynamics in social interactions.
-We leverage a longitudinal study to meticulously craft a dynamic social network framework.
-This innovative approach allows us to meticulously trace the progression of individuals' social networks over time, capturing the essence of their evolving connections and interactions.
-
-In addition to the above modification, we introduce and emphasize the technology components in the process of social network activation to make the manuscript fit IS research journals.
-
-### **\[Theorizing and hypothesis development\]**
-
-As suggested by the review team, we conduct a theoretical development for the network features we extracted (degree centrality and K-core), which allows us to develop three hypotheses.
-Drawing on the three streams of literature on social engagement and smartphone overuse, we first hypothesize that **activating social networks reduces smartphone screen time; the reduction in screen time increases with the number of contacts activated (H1)**.
-Furthermore, we identify key nodes with high social influence.
-We infer that contacts with a high degree centrality have a high capacity to motivate social engagement, therefore, our second hypothesis is: **Activating social networks with a higher score of average degree centrality in a social network reduces the time spent on a smartphone (H2)**.
-Nevertheless, we speculate that degree centrality cannot represent a contact's comprehensive influence in a social network as it may neglect a contact's indirect influence, which is the capacity to form social groups and mobilize other contacts.
-Thus, we utilize another essential social network feature, "K-core," to measure a contact's social influence by considering the connectivity of the contact as well as the cohesiveness of the group in which the contact exists.
-Therefore, we propose our third hypothesis: **Activating social networks with a higher average core number score can reduce the time spent on a smartphone (H3)**.
-
-### \[Analysis\]
-
-Our analysis has been improved in several ways. In addition, multiple robustness checks are conducted to validate our estimation results.
-
-1.
-We adjust the threshold of activation.
-In the first version of this manuscript, the activation threshold is communication event \> 0.
-However, there could be a situation in which the contacts did not respond to the information, which lead to a failed activation.
-We adjust the activation threshold to ensure a two-way communication (an effective activation) exists between two smartphone users.
-This eliminates the possibility of one-way communication: one only sends or receives communication information.
-Overall, the estimation results are mostly consistent with earlier results after the adjustment.
-
-2.
-We identified smartphone users who are addicted to smartphones.
-To the best of my knowledge, there is no quantitative definition of smartphone addiction.
-We define smartphone addiction based on multiple criteria.
-Finally, we conduct additional robustness checks to rule out alternative explanations and to check reverse causality.
-All estimation results show that the increase in core number is associated with a decrease in the likelihood of smartphone addiction.
-
-3.
-We conducted a lookup operation to search for the missing contacts’ social network information from the closest neighbors’ social network surveys.
-We also conducted an alternative lookup approach by searching for the missing contacts backward first and then forward.
-In both cases, we borrow the missed contacts’ network features from the closest wave that the contact exists.
-By doing this, we could have a relatively complete social network.  The estimation with an adjusted approach is mostly consistent with earlier estimations.
-
-### **\[Writting\]**
-
-In an effort to increase the readability of the paper, we have overhauled the structure and logic of the paper, tightened the analysis, and checked all the grammatical errors and citations.
-
 ::: panel-tabset
-## Dr.Idris Adjerid {#sec-dr.idris-adjerid}
+## CIST {#sec-dr.idris-adjerid}
 

### 2025-09-17 ProjectBlog/paper1.qmd
font palatino

---
title: "Smartphone Use, Social Support, and Sleep Health"
listing: 
  contents: paper1 # all Quarto docs in the `posts` directory will be included on your listing page
  type: grid # or `default` or `table`; each type has its own set of yaml options to include
  sort: 
      - "date-modified desc" # can also sort on more than one field
      - "date desc"
  categories: false # allows you to sort posts by assigned categories
  sort-ui: [date-modified, title]
  fields: [image, date-modified, title, description, date, author]
  page-size: 6
format:
  html:
    css: styles2.css
class: custom-font-pos
website:
  favicon: Virginia_Tech_seal.svg.png
  image: Horizontal_VT_Full_Color_RGB.png
  sidebar:
    tools:
      - icon: github
        href: https://github.com/Shaokang-Yang
      - icon: linkedin
        href: https://www.linkedin.com/in/shaokang-y-52b633162/
    section: true
    contents:
      - href: index.qmd
        text: Home
      - research.qmd
      - teaching.qmd
      - posts.qmd
---

### 2025-09-17 ProjectBlog/paper1/Pre3HoursSleep/chita.qmd
font palatino

---
title: "Screen Time Before Sleep"
date: 04/22/2025
date-modified: last-modified
date-format: full
categories: [Paper1]
#image: "search.png"
tbl-colwidths: [5,50,75]
format: 
  html:
    page-layout: full
---

# Measurement Window

![](images/clipboard-727691413.png){fig-align="center"}

## Descriptive Statistics

```{python}
#| echo: false
#| warning: false
#| output: true
import time;import pandas as pd;import numpy as np;import datetime
from datetime import datetime;from datetime import timedelta;import sqlite3;import warnings
import matplotlib.pyplot as plt;import seaborn as sns;warnings.filterwarnings('ignore')

df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/GoogleDrive-sky.ang510@gmail.com/My Drive/Nethealth/Data/CNSA/combine/7/df_pre_3hr.csv")

df[['major_minstofallasleep', 'sleep_duration','major_minsawake','sleep_debt', 
    'major_minsafterwakeup',  'major_bedtime',]].describe().round(2)
```

## Model-Free Evidence

![](images/clipboard-3316574643.png){fig-align="center"}

## Waking Up Time as DV

![](images/clipboard-3013034043.png){fig-align="center"}

## Confidence Intervals Plot

![](images/clipboard-3836821377.png){fig-align="center"}

![](images/clipboard-2494050607.png){fig-align="center"}

# CHTIA

The slides for CHITA 2024 are below:

<iframe src="pdfs/Social_Network_Paper_Slides___Yang_Adjerid_Liu.pdf" style="width:150%; height:1500px;" frameborder="0">

</iframe>

You can download it [here](pdfs/CHITA2024.pdf).

### 2025-09-17 index.qmd
font palatino

@@
 
-<table style="width:100%">
-  <tr>
-    <td>Department of Business Information Technology</td>
-    <td align="right">Tel: 540-824-8612</td>
-  </tr>
-  <tr>
-    <td>Pamplin College of Business, Virginia Tech</td>
-    <td align="right">Email: shaokang@vt.edu</td>
-  </tr>
-  <tr>
-    <td>Blacksburg, VA 24061</td>
-    <td align="right"><a href="https://wholehealth.isce.vt.edu/members-directory/yang-shaokang-bio.html">Whole Health Consortium</a></td>
-  </tr>
-</table>
++-----------------------------------------------+-----------------------------------------------------------------------------------------------------+
+| Department of Business Information Technology | Tel: 540-824-8612                                                                                   |
++-----------------------------------------------+-----------------------------------------------------------------------------------------------------+
+| Pamplin College of Business, Virginia Tech    | Email: shaokang\@vt.edu                                                                             |
++-----------------------------------------------+-----------------------------------------------------------------------------------------------------+
+| Blacksburg, VA 24061                          | [Whole Health Consortium](https://wholehealth.isce.vt.edu/members-directory/yang-shaokang-bio.html) |
++-----------------------------------------------+-----------------------------------------------------------------------------------------------------+
 

### 2025-09-17 posts/Clustering Anlysis/cluster.qmd
font palatino

--- 2025-01-05 ProjectBlog/paper1/Clustering Anlysis/cluster.qmd
@@
 
-df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/GoogleDrive-sky.ang510@gmail.com/My Drive/Nethealth/Data/CNSA/combine/7/df7_3hr.csv")
+df=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/OneDrive-Personal/Nethealth/Data/CNSA/combine/7/df7_3hr.csv")
 df1 = df

### 2025-09-17 posts/Daylight Saving Time/daylight.qmd
font palatino

---
title: "Daylight saving time"
date: 04/23/2024
date-modified: last-modified
date-format: full
categories: [Paper1]
image: "time.png"
tbl-colwidths: [5,50,75]
format: 
  html:
    page-layout: full
---

In this blog, we check our results could be impacted by daylight saving time.Daylight saving time refers to the practice of setting the clocks forward by one hour from standard time during the warmer months of the year, in order to make better use of natural daylight. The practice is used in many European countries, as well as in the United States. The idea is that by moving the clocks forward by one hour, people can enjoy more daylight in the evenings, and this can help to reduce energy consumption and promote outdoor activities. Since the data sets we use are longitudinal studies, we need to consider the impact of daylight saving time on our results. The dates of daylight saving time change in this study are as follows: **"2015-03-08", "2015-11-01", "2016-03-13", "2016-11-06", "2017-03-12", "2017-11-05", "2018-03-11", "2018-11-04"**.

### Anomalies Caused by Daylight saving time Change

The following table shows the smartphone use activities for egoid "79897" on a daylight saving time change date **"2016-11-06".** The measurement window for the day range from **2016-11-05 22:22:00** to **2016-11-06 01:22:00,** the observations between the two yellow rows are the those captured by our measurement.

![](images/clipboard-3850785954.png){fig-align="center"}

We observe that the clocks are set backward by one hour from daylight saving time to standard time (orange cells). If there were no daylight saving time change, the ending point of the measurement window will be **2016-11-06 02:22:00. In another word, the three-hour** measurement window is extended to **four** hours on this day. However, since the two observations at 1:57 and 1:59 are out of the measurement window, they are **not** considered in the aggregation process. Therefore, the daylight saving time change caused some anomalies of screen time and unlock.

### Impact of Time Adjustment on Sleep

Due to the clocks change in the Fall and Spring (Spring Forward，Fall Back). Individuals have one hour less sleep on spring change day, and one hour more sleep on fall. Therefore, we may need to drop the observation on those days.

### 2025-09-17 posts/Selection Issue/selection.qmd
font palatino

---
title: "Selection Issues"
date: 02/26/2024
date-modified: last-modified
date-format: full
categories: [Paper1]
image: images/clipboard-1245868360.png
tbl-colwidths: [5,50,75]
format: 
  html:
    page-layout: full
bibliography: references.bib
---

In this update, we try to identify the confounding factors for the three major independent variables: screen time, unlock frequency and message.

## Confounders

1.  **Busynesin the evening.** For example, when a student has to prepare for an exam the next day, he/she may need to focus on studying and reduce smartphone use the night before the exam. In the meantime, the student's sleep debt may increase as he/she spends more time studying on that day.

2.  **Busyness of the next day.** The schedule of the next day may impact students' smartphone use and sleep debt of the previous day. For instance, when students know they have an early class the next day, they may consciously reduce smartphone use and sleep earlier.

3.  **Social activities at night.** Social activities, including parties and dating, may impact both smartphone use and sleep debt. When students have parties scheduled at night, instead of using smartphones, they may spend more time on social activities. Their sleep debt may increase correspondingly due to the

4.  **Tiredness of the day.** One may reduce smartphone use and sleep earlier and more when he/she feels very tired on that day.

5.  **Health status of the day.** When an individual is sick, she/he may have to reduce smartphone use and spend more time on sleep.

6.  **Accident or emergency.** When an individual meets unexpected emergent events, she/he may have to reduce smartphone use. In the meantime, his/her sleep may be deprived.

7.  **Travelling/Flight.** Traveling may impact both smartphone use and sleep debt negatively. When an individual is on a flight, his/her access to a smartphone is limited. Also, the individual's sleep may be disturbed due to the turbulence during flight.

8.  **Change of lifestyle.** When one realizes the harm of smartphone overuse and the importance of healthy sleep, he/she may decide to regulate his/her lifestyle, resulting in less screen time and sleep debt.

9.  **Computer games.** Playing computer games may have impacts on both smartphone use and sleep debt. For example, a student who is addicted to computer games may spend less time on a smartphone and sleep.

10. **Fitness at night.** Some individuals have the habit of working out in the evening or at night. This lifestyle may reduce screen time before sleep and extend sleep duration, as tiredness may help individuals fall asleep earlier.

11. **Insomnia.** Having insomnia issues may impact both smartphone use and sleep. Individuals may have difficulties in falling asleep when they have insomnia issues. Staying awake may leave individuals time to use their smartphones.

12. **Entertainment at night.** Having entertainment activities at night may impact both smartphone use and sleep debt. For example, one may watch TV and stay up late, resulting in less smartphone use and more sleep debt.

13. **Caffeine and Alcohol Consumption**. These substances can affect sleep quality and are related to lifestyle choices that may correlate with smartphone use habits. For example, drinking alcohol may help individuals fall asleep faster and use less smartphone.

14. **Stress Levels**. Overall stress levels can impact both sleep quality and the amount/type of smartphone usage. For instance, when an individual is stressed out due to academic tasks, it may be harder for him/her to fall asleep. In the meantime, the individual may use a smartphone to kill time.

15. **Socioeconomic Status**. This can influence access to smartphones, as well as sleep environments and overall health. For example, students who face financial issues may need to do part-time jobs, which sometimes happens at night (e.g., waiters). This may reduce their smartphone use at night and increase sleep debt.

16. **Marital Status**. Being married or having a partner may influence sleep patterns due to shared sleeping environments and responsibilities that might affect smartphone use before bed.

17. **Children in Household**. The presence of children, especially young ones, can significantly affect sleep patterns and opportunities for smartphone use.

18. **Roommate.** Having roommates may impact individuals' smartphone use and sleep cycle. For example, an individual living with roommates may spend more time face-to-face chatting than on a smartphone screen. Moreover, interacting with roommates may impact sleep duration.

## Category of Confounders

![](images/confounders.png){fig-align="center"}

### Busyness

Weekends

![](images/clipboard-432615052.png){fig-align="center"}

Weekdays

![](images/clipboard-1300913234.png)

In Semesters

![](images/clipboard-2634925452.png){fig-align="center"}

In Breaks

![](images/clipboard-2739325680.png){fig-align="center"}

### Reverse Causality/Insomnia/Roommates/Children

To test the potential impact of insomnia on the relationship between smartphone use and sleep debt, we look at the students' insomnia level. In the first five waves of socil surveys, students took the **Pittsburgh Sleep Quality Index (PSQI)** test to measure their insomnia level. For the specific questions of the survey,please refer to the questionnaireof PSQI in this [link](https://drive.google.com/file/d/1bRWbcFo_mFa9SeZOeC5AiIczccl1xaqE/view) and its [references](https://drive.google.com/file/d/1wSZjLEjG4ISVGIiKkX036s0pzmAqpCpy/view). The PSQI test consists of 19 self-rated questions that generate seven component scores: subjective sleep quality, sleep latency, sleep duration, habitual sleep efficiency, sleep disturbances, use of sleeping medication, and daytime dysfunction. The sum of these seven component scores yields one global score. The global score ranges from 0 to 21, with higher scores indicating worse sleep quality. The PSQI test has been widely used in the literature to measure sleep quality and insomnia level. The following figure shows the distribution of individuals' average PSQI scores of based on the surveys they took.

![](images/clipboard-2084538279.png){fig-align="center"}

Based on PSQI score, a binary PSQIGroup is created to indicate an individual's overall sleep quality. When PSQI is \<= 5, the student is labeled as **'Good Sleep',** otherwise, the student is labeled as **'Disturbed Sleep'.** To test the consistency between Fitbit measured sleep quality and self-reported sleep quality, we compare the sleep debt between the two distinct PSQIGroup groups:

![](images/clipboard-125115316.png){fig-align="center"}

The above figure shows that 'Disturbed Sleep' group has a 10-minute higher sleep debt than "Good Sleep" group.

#### Descriptive Results with Total Observations

To evaluate whether our main results are influenced by the potential confounder "Insomnia", we conduct the estimation separately for "Good Sleep" and 'Disturbed Sleep' groups. First, we recall the main descriptive results with total observations:

![](images/clipboard-641235887.png){fig-align="center"}

#### Descriptive Results by PSQIGroup

Next, we turn to the separate estimations grouped by PSQI level.

![](images/clipboard-1245868360.png){fig-align="center"}

The blue lines in the figures show the sleep debt and orange lines show the message frequency. Lines with circle refer to the 'Disturbed Sleep' group. Lines with square refers to the 'Good Sleep' group. The results suggest that our main estimation results persist in both "Good Sleep" and 'Disturbed Sleep' groups.

#### Estimation by Insomnia Level

To validate the descriptive results above, we run the estimation separately for "Good Sleep" and 'Disturbed Sleep' groups.

##### Good Sleep Group

![](images/clipboard-74609558.png){fig-align="center"}

##### Disturbed Sleep Group

![](images/clipboard-1535161308.png){fig-align="center"}

The estimation results for "Good Sleep" group and "Disturbed Sleep" group are consistent with our main estimation results with full observations. The turning points of the "Disturbed Sleep" group are located **slightly lefter** (81.92 minutes \< 83.33 minutes)than those of the "Good Sleep" group, suggesting that sleep debt of "Disturbed Sleep" group increases earlier than the "Disturbed Sleep" group with the increase of screen time.

#### Predicted Sleep Debt

![](images/PSQI.png){fig-align="center"}

The above figure show the predicted sleep debt for "Good Sleep" group and "Disturbed Sleep" group. We observe that the predicted sleep debt of "Good Sleep" is **lower** than the "Disturbed Sleep" group. Both of them show a U-shape relationship between sleep debt and screen time. Overall, we observe that our main findings are not significantly influenced by insomnia.

### Depression(CES-D)

Depression might be a confounder for the relation between smartphone use and sleep debt. Evidence suggest that around 75% depressed patients have difficulties falling asleep to some degree[@nutt2008]. In this section, we examine whether our main results are influenced by individuals' depression level. Fortunately, students took standardized depression surveys named [Center for Epidemiologic Studies Depression Scale (CES-D)](https://drive.google.com/file/d/1UgC-6Qv7lB3e7LizyRAUcFGz5BZ4IMad/view) in the study, which is a screening test for depression and depressive disorder. CES-D measures depress symptoms defined by the American Psychiatric Association' Diagnostic and Statistical Manual (DSM-V), this [website](https://cesd-r.com/) shows the detail of the scale. The higher the CES-D score, the higher the depression level an individual has. Total Score of 16 or higher is considered depressed, otherwise, it is not depressed. The following figure shows the distribution of participants' CES-D scores.

![](images/clipboard-1199029835.png){fig-align="center"}

CES-D depression scale covered survey 1, 2, 4, 6 and 8. We check whether sleep debt differ between the depressed group and non-depressed group:

![](images/clipboard-1469132000.png){fig-align="center"}

The above figure shows that "Not Depressed" group has an average sleep debt of 49.69 minutes, which is 3.5 minutes lower than that of "Depressed" group.

#### Descriptive Results by Depression Group

![](images/clipboard-2883898341.png){fig-align="center"}

The above figure shows how sleep debt change over screen time for individuals with different depress levels. We observe that depressed individuals have an overall **higher sleep debt** and **lower message frequency**.

#### Estimation by Depression Level

![](images/CESD.png)

Not Depressed Group

![](images/clipboard-1275868022.png){fig-align="center"}

Depressed Group

![](images/clipboard-3857348345.png)

### Depression (BDI)

Beck Depression Inventory （BDI) is another standerdized survey for measuring depression level. The BDI survey was conducted in the second, third, fifth and seventh wave of the study. The BDI survey consists of 21 questions, each with four possible responses ranging from 0 to 3. The total score of the BDI survey ranges from 0 to 63, with higher scores indicating higher depression levels. The following figure shows the distribution of participants' BDI scores. Please refer to the [link](https://drive.google.com/file/d/1OrG87R2E4VOJ5gvT_U9EZPYL1OMnXIcb/view) for the detailed questionnaires.

![](images/clipboard-2833947798.png){fig-align="center"}

The above figure shows the depression levels based on BDI index. \[0-13\] belongs to minimal depression category, \[14-19\] refers to mid depression level, \[20-28\] refers to moderate depression level and \[29-63\] refers to severe depression level.

![](images/clipboard-340590785.png){fig-align="center"}

We combine mild, moderate and severe categories as depressed group and take minimal level category as non-depressed group. The above figure shows that the depressed group has a higher sleep debt.

#### Descriptive Results by Depression Group

![](images/clipboard-3369355500.png){fig-align="center"}

The above figure shows that descriptive trend of sleep debt varying over screen time. It suggests that dethe pressed group has a overall higher sleep debt than the non-depressed group.

#### Predicted Sleep Debt

![](images/BDI.png){fig-align="center"}

The above figure show the predicted sleep debt based on two-way fixed effect mdel. The figure shows that depressed group has an overall l higher sleep debt. Woe observe that the Ushape the relationship persists.

#### Estimation by Depression Level

Not Depresssed Group

![](images/clipboard-1856480893.png){fig-align="center"}

Depressed Group

![](images/clipboard-3789206540.png){fig-align="center"}

The estimation results show that the impact of screen time are consistent in not depressed group and depressed group. However, we observe that the impact of message is not significant for depressed group not matter depression is measured by the CESD or BDI.

### Children at Residential

### Socioeconomic Status

Socioeconomic status could be a confounder for the relationship between smartphone use and sleep debt. For example, students in low-income family may need to do part-time jobs to pay for their student loan debt. In this section, we examine whether our main results are influenced by individuals' socioeconomic status. Specifically, we use parents' income level to measure socioeconomic status. The following figure shows the sleep debt varying over participants' parents' income level.

![](images/clipboard-523211155.png){fig-align="center"}

We observe that students with parents' income greater than \$250K has 38.66 minutes sleep debt, which is much higher than other categories. While students whose parents' income are lower than \$50K have sleep debts of 53.24 and 66.37 minutes, which are higher than the average. We merge the categories with income less than \$50K as low income group, categories with income between \$50K\~\$250K as medium income, and take category with income higher than \$250K as high income. The following figure shows sleep debt with three groups:

![](images/clipboard-2770700742.png){fig-align="center"}

Next, we show how sleep debt vary with screen time differentiated by parents' income level:

![](images/clipboard-453175552.png){fig-align="center"}

We observe that students with low income have a significantly higher sleep debt when screen time is between 10-20 minutes. We speculate that those students may have **part-time jobs** to do **at night**, which limit their phone use time and sleep duration. We also observe that students with high household income have a **higher** message level, indicating that they may spend more time on **networking**.

#### Predicted Sleep Debt

![Sleep Debt by Parents' Income Level](images/income.png){fig-align="center"}

#### Estimation by Household Income Level

##### High Income

![](images/clipboard-1798400788.png){fig-align="center"}

##### Medium Income

![](images/clipboard-2401068854.png){fig-align="center"}

##### Low Income

![](images/clipboard-1508493203.png){fig-align="center"}

### Fitbit Work Status During night shift

Whether Fitbit works during night shift could be a confounder for the relationship between smartphone use and sleep debt. In this section, we examine whether our main results are influenced by individuals' Fitbit work status during night shift. In the survey, participants were asked whether they wear Fitbit during night shift. The following figure shows the sleep debt varying over participants' Fitbit work status during night shift: Does Fitbit work a night shift? The following figure shows the sleep debt varying over participants' Fitbit work status during night shift.

![](images/clipboard-3989197516.png){fig-align="center"}

We observe that individuals whose Fitbit work during night shit has a average sleep debt of 55.7 minutes, which is about 5 minutes higher than those whose Fitbit did not work during night shift.

![](images/clipboard-1822524005.png){fig-align="center"}

#### Estimation by Fitbit Status During Night Shift

##### Not work

![](images/clipboard-391694283.png){fig-align="center"}

##### Work

![](images/clipboard-2730077641.png){fig-align="center"}

### Part-time Job

Students do part-time job from time to time to pay for their student loan debt or release financial pressure. In the survey, students are asked the following question:

![](images/clipboard-3680031307.png){fig-align="center"}

Doing part-time could be a confounder for the causal inference between screen time and sleep debt as doing part-time jobs at night could limit individuals' time spent on screen and sleep.

To address the selection issue of part-time job, we first investigate the relationship between sleep debt and the weekly part-time hours.

![](images/clipboard-617484130.png){fig-align="center"}

We observe that sleep debt increases slightly with the weekly work hours. We then create a dummy variable to further check the results:

![](images/clipboard-1119310652.png)

We find that students with part-time jobs have over 6.57 minutes higher sleep debt than students without part-time job. Net we explore how sleep debt vary with screen time for the two groups:

![](images/clipboard-4185291164.png)

The above figure suggests that students with part-time jobs have higher sleep debt although both groups represent a U-shaped relationship.

#### Estimation by Part-Time Job

##### Without Part-Time Job

![](images/clipboard-2906772081.png){fig-align="center"}

##### With Part-Time Job

![](images/clipboard-321156171.png){fig-align="center"}

The sub-group analysis shows that the estimation results are consistent with our earlier results.

#### Predicted Sleep Debt by Part-Time Job

![](images/partime_job.png){fig-align="center"}

The figure above shows that the predicted sleep debt of students without part-time job is significantly lower than that of students with part-time job.

### Social Network Control

#### Social Closeness

![](images/clipboard-2945320106.png){fig-align="center"}

#### Duration Social Relationship

![](images/clipboard-1966662110.png){fig-align="center"}

#### Centrality of Social Networks

#### ![](images/clipboard-435771002.png) Core Number of Social Networks

![](images/clipboard-2412866658.png){fig-align="center"}

#### Trust

![](images/clipboard-838501164.png){fig-align="center"}

#### Social Network Nodes

![](images/clipboard-3129141658.png){fig-align="center"}

#### Social Network Edges

![](images/clipboard-1877886823.png)

#### Control for Social Network

![](images/clipboard-1538491404.png){fig-align="center"}

#### Control for Social Network(without Structure Features)

![](images/clipboard-3705985854.png){fig-align="center"}

#### Subgroup Analysis by Network Features

We observe that the group with a **long-relationship** social network group has less sleep debt than the group with a short-relationship social network, which supports our “social support” argument. I also conducted subgroup analysis based on the **size, closeness, degree centrality, core number** of the social network, however, their prediction curve do **not support** our “social support” argument. In addition, we can also find the difference between different groups reflected by the **height** of the predicted cure of sleep debt, it is not reflected in **when the turning point appears** (turning point at 80 minutes or 100 minutes).

1.  Subgroup Analysis by Relationship Length of Social Network

    ![](images/relationlength-02.png)

2.  Subgroup Analysis by the Size of Social Network

    ![](images/bigsmall%20net.png)

3.  Subgroup Analysis by the Closeness of Social Network

![](images/close.png){fig-align="center"}

## Alternative Specification

We estimate sleep debt with alternative specification taking "contacts" as main independent variables.

![](images/clipboard-1650227112.png){fig-align="center"}

![](images/clipboard-1320778945.png){fig-align="center"}

The results with alternative specification are consistent with our main specification.

### 2025-09-17 posts/Survey Overlap/index.qmd
font palatino

---
title: "Network Overlapping"
date: 01/29/2024
date-modified: last-modified
date-format: full
categories: [Paper2]
#image: "cluster1.png"
tbl-colwidths: [5,30,125]
format: 
  html:
    page-layout: full
---

Since participants report their network contacts over social network survey, some contacts may be repteatedly reprted in multiple surveys. To understand whether students' social network survey are cumulative or aggregated over time, in this blog, we exmaine the overlapping rate of reported contacts.

The following figure shows how many waves of surveys participants have ever joined.

![](images/paste-1.png)

For example, 78 participants completed 6 surveys.

```{python}
#| echo: false
#| warning: false
#| output: false
import time;import pandas as pd;import numpy as np;import datetime
from datetime import datetime;from datetime import timedelta;import sqlite3
import warnings;warnings.filterwarnings('ignore')
vt=pd.read_csv("/Users/shaokangyang/Library/CloudStorage/OneDrive-Personal/Nethealth/Data/overlap_rate.csv")
```

The following table shows the social network summary of participant "10237".

```{python}
#| echo: false
#| warning: false
#| output: true
vt10237 = vt[vt['egoid'] == 10237]
vt10237 = vt10237.drop(columns=['vertex1', 'vertex2'])
print(vt10237.to_string(index=False))
```

-   **egoid:** individual identifier;

-   **wave:** survey identifier;

-   **surveys:** the number of surveys the participant completed;

-   **contacts:** the number of contacts reported in the current survey;

-   **total contacts:** the number of contacts reported in total survey;

-   **participation_rate:** contacts/total contacts;

-   **contact_ids:** the identifiers of contacts reported in the current survey;

-   **overlap:** the overlapping rate of contacts of previous and current survey, which is calculated as: the number of contacts reported both by the previous and current surveys / the number of contacts in the current survey.

In the survey of wave 2, contacts "**395167(Sibling), 791455(Sibling)**" has been reported in the survey of wave 1, the overlap rate is 2/6=0.33.

In the survey of wave 3, contacts **"760234"(Romantic Partner)** has been reported in the survey of wave 2, the overlap rate is 1/13=0.076.

In the survey of wave 4, contacts "**982757(Sibling), 390853(Friend), 899046(Stepsibling/Friend), 349320(Friend), 760234(Romantic Partner), 857038(Romantic Partner/OtherFamily), 609614(Parent)**" has been reported in the survey of wave 3, the overlap rate is 7/10=0.70.

In the survey of wave 5, contacts " **760234(Romantic Partner), 390853(Friend), 899046(Stepsibling/Friend),, 277215(Friend)**" has been reported in the survey of wave 4, the overlap rate is 4/16=0.25.

In the survey of wave 6, contacts " **669474(Friend), 390853(Friend), 760234(Romantic Partner), 438507(Friend), 549070(Parent), 277215(Friend), 791455(Sibling), 395167(Sibling), 193183(Friend)**" has been reported in the survey of wave 5, the overlap rate is 9/15=0.60.

In the survey of wave 7, contacts " **760234(Romantic Partner), 486534(Friend), 193183(Friend)**" has been reported in the survey of wave 6, the overlap rate is 3/6=0.50.

The following table shows the descriptive summary for all participants (Person $⨯$ Wave of Survey)

```{python}
#| echo: false
#| warning: false
#| output: true
vt.describe()
```

### 2025-09-17 research.qmd
font palatino

@@
 
--   Topics: Policy evaluation on health IT, Digital technologies, Economics of AI
+-   Topics: Public policy evaluation on health IT, Digital technologies, Economics of AI
 -   Methodologies: Causal inference with econometrics, machine learning, statistical learning
@@
 
-### Policy Evaluation on Health IT
+### Public policy Evaluation on Health IT
 
@@
 
--   **Friends over Feeds: How Social Smartphone Use Reduces Screen Time.**\
-    Shaokang Yang, Idris Adjerid
-    -   Conference on Health IT and Analytics (CHITA) — Apr 2025, Austin, TX
-    -   INFORMS Annual Meeting — Oct 2024, Seattle, WA
--   **Smartphone Use, Social Support, and Sleep Health.**\
-    Shaokang Yang, Idris Adjerid
-    -   Conference on Health IT and Analytics (CHITA) — May 2024, Washington, DC
-    -   33rd Annual POMS Conference — May 2023, Orlando, FL
-    -   Conference on Health IT and Analytics (CHITA) — May 2023, Washington, DC
+- Shaokang Yang, Idris Adjerid. *Friends over Feeds: How Social Smartphone Use Reduces Screen Time.* **Scheduled on INFORMS Annual Meeting (2:09 PM – 2:27 PM)**, Atlanta, GA, Oct 28, 2025.
+
+- Shaokang Yang, Idris Adjerid. *Friends over Feeds: How Social Smartphone Use Reduces Screen Time.* *Conference on Health IT and Analytics (CHITA)*, Austin, TX, Apr 2025.
+
+- Shaokang Yang, Idris Adjerid. *Friends over Feeds: How Social Smartphone Use Reduces Screen Time.* *Doctoral Consortium of CHITA*, Austin, TX, Apr 2025.
+
+- Shaokang Yang, Idris Adjerid. *Friends over Feeds: How Social Smartphone Use Reduces Screen Time.* *INFORMS Annual Meeting*, Seattle, WA, Oct 2024.
+
+- Shaokang Yang, Idris Adjerid. *Smartphone Use, Social Support, and Sleep Health.* *Conference on Health IT and Analytics (CHITA)*, Washington, DC, May 2024.
+
+- Shaokang Yang, Idris Adjerid. *Smartphone Use, Social Support, and Sleep Health.* *33rd Annual POMS Conference*, Orlando, FL, May 2023.
+
+- Shaokang Yang, Idris Adjerid. *Smartphone Use, Social Support, and Sleep Health.* *Conference on Health IT and Analytics (CHITA)*, Washington, DC, May 2023.

### 2025-09-17 teaching.qmd
job website
font palatino

@@
 ---
+
+## Instructor
+
+-   **BIT 3424 — Intro to Business Analytics Modelling** — Summer 2024
+
+*Undergraduate advanced course; programming with VBA, Python, and R*
+
+## Tutorial Instructor
+
+-   **BIT 4624 — Cybersecurity Analytics**
+
+Cybersecurity tutorials in data analytics and machine learning with R — Fall 2024
+
+Cybersecurity tutorials in data analytics and machine learning with R — Spring 2023
+
+Cybersecurity tutorials in data analytics and machine learning with R — Fall 2022

### 2025-09-29 research.qmd
talks
Font update
research profile update

@@
 
--   Topics: Public policy evaluation on health IT, Digital technologies, Economics of AI
--   Methodologies: Causal inference with econometrics, machine learning, statistical learning
+-   **Topics:** Public policy evaluation on health IT, Digital technologies, Artificial intelligence (AI) for Behavioral Decision-making, Economics of AI
+-   **Methodologies:** Applied econometrics, experiments, machine learning, statistical learning
 
@@
 
-1. **Smartphone Use, Social Support, and Sleep Health.** Shaokang Yang, Idris Adjerid. [SSRN](http://dx.doi.org/10.2139/ssrn.5368531) -- *Under Review at Information Systems Research*
+1.  **Smartphone Use, Social Support, and Sleep Health.** Shaokang Yang, Idris Adjerid. [SSRN](http://dx.doi.org/10.2139/ssrn.5368531) -- *Under Review at **Information Systems Research***
 
@@
 
-### Public policy Evaluation on Health IT
+### Public Policy Evaluation on Health IT
 
@@
 
-2. **Pro-Choice Vs Pro-Life: The Impact of Telehealth Abortion on Infant Health.** -- *Data collected, working on empirical analysis*
+2.  **Pro-Choice Vs Pro-Life: The Impact of Healthcare Digitalization on Infant Health.** -- *Data collected, working on empirical analysis*
 
-## Presentations
+### AI for Behavioral Decision-making
+
+1.  **Prevention is Better Than Cure: Artificial Intelligence-based Nudging to Prevent Digital Addiction.** -- *Ideation phase.*
+
+## Talks
 

### 2025-10-01 research.qmd
Work in Progress
wise talk

@@
 
-## Working Papers
+## Work in Progress
 
@@
 
--   Shaokang Yang, Idris Adjerid. *Friends over Feeds: How Social Smartphone Use Reduces Screen Time.* **Scheduled on INFORMS Annual Meeting (2:09 PM – 2:27 PM)**, Atlanta, GA, Oct 28, 2025.
+-   Shaokang Yang, Idris Adjerid. *Smartphone Use, Social Support, and Sleep Health.* **Workshop on Information Systems and Economics (WISE)**, Nashville, TN, Dec 17--19, 2025.
+
+-   Shaokang Yang, Idris Adjerid. *Friends over Feeds: How Social Smartphone Use Reduces Screen Time.* **Scheduled on INFORMS Annual Meeting **, Atlanta, GA, 2:09 PM – 2:27 PM, Oct 28, 2025.
 

### 2025-10-09 research.qmd
profile update

@@
 
--   **Topics:** Public policy evaluation on health IT, Digital technologies, Artificial intelligence (AI) for Behavioral Decision-making, Economics of AI
--   **Methodologies:** Applied econometrics, experiments, machine learning, statistical learning
+-   **Topics:** Artificial intelligence (AI) for Behavioral Decision-making,  Technology policy evaluation, Digital technologies, Economics of AI 
+-   **Methodologies:** Applied econometrics, experiments, machine learning, LLM, Causal AI
 
-## Work in Progress
+## Research
 
@@
 
-1.  **Smartphone Use, Social Support, and Sleep Health.** Shaokang Yang, Idris Adjerid. [SSRN](http://dx.doi.org/10.2139/ssrn.5368531) -- *Under Review at **Information Systems Research***
+1. **Smartphone Use, Social Support, and Sleep Health.** Shaokang Yang, Idris Adjerid. [SSRN](http://dx.doi.org/10.2139/ssrn.5368531) — *Under Review at **Information Systems Research***  
+   - Accepted to WISE, Nashville, TN, Dec 17–19, 2025  
+   - Accepted to Conference on Health IT and Analytics (CHITA), Washington, DC, May 2024  
+   - Presented to Doctoral Consortium of CHITA, Washington, DC, May 2024  
+   - Presented to 33rd Annual POMS Conference, Orlando, FL, May 2023  
+   - Accepted to CHITA, Washington, DC, May 2023
 
-2.  **Friends over Feeds: How Social Smartphone Use Reduces Screen Time.** Shaokang Yang, Idris Adjerid. -- *In preparation for submission (target: Organization Science)*
+2. **Friends over Feeds: How Social Smartphone Use Reduces Screen Time.** Shaokang Yang, Idris Adjerid. — *In preparation for submission (target: **Organization Science**)*  
+   - Scheduled at INFORMS, Atlanta, GA, Oct 28, 2025  
+   - Accepted to CHITA, Austin, TX, Apr 2025  
+   - Presented at INFORMS Annual Meeting, Seattle, WA, Oct 2024
 
-3.  **Pet Ownership and Mental Health During the Pandemic: Evidence from an E-Commerce Platform** Li Lin, Shaokang Yang -- *Data collection phase*
+3. **Pet Ownership and Mental Health During the Pandemic: Evidence from an E-Commerce Platform.** Li Lin, Shaokang Yang. — *Data collection phase*
+
+---
 
@@
 
-1.  **The Abortion War: When Restrictions Meet Technology.** Shaokang Yang, Idris Adjerid. -- *Data collected, working on empirical analysis*
+1. **The Abortion War: When Restrictions Meet Technology.** Shaokang Yang, Idris Adjerid. — *Data collected, working on empirical analysis*  
+2. **Pro-Choice Vs Pro-Life: The Impact of Healthcare Digitalization on Infant Mortality.** Shaokang Yang. — *Data collected, working on empirical analysis*
 
-2.  **Pro-Choice Vs Pro-Life: The Impact of Healthcare Digitalization on Infant Health.** -- *Data collected, working on empirical analysis*
+---
 
@@
 
-1.  **Prevention is Better Than Cure: Artificial Intelligence-based Nudging to Prevent Digital Addiction.** -- *Ideation phase.*
+1. **Prevention is Better Than Cure: Artificial Intelligence-based Nudging to Prevent Digital Addiction.** — *Ideation phase*
 

### 2025-10-09 research.qmd
profile update

@@
    - Accepted to Conference on Health IT and Analytics (CHITA), Washington, DC, May 2024  
-   - Presented to Doctoral Consortium of CHITA, Washington, DC, May 2024  
-   - Presented to 33rd Annual POMS Conference, Orlando, FL, May 2023  
+   - Presented at Doctoral Consortium of CHITA, Washington, DC, May 2024  
+   - Presented at 33rd Annual POMS Conference, Orlando, FL, May 2023  
    - Accepted to CHITA, Washington, DC, May 2023
@@
 
--   Shaokang Yang, Idris Adjerid. *Friends over Feeds: How Social Smartphone Use Reduces Screen Time.* *Doctoral Consortium of CHITA*, Austin, TX, Apr 2025.
-
 -   Shaokang Yang, Idris Adjerid. *Friends over Feeds: How Social Smartphone Use Reduces Screen Time.* *INFORMS Annual Meeting*, Seattle, WA, Oct 2024.
@@
 
+-   Shaokang Yang, Idris Adjerid. *Friends over Feeds: How Social Smartphone Use Reduces Screen Time.* *Doctoral Consortium of CHITA*, Washington, DC, May 2024.
+
 -   Shaokang Yang, Idris Adjerid. *Smartphone Use, Social Support, and Sleep Health.* *33rd Annual POMS Conference*, Orlando, FL, May 2023.
